% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={From Newton to the Path Integral},
  pdfauthor={A. Rivero and A.I.Scaffold},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{From Newton to the Path Integral}
\author{A. Rivero and A.I.Scaffold}
\date{2026}

\begin{document}
\maketitle
\begin{abstract}
This paper develops a single structural thesis across classical and
quantum theory: physically meaningful laws arise as controlled limits of
composable local refinements. We begin with Newton's polygonal
approximation of central-force motion and its limit to continuous
dynamics, then re-express the same logic in modern variational form
through additive action functionals. We treat the path integral as a
composition law over refined time slices, not as an isolated quantum
postulate, and we frame deformation quantization and renormalization as
two mathematically distinct control mechanisms for limit consistency.
The narrative is constructive: each stage retains the previous one as a
limiting or compatibility condition rather than replacing it. Within
this architecture we reserve a dedicated role for point-like
(Dirac-supported) probes in weak formulations of the action principle,
emphasizing where they are mathematically valid and where regularization
is mandatory. The result is a staged program from Newtonian limit
methods to quantum amplitudes in which the classical equations are
recovered as stationary limits of a broader compositional framework.
\end{abstract}

\hypertarget{introduction}{%
\section{1. Introduction}\label{introduction}}

The historical and technical problem addressed here is not merely ``how
to quantize,'' but ``how to define a stable continuum theory from
iterative refinement.'' The paper therefore treats Newtonian mechanics,
action principles, path integration, deformation quantization, and
renormalization as parts of one continuity problem.

The first anchor is Newton's geometric method in central-force motion:
replace a curve by a sequence of short segments, impose a local update
rule, and pass to a limit while controlling what is meant by
``vanishing'' quantities. In modern language, the key object is not a
smallest geometric piece but a refinement procedure with invariant
content {[}Newton1687{]}. (The term ``uncuttable'' in this program means
defined only via a refinement limit, not indivisible in the ontological
sense.)

The second anchor is the action formulation. Action is additive under
temporal partitioning, and that additivity is exactly the algebraic
structure needed to compare coarse and fine descriptions. This creates
the bridge to quantum composition: if local contributions compose
multiplicatively while the underlying functional is additive,
exponential weighting is structurally natural {[}Dirac1933{]}
{[}Feynman1948{]}.\footnote{The additivity of the action under temporal
  partition forces the Lagrangian to be local, up to boundary terms:
  cross-temporal correlations would break
  \(S[\gamma_{if}]=S[\gamma_{im}]+S[\gamma_{mf}]\) for generic paths, so
  no cross-time kernel survives. Locality of \(L\) is a Stage 1 forcing
  result (analogous to P4.2's structural forcing at Stage 2), though
  weaker --- it constrains form, not content. With Ostrogradsky
  stability, \(L=L(t,q,\dot{q})\) follows.}

The long-standing foundational tension can be phrased as a Zeno-style
refinement paradox: a refinement description is an \emph{infinite-limit}
construction, and the limit is not automatically unique or even defined
once the refined objects become singular (Dirac-supported probes,
distributional derivatives) or once intermediate quantities diverge.
Berkeley's critique of Newton's fluxions --- the ``ghosts of departed
quantities'' objection {[}Berkeley1734Analyst{]} --- is an early
articulation of this tension. Classical mechanics often hides it by
treating ``send the refinement parameter to zero'' as an axiomatically
legitimate operation. The program pursued here is instead: keep
refinement explicit, isolate where limit-taking needs extra control, and
treat \textbf{quantization} and \textbf{renormalization} as two distinct
mechanisms for making refined composition stable when the naive
Newtonian limit is not rigorous as written.

\texttt{Heuristic\ H0.2\ (Concrete\ failure\ modes\ of\ naive\ refinement-to-zero).}
Three recurring obstructions that make ``refine \(\to 0\)'' nontrivial
in practice are: 1. \textbf{Singular probes:} point-supported variations
and corners/impulses force distributional weak forms (mollifiers and
contact terms). 2. \textbf{Non-uniqueness:} refinement/composition can
admit multiple classically equivalent but quantum-distinct schemes
(ordering/discretization choices), requiring an explicit equivalence or
control map. (Minimal witness: time-slicing \(H=pq\) can yield
\(-\hat p\hat q\) vs \(-\hat q\hat p\), differing by \(O(\hbar)\) as
operators; requiring symmetry of the generator --- the minimal condition
for self-adjointness, itself needed for unitarity --- selects the
midpoint (half-density) convention; see Remark D4.1c.) 3.
\textbf{Divergence:} some refinement limits do not converge without
subtraction/parameter flow (renormalization). (Toy witness: the
derivative exists only after subtracting a \(1/\varepsilon\) divergence
in the difference quotient.) This manuscript treats these as
limit-control problems rather than as postulates about ``nature at the
smallest scale.''

\texttt{Heuristic\ H0.2a\ (No\ Lebesgue\ measure\ on\ path\ space).} In
infinite-dimensional spaces there is no nontrivial translation-invariant
\(\sigma\)-finite Borel measure (no Lebesgue/Haar measure)
{[}Sudakov1959{]} {[}GlimmJaffe1987{]} (see also
{[}Velhinho2017InfDimMeasure{]} for a modern survey), so the formal
symbol \(Dq\) in a path integral cannot be interpreted as an ordinary
``Lebesgue measure on trajectories.'' Therefore the slogan ``refine the
time slicing, integrate over paths, and send \(\Delta t\to0\)'' is not a
raw Newtonian limit statement but a definition-by-refinement that must
specify normalization and, when singularities are present,
regulator/subtraction rules.

\texttt{Heuristic\ H0.3\ (Constants\ as\ control\ parameters\ for\ compatibility\ limits).}
In this program, \(\hbar\), \(c\), and \(G\) can be read as control
parameters for three distinct compatibilities: \(\hbar\to0\) recovers
classical stationarity from oscillatory composition, \(c\to\infty\)
recovers Galilean/Newtonian kinematics from Lorentz-compatible
refinement, and \(G\to0\) switches off geometric backreaction (with
\(\hbar,c,G\) together defining the Planck scale where quantum and
gravitational refinement controls meet). \texttt{Derivation\ D0.2} below
gives a concrete example of a \(c\to\infty\) passage requiring an
explicit subtraction convention.

The third anchor is methodological. In this manuscript, deformation
quantization and renormalization are not presented as detached
specialist topics. They are two ways to control limits: 1. Deformation
quantization controls the classical-to-quantum passage through algebraic
deformation and recovery of Poisson structure in the small-parameter
limit {[}Landsman1998{]} {[}Connes1994{]}. 2. Renormalization controls
divergent refinement procedures by regulator-dependent intermediate
steps and regulator-independent observables {[}ConnesKreimer2000{]}.

Section 2 fixes the formal vocabulary and claim taxonomy used in later
sections. It also narrows one foundational ambiguity: the paper does not
assume that continuum limits are ontological statements about nature. It
assumes only that they are operational definitions of stable predictive
objects. This narrowed statement will be stress-tested in later
sections.

\textbf{Contributions (what is new here).} 1. A refinement/composition
reading of the Newton \(\to\) action \(\to\) kernel chain in which each
stage is retained as a compatibility condition, not replaced. 2. An
intrinsic half-density formulation of the composition law for
propagators, separating coordinate-free kernel composition from
scalarization conventions. 3. A semigroup-closure derivation showing the
short-time normalization exponent \(t^{-d/2}\) is forced by composition
(the ``square-root Jacobian''). 4. A necessity theorem (Proposition
P4.2) showing that an action-dimensional scale \(\kappa=\hbar\) is
forced by composition (the single master axiom), with the identity limit
and dimensional homogeneity derivable from composition combined with the
physical setup (action-based dynamics on \(\mathbb{R}^d\) with mass
\(m\)). The exponential weight form is derived rather than assumed;
extensions to curved, interacting, and Lorentzian settings are
discussed. 5. A refinement-compatibility framing of renormalization in
which RG invariance is the consistency condition demanded by divergent
refinement limits. 6. A fully explicit ``RG appears before QFT''
computation (2D delta/contact interaction) included as an appendix-level
witness.

\hypertarget{notation-and-claim-taxonomy}{%
\section{2. Notation and Claim
Taxonomy}\label{notation-and-claim-taxonomy}}

\textbf{Dimension bookkeeping.} Throughout Sections 2--7, \(d\) denotes
the dimension of the manifold being integrated over in the composition
law (typically configuration-space/spatial dimension in nonrelativistic
kernels). When we write field-theory-style spacetime integrals, we will
denote spacetime dimension by \(D\) to avoid conflating it with the
composition-variable dimension.

\hypertarget{core-objects}{%
\subsection{2.1 Core Objects}\label{core-objects}}

Let \(q:[t_i,t_f]\to \mathbb{R}^d\) be a configuration-space trajectory
and \(\mathcal{L}(q,\dot q,t)\) a Lagrangian. Define the action:

\[
S[q] = \int_{t_i}^{t_f} \mathcal{L}(q,\dot q,t)\,dt.
\]

For a partition \(t_i=t_0< t_1<\cdots<t_N=t_f\) with
\(\Delta t_k=t_{k+1}-t_k\), define the discrete action functional:

\[
S_N[q] = \sum_{k=0}^{N-1} \mathcal{L}\!\left(q_k,\frac{q_{k+1}-q_k}{\Delta t_k},t_k\right)\Delta t_k.
\]

For planar central motion \(q=(r,\theta)\), define areal velocity and
angular momentum:

\[
\dot A = \frac{1}{2}r^2\dot\theta,\qquad
L_{\mathrm{ang}} = m r^2\dot\theta = 2m\dot A.
\]

These definitions are used as the Newtonian-to-variational bridge in
Section 3 and Section 4.

\hypertarget{weak-form-preliminaries-for-point-like-probes}{%
\subsection{2.2 Weak-Form Preliminaries for Point-Like
Probes}\label{weak-form-preliminaries-for-point-like-probes}}

Let \(\eta\in C_c^\infty((t_i,t_f);\mathbb{R}^d)\) be a smooth compactly
supported test variation. The first variation is written
\(\delta S[q;\eta]\), and stationarity means \(\delta S[q;\eta]=0\) for
all admissible \(\eta\).

To model point-supported probes later, introduce a mollifier family
\(\rho_\varepsilon\) with \(\rho_\varepsilon \rightharpoonup \delta\) in
distributions as \(\varepsilon\to 0^+\). Any use of Dirac-supported
variations in this manuscript is understood as a mollified limit unless
explicitly labeled heuristic.

\hypertarget{claim-taxonomy}{%
\subsection{2.3 Claim Taxonomy}\label{claim-taxonomy}}

Every substantive claim is marked by one of: 1. \texttt{Proposition}:
statement intended as mathematically valid under explicit assumptions.
2. \texttt{Derivation}: explicit calculation from stated premises. 3.
\texttt{Heuristic}: physically motivated bridge that is not presented as
full proof.

\hypertarget{seed-claims-for-the-program}{%
\subsection{2.4 Seed Claims for the
Program}\label{seed-claims-for-the-program}}

\texttt{Proposition\ P0.1\ (Additive\ refinement\ structure).} Given a
partition of \([t_i,t_f]\), the discrete action \(S_N\) is additive over
concatenated subintervals by construction. Therefore action is a natural
candidate for refinement comparison.

\texttt{Derivation\ D0.1\ (Composition-compatible\ exponential\ form).}
Suppose a weight map \(W\) on time-sliced paths satisfies: 1.
\(W[\gamma_1\!\circ\!\gamma_2]=W[\gamma_1]W[\gamma_2]\) for composable
segments. 2. \(\log W\) is local in the slice contributions. 3. The
corresponding additive functional is proportional to \(S_N\) in the
refinement limit.

Then there exists a scale \(\kappa\) and constant \(c_0\) such that, up
to normalization, \(W[\gamma]\propto \exp(c_0 S[\gamma]/\kappa)\).
Choosing \(c_0=i\) and \(\kappa=\hbar\) recovers the standard
oscillatory quantum weighting form.

\texttt{Heuristic\ H0.1\ (Classical\ recovery\ as\ concentration).} When
the phase scale is small relative to action variation, dominant
contributions concentrate near stationary-action trajectories. This is
the structural claim later made precise through stationary-phase
analysis.

\texttt{Derivation\ D0.2\ (Nonrelativistic\ limit\ as\ a\ controlled\ \textbackslash{}(c\textbackslash{}to\textbackslash{}infty\textbackslash{})\ subtraction).}
Consider the relativistic free-particle action written with an explicit
speed-of-light parameter: \[
S_{\mathrm{rel}}[q]
=-mc^2\int_{t_i}^{t_f} dt\;\sqrt{1-\frac{\|\dot q(t)\|^2}{c^2}}.
\] For \(\|\dot q\|\ll c\), expand the square root: \[
S_{\mathrm{rel}}[q]
=\int_{t_i}^{t_f} dt\left(-mc^2+\frac12 m\|\dot q(t)\|^2+O(c^{-2})\right).
\] The term \(-mc^2(t_f-t_i)\) diverges as \(c\to\infty\). Classically
it is inert (adding a constant to \(\mathcal L\) does not change the
Euler-Lagrange equations), so one may subtract it as an allowed additive
counterterm to obtain a finite \(c\to\infty\) limit: the Newtonian
kinetic action \(\int \frac12 m\|\dot q\|^2 dt\) plus higher-order
relativistic corrections. In quantum amplitudes, the same subtraction
corresponds to an overall phase \(e^{-imc^2(t_f-t_i)/\hbar}\). This
remark is at the particle-mechanics level; field-theory and gravity
effects of constant terms (vacuum energy) are a separate issue not
addressed here.

\hypertarget{scope-boundary-established}{%
\subsection{2.5 Scope Boundary
Established}\label{scope-boundary-established}}

This section fixes notation and methodological boundaries: 1. Historical
statements are used only as source-anchored motivation. 2. Mathematical
validity requires explicit assumptions and, for singular objects,
explicit regularization. 3. Quantum and QFT-level statements are
introduced only after the composition law and refinement language are
fixed.

\begin{quote}
\textbf{Reader map (compatibilities; where to look).} -
\textbf{Partition compatibility} (\(\mathcal C_t\)): temporal
refinement/composition (time slicing). See Sections 3--4. -
\textbf{Representation compatibility} (\(\mathcal Q_\hbar\)):
ordering/discretization choices with the same \(\hbar\to0\) limit. See
Sections 6--7. - \textbf{Scale compatibility} (\(\mathcal R_\Lambda\)):
coarse/fine scale comparison after parameter running (RG). See Section 8
(and Appendix 10.5 for an explicit witness).

Symbol definitions and formal summary: Appendix 10.3.
\end{quote}

Transition to Section 3: with notation fixed, the next section derives
the Newtonian area-law refinement argument in modern symbols and links
it to \(L_{\mathrm{ang}}\) conservation.

\hypertarget{newtonian-refinement-and-area-law}{%
\section{3. Newtonian Refinement and Area
Law}\label{newtonian-refinement-and-area-law}}

\hypertarget{source-critical-framing}{%
\subsection{3.1 Source-Critical Framing}\label{source-critical-framing}}

In Book I, Proposition I of the \emph{Principia}, Newton proves that a
centripetal forcing rule implies equal areas swept in equal times by the
radius vector. The historical proof is polygonal and limit-based: one
constructs a piecewise-linear trajectory with impulses directed to a
fixed center, then passes to a continuous curve by refinement
{[}Newton1687{]}.

This section uses that structure directly and only then translates to
modern vector notation. Source-critically, the statements below
distinguish: 1. Newton's geometric argument about polygons and limits.
2. A modern reformulation via torque and angular momentum.

The reformulation is mathematically equivalent under the same
assumptions, but it is an interpretive translation, not a verbatim
historical rendering.

\hypertarget{discrete-refinement-model}{%
\subsection{3.2 Discrete Refinement
Model}\label{discrete-refinement-model}}

Fix equal time steps \(\Delta t>0\), times \(t_k=t_0+k\Delta t\), and a
fixed center \(O\). Let \(\mathbf r_k\) be the position vector at
\(t_k\). The stepwise model is: 1. Free inertial drift between \(t_k\)
and \(t_{k+1}\). 2. Instantaneous impulse at each vertex \(t_k\),
directed along \(\mathbf r_k\) (centripetal/central).

Let \(\mathbf v_k^{-}\) be velocity just before the impulse at \(t_k\),
and \(\mathbf v_k^{+}\) just after. The impulse condition is

\[
m\big(\mathbf v_k^{+}-\mathbf v_k^{-}\big)=J_k\,\hat{\mathbf r}_k,
\qquad \hat{\mathbf r}_k=\frac{\mathbf r_k}{\|\mathbf r_k\|}.
\]

Drift then gives

\[
\mathbf r_{k+1}=\mathbf r_k+\mathbf v_k^{+}\Delta t,
\qquad
\mathbf v_{k+1}^{-}=\mathbf v_k^{+}.
\]

\texttt{Derivation\ D1.1\ (Finite-step\ angular\ momentum\ invariance).}
Define \(\mathbf L_k^{-}=m\,\mathbf r_k\times \mathbf v_k^{-}\),
\(\mathbf L_k^{+}=m\,\mathbf r_k\times \mathbf v_k^{+}\).

At impulse:

\[
\mathbf L_k^{+}-\mathbf L_k^{-}
=m\,\mathbf r_k\times(\mathbf v_k^{+}-\mathbf v_k^{-})
=\mathbf r_k\times (J_k\hat{\mathbf r}_k)=\mathbf 0.
\]

During drift:

\[
\mathbf L_{k+1}^{-}
=m\,\mathbf r_{k+1}\times \mathbf v_{k+1}^{-}
=m(\mathbf r_k+\mathbf v_k^{+}\Delta t)\times \mathbf v_k^{+}
=m\,\mathbf r_k\times \mathbf v_k^{+}
=\mathbf L_k^{+}.
\]

Hence \(\mathbf L_{k+1}^{-}=\mathbf L_k^{-}\): angular momentum is
exactly conserved at every finite step in this refinement model.

\texttt{Derivation\ D1.2\ (Equal\ areas\ in\ equal\ times,\ discrete\ form).}
The swept area in step \(k\) is the triangle area

\[
\Delta A_k
=\frac12\left\|\mathbf r_k\times(\mathbf r_{k+1}-\mathbf r_k)\right\|
=\frac12\left\|\mathbf r_k\times \mathbf v_k^{+}\right\|\Delta t
=\frac{\|\mathbf L\|}{2m}\Delta t.
\]

Therefore for fixed \(\Delta t\), \(\Delta A_k\) is independent of
\(k\). This is the equal-areas statement at finite polygonal level.

\texttt{Derivation\ D1.2a\ (Numerical\ witness\ for\ the\ finite-step\ area\ law).}
Consider an inverse-square force with \(GM=m=1\). Place a body at
\(\mathbf r_0=(1,0)\) with velocity \(\mathbf v_0=(0,0.8)\) --- this is
apoapsis of an ellipse with eccentricity \(e=9/25=0.36\) and semi-major
axis \(a\approx 0.735\). The angular momentum is \(L=0.8\).

Running the kick-drift scheme of Section 3.2 with \(N=12\) equal steps
over one period (\(T\approx 3.96\)): every triangular area
\(\Delta A_k\) equals \(L\,\Delta t/(2m)\approx 0.132\) exactly in the
algebraic sense of D1.1--D1.2, despite the radial distance varying by a
factor
\(r_{\mathrm{apo}}/r_{\mathrm{peri}}=(1+e)/(1-e)=17/8\approx 2.1\)
between apoapsis and periapsis. The equality is not a numerical
coincidence or a continuum approximation --- it is an algebraic identity
at each finite step, holding for any central force. Only the trajectory
shape converges under refinement; the swept-area invariant is exact at
every \(N\).

\hypertarget{continuum-passage-and-central-force-generality}{%
\subsection{3.3 Continuum Passage and Central-Force
Generality}\label{continuum-passage-and-central-force-generality}}

\texttt{Proposition\ P1.1\ (Refinement\ limit\ of\ areal\ velocity).} If
\(\max_k \Delta t_k\to 0\) under consistent refinement, the finite-step
law above yields

\[
\frac{dA}{dt}=\frac{\|\mathbf L\|}{2m},
\]

for the limiting trajectory whenever the limit exists in the standard
differentiable sense.

For a smooth central force \(\mathbf F(\mathbf r)=f(r)\hat{\mathbf r}\),
this same invariant follows from torque:

\[
\frac{d\mathbf L}{dt}=\mathbf r\times \mathbf F=\mathbf 0.
\]

So the areal law is independent of the inverse-power index \(n\) in
\(\mathbf F=-(K/r^n)\hat{\mathbf r}\): \(n\) changes radial dynamics and
orbit families, but not the areal-velocity conservation mechanism
itself. A companion note on relativistic central orbits analyzes
Lorentz-compatible kinematics in detail.

\texttt{Remark\ P1.1a\ (Asymptotic\ threshold\ bridge:\ Newton\ \textbackslash{}(3\textbackslash{})\ vs\ SR\ \textbackslash{}(2\textbackslash{})).}
For attractive power-law \(F(r)=K/r^q\), fixed angular momentum \(L\),
and high-momentum kinetic asymptotic
\(E_{\mathrm{kin}}(p)\sim a p^\nu\), one has \(p\sim L/r\) as \(r\to0\).
Hence the centrifugal barrier scales as \(r^{-\nu}\) while the
attraction scales as \(r^{-(q-1)}\), giving threshold
\(q_{\mathrm{crit}}=\nu+1\). This recovers the Newtonian/SR shift
(\(\nu=2\Rightarrow q_{\mathrm{crit}}=3\),
\(\nu=1\Rightarrow q_{\mathrm{crit}}=2\)) in one line. The criterion is
a fixed-\(L\), small-\(r\) asymptotic statement and is distinct from the
separate inverse-square dimensional identity mechanism (where \(K/L\)
has velocity units and yields \(v=K/L\) in SR circular analysis).

\texttt{Heuristic\ H1.1\ (Impulse-to-continuous\ interpretation).} The
impulse model is a refinement scaffold for continuous forcing, not a
literal claim that nature acts by discrete kicks. Its value is
structural: invariants proven exactly at finite step survive controlled
refinement.

\texttt{Remark\ H1.1a\ (Convergence\ of\ the\ polygonal\ construction).}
The passage from discrete polygonal orbits to a continuous trajectory is
non-trivial: it depends on Newton's Lemma 3 (Book I, Section 1 of the
\emph{Principia}) and has been the subject of a scholarly debate.
Nauenberg {[}Nauenberg2003KeplerArea{]} gives a modern reconstruction
showing the polygonal construction has a well-defined continuum limit
parameterizing a continuous planar curve; Pourciau {[}Pourciau2003{]}
critically analyses the same limit and identifies conditions under which
the impulse assumption requires additional care. For the purposes of
this paper, the hedging in P1.1 (``whenever the limit exists in the
standard differentiable sense'') is sufficient: the structural content
of the equal-area invariant at finite step is independent of the
convergence subtleties.

\texttt{Heuristic\ H1.2\ (Newton\textquotesingle{}s\ scheme\ as\ a\ symplectic\ integrator).}
The kick-drift structure of Section 3.2 --- update velocity by an
impulse at the current position, then drift --- is precisely the
symplectic Euler integrator applied to the separable Hamiltonian
\(H(\mathbf r,\mathbf p)=|\mathbf p|^2/(2m)+V(r)\)
{[}Nauenberg1994SymplecticNewton{]} {[}Nauenberg2018GraphicalMethod{]}.
The exact angular-momentum conservation (D1.1) is a consequence of two
properties: the force is central (so each kick preserves \(\mathbf L\)),
and the free drift is linear (so it also preserves \(\mathbf L\)). More
broadly, the symplectic character of the map means it preserves the
canonical 2-form \(\omega=d\mathbf p\wedge d\mathbf r\) at each finite
step. While the method has the same first-order convergence rate as the
explicit Euler scheme analyzed in Section 8.4, its step-doubling
corrections are constrained to preserve the symplectic form --- a
finite-step analogue of the principle that renormalization counterterms
must respect the symmetries of the theory.

\texttt{Remark\ H1.2a\ (Convergence\ theorem\ and\ failure\ mode).}
Standard convergence theory for one-step numerical integrators
guarantees that the polygonal orbit converges to the true continuous
orbit with global error \(O(h)\) on any finite time interval where the
force \(\nabla V\) is Lipschitz --- i.e.~away from the \(r=0\) collision
singularity of central potentials. At the collision point the Lipschitz
constant diverges, the fixed-step scheme breaks down, and regularization
(Kustaanheimo-Stiefel / Levi-Civita coordinate transformations) or
adaptive stepping is required. The structural invariants (angular
momentum, equal areas) are exact at each finite step regardless and do
not depend on the convergence of the interpolation limit. This makes
precise the hedge in H1.1a: the limit exists in the standard
differentiable sense exactly where the force is Lipschitz, and fails at
the singularities where central-force models cease to be smooth.

\hypertarget{closed-question-from-the-section-2-setup}{%
\subsection{3.4 Closed Question from the Section 2
Setup}\label{closed-question-from-the-section-2-setup}}

Section 2 left one key ambiguity open: is Newton's area law a small-step
approximation or a genuine invariant statement? The derivations above
close that point: within the polygonal central-impulse model, the
equal-area law is exact at each finite step and only the curve
interpolation is a limiting passage.

Transition to Section 4: with the Newtonian invariant fixed in modern
notation, the next section derives Euler-Lagrange equations and Noether
charge conservation to show the same structure directly in action
language.

\hypertarget{action-as-additive-invariant}{%
\section{4. Action as Additive
Invariant}\label{action-as-additive-invariant}}

\hypertarget{stationarity-setup}{%
\subsection{4.1 Stationarity Setup}\label{stationarity-setup}}

The Section 3 invariant was derived from a refinement model in
configuration geometry. We now restate the same physics through
stationarity of action.

Assume: 1. \(q:[t_i,t_f]\to\mathbb R^d\) is at least \(C^2\), and
variations \(\eta\) are \(C^1\) (or smooth with compact support). 2.
\(\mathcal L(q,\dot q,t)\) is \(C^1\) in \(t\) and \(C^2\) in
\((q,\dot q)\) on the region reached by \((q(t),\dot q(t))\).

Let the action be

\[
S[q]=\int_{t_i}^{t_f}\mathcal L\big(q(t),\dot q(t),t\big)\,dt,
\]

and define \(q_\varepsilon=q+\varepsilon\eta\) for an admissible
variation \(\eta\), with either: 1. fixed endpoints
\(\eta(t_i)=\eta(t_f)=0\), or 2. compact support in \((t_i,t_f)\).

Stationarity means

\[
\delta S[q;\eta]
=\left.\frac{d}{d\varepsilon}\right|_{\varepsilon=0} S[q_\varepsilon]
=0
\quad\text{for all admissible }\eta.
\]

\texttt{Proposition\ P2.0\ (Fundamental\ lemma,\ vector\ form).} If
\(F:[t_i,t_f]\to\mathbb R^d\) is continuous and
\(\int_{t_i}^{t_f} F(t)\cdot\eta(t)\,dt=0\) for all
\(\eta\in C_c^\infty((t_i,t_f);\mathbb R^d)\), then \(F(t)=0\) for all
\(t\in(t_i,t_f)\).

\hypertarget{euler-lagrange-derivation}{%
\subsection{4.2 Euler-Lagrange
Derivation}\label{euler-lagrange-derivation}}

\texttt{Derivation\ D2.1\ (Euler-Lagrange\ equation).} Differentiate
under the integral sign (justified by the smoothness assumptions). By
the chain rule,
\(\left.\frac{d}{d\varepsilon}\right|_{0}\mathcal L(q+\varepsilon\eta,\dot q+\varepsilon\dot\eta,t) =\frac{\partial\mathcal L}{\partial q}\cdot\eta+\frac{\partial\mathcal L}{\partial\dot q}\cdot\dot\eta\).
Therefore:

\[
\delta S[q;\eta]
=\int_{t_i}^{t_f}
\left(
\frac{\partial\mathcal L}{\partial q}\cdot\eta
+
\frac{\partial\mathcal L}{\partial \dot q}\cdot\dot\eta
\right)dt.
\]

Integrating the second term by parts:

\[
\delta S[q;\eta]
=
\left[
\frac{\partial\mathcal L}{\partial\dot q}\cdot\eta
\right]_{t_i}^{t_f}
+
\int_{t_i}^{t_f}
\left(
\frac{\partial\mathcal L}{\partial q}
-\frac{d}{dt}\frac{\partial\mathcal L}{\partial\dot q}
\right)\cdot\eta\,dt.
\]

Endpoint or compact-support conditions remove the boundary term. By
\texttt{Proposition\ P2.0}, stationarity for all admissible \(\eta\)
implies:

\[
\frac{d}{dt}\frac{\partial\mathcal L}{\partial\dot q}
-\frac{\partial\mathcal L}{\partial q}
=0.
\]

This is the Euler-Lagrange equation.

\hypertarget{rotational-symmetry-and-angular-momentum}{%
\subsection{4.3 Rotational Symmetry and Angular
Momentum}\label{rotational-symmetry-and-angular-momentum}}

For planar central motion with

\[
\mathcal L(r,\theta,\dot r,\dot\theta)=
\frac{m}{2}\big(\dot r^2+r^2\dot\theta^2\big)-V(r),
\]

\(\theta\) is cyclic (\(\partial\mathcal L/\partial\theta=0\)). Applying
Euler-Lagrange to \(\theta\) gives:

\[
p_\theta=\frac{\partial\mathcal L}{\partial\dot\theta}=m r^2\dot\theta
=L_{\mathrm{ang}}
\quad\Rightarrow\quad
\frac{dL_{\mathrm{ang}}}{dt}=0,
\]

which is the rotational Noether conservation law {[}Noether1918{]}.

In full vector form for
\(\mathcal L(\mathbf r,\dot{\mathbf r})=\frac{m}{2}\|\dot{\mathbf r}\|^2-V(\|\mathbf r\|)\),
the canonical momentum is
\(\mathbf p=\partial\mathcal L/\partial\dot{\mathbf r}=m\dot{\mathbf r}\)
and rotational invariance yields the conserved angular momentum vector

\[
\mathbf L=\mathbf r\times\mathbf p.
\]

\texttt{Proposition\ P2.1\ (Geometric-variational\ invariant\ equivalence).}
Under the regularity assumptions above, the Section 3 area-law invariant
and the Noether charge are the same quantity in different language:

\[
\dot A=\frac12 r^2\dot\theta=\frac{L_{\mathrm{ang}}}{2m}.
\]

Thus Section 3 and Section 4 do not provide competing derivations; they
provide geometric and variational presentations of one conserved
structure. Newton's polygonal proof is also strictly stronger in scope:
the equal-area statement is exact at each finite impulse step without
assuming smoothness or even a Lagrangian, whereas Noether's charge
conservation requires a smooth trajectory and rotational symmetry of
\(\mathcal L\) to reproduce the same invariant.

\texttt{Proposition\ P2.2\ (Energy\ for\ autonomous\ central\ motion).}
If \(\mathcal L\) has no explicit time dependence, then the energy
function

\[
E=\dot q\cdot\frac{\partial\mathcal L}{\partial\dot q}-\mathcal L
\]

is conserved (time-translation symmetry, another Noether law)
{[}Noether1918{]}. For the central-motion Lagrangian above,

\[
E=\frac{m}{2}\dot r^2+\frac{L_{\mathrm{ang}}^2}{2mr^2}+V(r),
\]

showing the standard reduction to one-dimensional radial motion with
effective potential
\(V_{\mathrm{eff}}(r)=V(r)+L_{\mathrm{ang}}^2/(2mr^2)\).

\hypertarget{additivity-and-composition-pre-bridge}{%
\subsection{4.4 Additivity and Composition
Pre-Bridge}\label{additivity-and-composition-pre-bridge}}

Recall the discrete action functional from the refinement viewpoint:

\[
S_N[q]=\sum_{k=0}^{N-1}
\mathcal L\!\left(q_k,\frac{q_{k+1}-q_k}{\Delta t_k},t_k\right)\Delta t_k.
\]

It is additive under interval concatenation by construction. This
additivity is the structural input used later for composition-based
quantum weighting in Section 6.

\texttt{Heuristic\ H2.1\ (Toward\ distributional\ probes).} Point-like
probes of extrema can be expressed in distributional language. In this
manuscript, technical use of such probes is deferred to Section 5, where
mollifier limits and admissibility are stated explicitly.

Transition to Section 5: with Euler-Lagrange and Noether structure
fixed, we next extend stationarity analysis to weak/distributional
settings and clarify where Dirac-supported constructions are valid.

\hypertarget{dirac-distributions-and-extremal-action}{%
\section{5. Dirac Distributions and Extremal
Action}\label{dirac-distributions-and-extremal-action}}

\hypertarget{why-weak-formulations-appear-here}{%
\subsection{5.1 Why Weak Formulations Appear
Here}\label{why-weak-formulations-appear-here}}

The story so far treated trajectories as classically smooth. Two themes
force a more careful formulation: 1. Refinement limits often produce
objects that are only piecewise smooth (corners) or are best handled by
weak limits. 2. The ``point-like probe'' idea (Dirac-supported
localization) is naturally stated in distribution theory.

We keep the role of distributions narrow and explicit: distributions are
used as linear functionals on test functions and as limits of smooth
approximations. Nonlinear operations on distributions are not assumed
unless regularized.

\hypertarget{weak-euler-lagrange-equation}{%
\subsection{5.2 Weak Euler-Lagrange
Equation}\label{weak-euler-lagrange-equation}}

Let \(q\in C^1([t_i,t_f];\mathbb R^d)\) be a candidate trajectory and
assume \(\mathcal L(q,\dot q,t)\) is smooth enough that
\(\partial_q\mathcal L\) and \(\partial_{\dot q}\mathcal L\) are
well-defined along \(q\).

\texttt{Proposition\ P3.1\ (Weak\ stationarity\ statement).} If
\(\delta S[q;\eta]=0\) for all
\(\eta\in C_c^\infty((t_i,t_f);\mathbb R^d)\), then the Euler-Lagrange
operator

\[
F[q](t)\equiv \frac{\partial\mathcal L}{\partial q}(q,\dot q,t)
-\frac{d}{dt}\frac{\partial\mathcal L}{\partial\dot q}(q,\dot q,t)
\]

vanishes as a distribution on \((t_i,t_f)\): for all test \(\eta\),

\[
\int_{t_i}^{t_f} F[q](t)\cdot\eta(t)\,dt=0.
\]

Equivalently, \(F[q]=0\) in \(\mathcal D'((t_i,t_f);\mathbb R^d)\),
where \(\mathcal D'\) is the dual of \(C_c^\infty\).

\texttt{Derivation\ D3.1\ (Weak\ form\ from\ first\ variation).} Start
from the first-variation identity (as in Section 4):

\[
\delta S[q;\eta]
=\int_{t_i}^{t_f}\left(
\frac{\partial\mathcal L}{\partial q}\cdot\eta
+
\frac{\partial\mathcal L}{\partial\dot q}\cdot\dot\eta
\right)dt.
\]

Integrate the second term by parts. Compact support eliminates the
boundary term and yields the stated distributional identity.

\hypertarget{point-like-probes-via-mollifiers-not-raw-deltas}{%
\subsection{5.3 Point-Like Probes via Mollifiers (Not Raw
Deltas)}\label{point-like-probes-via-mollifiers-not-raw-deltas}}

Pick a nonnegative mollifier \(\rho\in C_c^\infty(\mathbb R)\) with
\(\int\rho=1\), and define
\(\rho_\varepsilon(t)=\varepsilon^{-1}\rho(t/\varepsilon)\).

\texttt{Proposition\ P3.2\ (Localized\ probing\ under\ continuity).}
Assume \(F[q](t)\) is continuous at a time \(t_0\in(t_i,t_f)\). Then
weak stationarity implies the pointwise condition \(F[q](t_0)=0\).

\texttt{Derivation\ D3.2.} For any fixed vector \(u\in\mathbb R^d\),
choose a localized test function
\(\eta_\varepsilon(t)=\rho_\varepsilon(t-t_0)\,u\). Then the weak
identity gives

\[
0=\int_{t_i}^{t_f} F[q](t)\cdot \rho_\varepsilon(t-t_0)\,u\,dt
=u\cdot\int_{t_i}^{t_f} \rho_\varepsilon(t-t_0)\,F[q](t)\,dt.
\]

As \(\varepsilon\to 0^+\), the convolution integral tends to
\(F[q](t_0)\) by continuity. Since \(u\) was arbitrary, \(F[q](t_0)=0\).

This is the precise sense in which ``Dirac-supported probes'' recover
pointwise Euler-Lagrange equations: they do so through mollifier limits,
not by inserting nonlinear expressions involving \(\delta(t-t_0)\). (For
an expanded treatment with explicit functional-analytic hypotheses, a
fully worked delta-kick model, and the connection from \(N\)-impulse
matching to the time-sliced path integral, cf.~Theorem 2.1 and Section 4
in the Dirac Probes companion note.)

\hypertarget{corners-and-impulses-jump-conditions}{%
\subsection{5.4 Corners and Impulses: Jump
Conditions}\label{corners-and-impulses-jump-conditions}}

There are two distinct phenomena that look ``singular'' in time: 1.
\textbf{Corners}: \(q\) is continuous but \(\dot q\) has a jump at
\(t_0\), with no delta forcing. 2. \textbf{Impulses}: the dynamics
includes a delta force at \(t_0\), producing a momentum jump.

We record both conditions explicitly.

\texttt{Proposition\ P3.3\ (Corner\ condition\ without\ impulse).}
Assume \(q\) is piecewise \(C^2\) with a velocity discontinuity at
\(t_0\), and satisfies the unforced Euler-Lagrange equation on each side
of \(t_0\). Then:

\[
\left[\frac{\partial\mathcal L}{\partial\dot q}\right]_{t_0^-}^{t_0^+}=0.
\]

\texttt{Derivation\ D3.3\ (Corner\ condition).} Integrate the unforced
Euler-Lagrange equation on \([t_0-\varepsilon,t_0+\varepsilon]\):

\[
\left[\frac{\partial\mathcal L}{\partial\dot q}\right]_{t_0-\varepsilon}^{t_0+\varepsilon}
=\int_{t_0-\varepsilon}^{t_0+\varepsilon}\frac{\partial\mathcal L}{\partial q}\,dt.
\]

Let \(\varepsilon\to0^+\). Under local boundedness of
\(\partial_q\mathcal L\), the right-hand side vanishes, yielding the
jump condition above. This is the local corner continuity of canonical
momentum (Weierstrass-Erdmann form in this one-corner setting).

\texttt{Proposition\ P3.4\ (Impulse\ force\ implies\ momentum\ jump).}
Consider the forced Euler-Lagrange equation in distribution form

\[
\frac{d}{dt}\frac{\partial\mathcal L}{\partial\dot q}
-\frac{\partial\mathcal L}{\partial q}
=J\,\delta(t-t_0),
\]

for a fixed impulse vector \(J\in\mathbb R^d\). If
\(\partial_{\dot q}\mathcal L\) has one-sided limits at \(t_0\), then

\[
\left[\frac{\partial\mathcal L}{\partial\dot q}\right]_{t_0^-}^{t_0^+}
\equiv
\frac{\partial\mathcal L}{\partial\dot q}(t_0^+)-\frac{\partial\mathcal L}{\partial\dot q}(t_0^-)
=J.
\]

\texttt{Derivation\ D3.4.} Integrate the equation on
\([t_0-\varepsilon,t_0+\varepsilon]\). The integral of the smooth term
\(\partial_q\mathcal L\) tends to 0 as \(\varepsilon\to 0\). The
derivative term integrates to the jump in
\(\partial_{\dot q}\mathcal L\). The right-hand side integrates to
\(J\).

For the standard mechanical Lagrangian
\(\mathcal L=\frac{m}{2}\|\dot q\|^2-V(q)\), this reduces to the
familiar momentum jump:

\[
m\big(\dot q(t_0^+)-\dot q(t_0^-)\big)=J.
\]

This connects directly to the Section 3 impulse scaffold: central
impulses preserve angular momentum because they change momentum only in
the radial direction.

\hypertarget{extremal-measures-finite-dimensional-analogy-and-limits}{%
\subsection{5.5 Extremal Measures: Finite-Dimensional Analogy and
Limits}\label{extremal-measures-finite-dimensional-analogy-and-limits}}

The phrase ``Dirac distributions to calculate extrema'' is unambiguous
in finite dimensions. For a smooth \(f:\mathbb R\to\mathbb R\), the
distribution \(\delta(f'(x))\) is supported on the critical points of
\(f\). In higher dimensions one analogously uses \(\delta(\nabla f)\).

\texttt{Derivation\ D3.5\ (Square-root\ delta\ normalization\ and\ Born-rule\ form).}
Let \(f:\mathbb R^N\to\mathbb R\) be smooth and define, for
\(\varepsilon>0\),
\(A_\varepsilon(O):=\varepsilon^{-N/2}\int e^{\frac{i}{\varepsilon}f(x)}O(x)\,dx\).
Then
\(|A_\varepsilon(O)|^2=\varepsilon^{-N}\iint e^{\frac{i}{\varepsilon}(f(x)-f(y))}O(x)\overline{O(y)}\,dx\,dy\).
Under the near-diagonal scaling \(y=x+\varepsilon z\) (so
\(dy=\varepsilon^Ndz\)), one formally obtains
\(|A_\varepsilon(O)|^2\to (2\pi)^N\int \delta(\nabla f(x))\,|O(x)|^2\,dx\).
This exhibits the pattern ``density = \(|\text{amplitude}|^2\)'', with
the exponent \(N/2\) matching the half-density scaling needed to cancel
Jacobians under refinement.

\texttt{Derivation\ D3.5a\ (Nondegenerate\ critical\ points:\ why\ the\ weights\ are\ square\ roots).}
In one dimension, if \(f\) has finitely many nondegenerate critical
points \(x_i\) (so \(f'(x_i)=0\) and \(f''(x_i)\neq 0\)), then the
distributional identity \[
\delta(f'(x))=\sum_i \frac{\delta(x-x_i)}{|f''(x_i)|}
\] makes explicit that \(\delta(f')\,dx\) is a density supported on
stationary points with weights \(1/|f''|\). Stationary phase, by
contrast, gives amplitude contributions weighted by
\(1/\sqrt{|f''(x_i)|}\). This is the clean finite-dimensional reason the
``half-density first'' viewpoint is natural: amplitude weights are
square roots of density weights.

Section 6 recovers the same ``square-root Jacobian'' in the dynamical
setting: semigroup composition of short-time kernels forces the
characteristic \(t^{-d/2}\) normalization (Derivation D4.1a). (A
comprehensive treatment showing this exponent is forced across four
distinct settings --- temporal composition, Van Vleck determinant in
curved space, heat-kernel diffusion, and renormalization thresholds ---
is given in the companion satellite {[}PathIntegralNormalization{]}.)

In infinite-dimensional settings (paths), one is tempted to write
``formal measures'' supported on stationary-action trajectories. In this
manuscript we treat such expressions as roadmap heuristics until they
are regularized and made compatible with composition (Section 6); see
also \texttt{Heuristic\ H0.2a}. (A companion note on delta objects
collects the finite-dimensional scaling computations --- identity
kernel, stationary-set concentration, point interactions as rank-one
kernels --- and traces the Van Vleck determinant as the propagator
instance of the square-root Hessian.)

\texttt{Remark\ D3.5b\ (Delta-object\ dictionary\ and\ safe/unsafe\ criterion).}
Five delta-adjacent constructions appear in this work: (i) the
stationary-set delta \(\delta(\nabla f)\), which localizes on critical
points of a smooth function with Hessian-determinant weights (the
distributional change-of-variables formula); (ii) the distributional
derivative \(\delta'\), defined by duality and realizable as a
point-splitting limit; (iii) the diagonal delta kernel
\(\delta(x-y)|dx|^{1/2}|dy|^{1/2}\), the Schwartz kernel of the identity
on half-densities; (iv) the delta potential \(g\,\delta(x)\), a rank-one
perturbation that defines a self-adjoint extension in \(d\le3\) but
requires renormalization for \(d\ge2\); and (v) the heuristic
``\(\delta(\delta S)\)'' for extremal support on path space. The first
four are rigorous (with renormalization where noted); the fifth is
meaningful only as a shorthand for the finite-dimensional
stationary-phase identity combined with the composition-compatible
\(N\to\infty\) limit of Section 6. The safe/unsafe boundary is mollifier
universality: a delta construction is scheme-independent precisely when
it probes a continuous object, so that the mollifier-sequence limit is
unique; products of singular distributions or coincident-point
evaluations of singular kernels are scheme-dependent and require
explicit regularization.

\hypertarget{caveats-nonlinear-distribution-pitfalls}{%
\subsection{5.6 Caveats (Nonlinear Distribution
Pitfalls)}\label{caveats-nonlinear-distribution-pitfalls}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Products like \(\delta(t)^2\) are not defined in standard distribution
  theory; any appearance requires a regularization scheme and a proof of
  scheme-independence for claimed observables.
\item
  ``Evaluate at a point'' is only legitimate for quantities known to be
  continuous (or otherwise well-defined) at that point; mollifier
  probing must state this assumption explicitly.
\item
  Stationarity (\(\delta S=0\)) is not the same as minimality; second
  variation and convexity conditions are separate and are not assumed
  here.
\end{enumerate}

Transition to Section 6: we now have a controlled notion of ``extremal
classical dynamics'' (including impulses and corners) and a precise
language for refinement-local probes. The next section uses composition
under time slicing to motivate amplitude weights and the path integral.

\hypertarget{composition-and-path-integral}{%
\section{6. Composition and Path
Integral}\label{composition-and-path-integral}}

\hypertarget{composition-postulate-for-amplitudes}{%
\subsection{6.1 Composition Postulate for
Amplitudes}\label{composition-postulate-for-amplitudes}}

Let \(K(q_f,t_f;q_i,t_i)\) denote the transition amplitude. The
structural postulate is composition on intermediate time slices:

\[
K(q_f,t_f;q_i,t_i)
=\int dq\,K(q_f,t_f;q,t)\,K(q,t;q_i,t_i),
\qquad t_i<t<t_f.
\]

\texttt{Heuristic\ H4.0\ (Half-density\ kernels\ make\ composition\ measure-free).}
On a configuration manifold \(M\), the coordinate-free object underlying
the displayed formula is a \textbf{bi-half-density kernel}:
\(K_t(q',q)\in|\Lambda^dT^\ast_{q'}M|^{1/2}\otimes|\Lambda^dT^\ast_qM|^{1/2}\).
Then composition is the canonical pairing in the intermediate variable
\(q\), and it does not require choosing a background measure. Writing
\(\int dq\) is what one gets after choosing a reference density to
identify half-densities with scalar functions.

\texttt{Derivation\ D4.0\ (Coordinate\ invariance\ of\ composition\ via\ half-densities).}
In local coordinates \(q\), write
\(K_t(q',q)=k_t(q',q)\,|dq'|^{1/2}|dq|^{1/2}\). Then
\(K_{t_f-t}(q_f,q)\,K_{t-t_i}(q,q_i) =k_1k_2\,|dq_f|^{1/2}|dq|\,|dq_i|^{1/2}\)
is a density in \(q\), so \(\int_M K_{t_f-t}(q_f,q)K_{t-t_i}(q,q_i)\) is
coordinate invariant. This is the intrinsic meaning of the composition
postulate.

\texttt{Heuristic\ H4.0a\ (Scalarization\ gauge\ and\ scale).} Writing a
half-density kernel as an ordinary scalar function with an explicit
``\(dq\)'' implicitly chooses a reference density \(\rho_\ast\) on \(M\)
(equivalently a reference half-density \(\sigma_\ast=\rho_\ast^{1/2}\)).
Different choices are related by pointwise multiplication and give
unitarily equivalent scalar representations. If one additionally demands
scalar amplitudes be dimensionless, then \(\sigma_\ast\) must carry the
full \(\text{length}^{d/2}\) weight, so a universal choice of
\(\sigma_\ast\) is equivalent to choosing a universal
\(\text{length}^{d/2}\) scale. In a spacetime QFT setting where the
scalarization problem is formulated over an integration variable of
dimension \(D\), this is a \(\text{length}^{D/2}\) scale; in \(D=4\) it
is an area, with the Planck area \(\ell_P^2=\hbar G/c^3\) a natural
universal candidate. A companion note explores further (optional)
hypotheses about such scale suppliers; no such identification is
required for the present paper's structural chain.

\texttt{Heuristic\ H4.0b\ (Independent\ \textbackslash{}(D=4\textbackslash{})\ filter:\ operator\ simplicity\ under\ conformal\ scalarization\ changes).}
The ``scale supplier'' question above is distinct from a different way
\(D=4\) can appear once one insists on scalar representatives:
simplicity of how \emph{kinetic operators} depend on scalarization
choices. In a covariant/QFT setting (spacetime dimension \(D\)), the
scalar Laplacian \(\Delta_g\) induces an operator on half-densities by
conjugation, \[
\widetilde\Delta_g := |g|^{1/4}\Delta_g|g|^{-1/4}.
\] Under a conformal rescaling \(g=e^{2\sigma}\bar g\), the half-density
conjugation produces a quadratic-gradient term
\(\propto |\nabla\sigma|^2\) with universal coefficient \(D(4-D)/4\),
hence it cancels at \(D=4\) (within the conformal class). (To see this,
note that \(|g|^{1/4}=e^{D\sigma/2}|\bar g|^{1/4}\); conjugating
\(\Delta_g\) by \(e^{D\sigma/2}\) and using the conformal Laplacian
identity
\(\Delta_g\phi=e^{-2\sigma}[\Delta_{\bar g}\phi+(D{-}2)\bar g^{ij}\partial_i\sigma\,\partial_j\phi]\)
produces the potential
\(V_{\mathrm{HD}}=-\tfrac{D}{2}\Delta_{\bar g}\sigma+\tfrac{D(4-D)}{4}|\bar\nabla\sigma|^2\);
the coefficient \(\tfrac{D(4-D)}{4}=\tfrac{D^2}{4}-\tfrac{D(D-2)}{2}\)
collects the contributions from the chain rule applied to
\(e^{-D\sigma/2}\).) This is an operator-simplicity filter
(scale-neutral) and is independent of the coupling-dimension sieve
discussed above. (A companion satellite on half-densities in QFT
develops the full bi-half-density calculus for spacetime propagators and
Green functions, including the conformal-class expansion, the
normal-coordinate computation showing the universal conjugation
potential \(V=(1/6)R\) matches conformal coupling only at \(D=4\), and
the heat-kernel trace formula without extraneous \(\sqrt{|g|}\)
factors.)

\texttt{Heuristic\ H4.0c\ (RG-side\ echo:\ gauge-coupling\ marginality\ at\ \textbackslash{}(D=4\textbackslash{})).}
On the renormalization side, \(D=4\) is the unique dimension in which
1-form gauge couplings are marginal by power counting
(\([g^2]=\text{length}^{D-4}\)), and in which the classical Yang--Mills
action is conformally invariant (the action-density weight factor
\(e^{(D-4)\sigma}\) equals unity). Both this statement and the
half-density cancellation in H4.0b share the algebraic root \((D-4)=0\),
but they apply to different objects: the half-density version is
universal (independent of matter content), while the RG version is
coupling-specific (tied to the form degree of the gauge connection via
\(D=2(p+1)\) for a \(p\)-form field; \(p=1\) gives \(D=4\)). The
consistency of these two logically independent filters at \(D=4\) is a
nontrivial structural check: the half-density filter selects the
kinematic arena, and the RG filter constrains the dynamics within it.

\texttt{Derivation\ D4.1\ (Time\ slicing\ from\ repeated\ composition).}
Iterating the composition law over a partition
\(t_i=t_0<\cdots<t_N=t_f\) gives

\[
K(q_f,t_f;q_i,t_i)=
\int \prod_{k=1}^{N-1} dq_k
\prod_{k=0}^{N-1}
K_\Delta(q_{k+1},q_k;t_k),
\]

with \(q_0=q_i,\;q_N=q_f,\;\Delta t_k=t_{k+1}-t_k\), and \(K_\Delta\)
the short-time kernel.

\texttt{Derivation\ D4.1a\ (Semigroup\ fixes\ the\ \textbackslash{}(t\^{}\{-d/2\}\textbackslash{})\ normalization).}
On \(M=\mathbb R^d\), translation invariance suggests a bi-half-density
kernel of the form \(K_t(x,y)=k_t(x-y)\,|dx|^{1/2}|dy|^{1/2}\), so the
semigroup law becomes a scalar convolution: \(k_{t+s}=k_t*k_s\). Assume
a quadratic short-time phase and write \[
k_t(u)=A(t)\,\exp\!\left(\frac{i m}{2\hbar}\frac{\|u\|^2}{t}\right),
\] interpreting the Gaussian integral in Euclidean time (heat kernel)
and then analytically continuing, or with the usual \(i0\) prescription.
Then \[
(k_t*k_s)(u)=A(t)A(s)\int_{\mathbb R^d}
\exp\!\left(\frac{i m}{2\hbar}\left(\frac{\|u-v\|^2}{t}+\frac{\|v\|^2}{s}\right)\right)\,dv.
\] Completing the square yields \[
\frac{\|u-v\|^2}{t}+\frac{\|v\|^2}{s}
=\frac{\|u\|^2}{t+s}+\frac{t+s}{ts}\left\|v-\frac{s}{t+s}u\right\|^2,
\] so the convolution closes on the same family with \[
A(t+s)=A(t)A(s)\left(\frac{ts}{t+s}\right)^{d/2}\times(\text{phase}).
\] The unique solution (up to an overall constant phase) is
\(A(t)\propto t^{-d/2}\). Thus the exponent \(d/2\) is forced by
semigroup composition: it is the half-density ``square-root Jacobian''
needed for refinement-stable kernel composition. Imposing the delta
initial condition as \(t\to0^+\) fixes the remaining normalization
constant and forces \(\hbar\) into the prefactor (in standard flat-space
scalar conventions, \(A(t)=(m/2\pi i\hbar t)^{d/2}\) up to phase).

\texttt{Proposition\ P4.2\ (Necessity\ of\ an\ action-dimensional\ scale\ for\ composition-compatible\ refinement).}
Let \(M=\mathbb R^d\) with Lagrangian \(\mathcal L(q,\dot q,t)\) and
action \(S[q]=\int\mathcal L\,dt\) of dimension
\([S]=\mathrm{mass}\cdot\mathrm{length}^2\cdot\mathrm{time}^{-1}\).
Assume a family of transition kernels
\(\{K(q_f,t_f;q_i,t_i)\}_{t_f>t_i}\) satisfying: \textbf{(C)}
Composition (semigroup):
\(K(q_f,t_f;q_i,t_i)=\int_M dq\,K(q_f,t_f;q,t)K(q,t;q_i,t_i)\) for all
\(t_i<t<t_f\); \textbf{(L)} Local exponential weight:
\(K_{\Delta t}(q_f,q_i)=\mathcal N(\Delta t)\exp(c_0 S_{\mathrm{slice}})\)
for short times; \textbf{(I)} Identity:
\(K(q_f,t_f;q_i,t_i)\to\delta^{(d)}(q_f-q_i)\) as \(t_f\to t_i^+\);
\textbf{(D)} Dimensional homogeneity: \([K]=\mathrm{length}^{-d}\).
Then: (i) the normalization exponent is
\(\mathcal N(\Delta t)\propto(\Delta t)^{-d/2}\), uniquely determined by
composition closure (Derivation D4.1a); (ii) there exists a constant
\(\kappa\) with \([\kappa]=[\mathrm{action}]\) such that
\(\mathcal N(\Delta t)=(m/2\pi\kappa\Delta t)^{d/2}\) and
\(c_0=i/\kappa\) (or \(-1/\kappa\) in Euclidean signature), fixed by the
identity limit and dimensional analysis; (iii) \(\kappa\) cannot be
eliminated: setting \(\kappa\to0\) collapses composition to
Hamilton--Jacobi extremization, which has no distributional identity
limit (the composed kernel approaches
\(\delta(q_f-q_{\mathrm{cl}}(q_i))\), generically not
\(\delta(q_f-q_i)\) for \(t>0\)); setting \(\kappa\to\infty\) makes the
weight trivial and loses dynamical content. The scale \(\kappa\) is
therefore a necessary structural constant of any composition-compatible
refinement of action-based dynamics. (iv) The structural result is that
\(\kappa\) exists and is necessary; identifying \(\kappa=\hbar\) (a
physical identification with the empirically measured quantum of action,
not a further structural forcing) recovers the standard quantum
propagator with Feynman phase \(e^{iS/\hbar}\) and Van Vleck
normalization.

\texttt{Remark\ P4.2a\ (Consolidation\ of\ existing\ derivations).} The
proposition consolidates Derivation D4.1a (composition forces
\(t^{-d/2}\)), Derivation D4.2a (soft extremum requires \(\hbar>0\)),
Derivation PA-D1.2a/b (half-density identity kernel scaling in the
planck-area note), and the heat-kernel witness (five manifestations of
\(d/2\): identity kernel, heat trace, propagator Schwinger
parametrization, UV divergence degree, dimensional regularization
poles). It reorganizes existing results into a necessity statement
rather than introducing new mathematics.

\texttt{Remark\ P4.2a\textquotesingle{}\ (Literature\ precedents\ for\ composition-forced\ measure).}
The idea that composition (the semigroup law) constrains the
path-integral measure has three principal antecedents. DeWitt
{[}DeWitt1957{]} first identified the Van Vleck--Morette determinant
\(\Delta^{1/2}(x,y)\) as the required measure factor for path integrals
on curved spaces; the factor is a bi-half-density (it transforms as
\(|g(x)|^{1/4}|g(y)|^{1/4}\) under coordinate changes). Kleinert and
Chervyakov {[}KleinertChervyakov2000{]} derived \(\Delta^{1/2}\) from
the global semigroup property alone, showing that composition forces the
normalization without appeal to operator-ordering arguments---the
closest antecedent to the present derivation. Baldazzi, Percacci, and
Zanusso {[}BaldazziPercacciZanusso2021{]} showed that ``cutting and
gluing'' (composition across temporal boundaries) determines the
normalization of self-normalizing path integrals uniquely. Proposition
P4.2 extends these measure-level results to a necessity theorem for the
scale \(\kappa=\hbar\) itself, operating at the level of the kernel
functional equation and reducing the hypothesis set to composition plus
dimensional setup (Remarks P4.2c--h).

\texttt{Remark\ P4.2b\ (Connection\ to\ RCP).} The proposition is the
primary constructive witness of Proposition P10.1 (Refinement
Compatibility Principle): partition compatibility demands a parameter
update for composition to close. The fact that this parameter has
dimension of action is forced by the dimensional content of the
classical Lagrangian, making RCP not merely structural but
constructive---it tells you what the control parameter must be.

\texttt{Remark\ P4.2c\ (Hypothesis\ reduction:\ exponential\ weight\ is\ a\ theorem).}
Hypothesis \textbf{(L)} (local exponential weight) decomposes into two
parts: \textbf{(L\(_{\mathrm{loc}}\))} kernel dependence on classical
action only, and \textbf{(L\(_{\mathrm{exp}}\))} exponential form
\(W=\exp(c_0 S/\kappa)\). The exponential form is not an independent
assumption: for a translation-invariant free kernel
\(K_t(u)=N(t)W(mu^2/(2\kappa t))\), composition \textbf{(C)} in Fourier
space reduces to the multiplicative equation
\(\hat K_T(p)=\hat K_{t_1}(p)\hat K_{t_2}(p)\). Under continuity, the
unique solution is \(\log\hat K_t(p)=t\,\phi(p)\), which forces
\(\log\hat W_0(q)=\alpha q^2+\beta\) (quadratic), i.e.,
\(W=\exp(\text{quadratic})\). The functional equation admits no
continuous non-Gaussian solution. Thus \textbf{(L\(_{\mathrm{exp}}\))}
is a theorem of composition, not an axiom.

\texttt{Remark\ P4.2d\ (Hypothesis\ reduction:\ L\textbackslash{}\textquotesingle{}evy-\/-Khintchine\ obstruction\ closes\ the\ loophole).}
The remaining escape from Gaussian kernels is
L\textquotesingle evy-stable processes with characteristic exponent
\(\Psi(p)=-c|p|^\alpha\), \(\alpha\in(0,2]\). For these, dimensional
homogeneity \textbf{(D)} requires \([c]=[m]^a[\hbar]^b\). Matching
length, mass, and time exponents yields the consistency condition
\(-\alpha/2=1-\alpha\), which forces \(\alpha=2\) (Gaussian). For
\(\alpha\neq 2\), no combination of \(m\) and \(\hbar\) can build the
required coefficient \(c\). While all L\textquotesingle evy processes
satisfy the identity limit \textbf{(I)}, the discriminating hypothesis
is \textbf{(D)}: any kernel satisfying
\textbf{(C)}+\textbf{(I)}+\textbf{(D)} with dimensional constants
\(\{m,\hbar\}\) must be Gaussian. The effective hypothesis count for
Proposition P4.2 is therefore reduced from four to three: composition
\textbf{(C)}, identity limit \textbf{(I)}, and dimensional homogeneity
\textbf{(D)}.

\texttt{Remark\ P4.2e\ (Extensions:\ curved,\ interacting,\ and\ Lorentzian\ settings).}
The conclusions of Proposition P4.2 are not limited to free particles in
flat Euclidean space. Three independent extensions confirm robustness:
(1) \textbf{Curved configuration spaces.} On a Riemannian manifold
\((M,g)\), the short-time kernel involves the Van Vleck--Morette
determinant \(\Delta^{1/2}(x,y)\), which composes via the
DeWitt--Morette semigroup law. The \(d/2\) normalization exponent is
forced by the same functional equation; \(\Delta\) and \(\sqrt{|g|}\)
are geometric (metric-dependent) but \(\kappa\)-independent. The metric
provides no escape route from \(\kappa\)-necessity. (2)
\textbf{Interacting systems.} The Mehler kernel for the harmonic
oscillator \(V=\tfrac{1}{2}m\omega^2 q^2\) satisfies composition with
\(\sin\omega t\) replacing \(t\) as ``time function.'' The \(d/2\)
forcing is purely algebraic (dimension-counting), and the Seeley--DeWitt
coefficients \(a_n\) are composition-compatibility conditions, not
escape routes. Short-time extraction of \(a_1=-iV/\hbar\) confirms this.
(3) \textbf{Lorentzian signature.} Replacing Gaussian damping by
oscillatory Fresnel phase, the algebraic parts of the argument (\(d/2\)
exponent, \(\kappa=\hbar\) necessity, semigroup closure) are
signature-independent. The \(i\varepsilon\) prescription is itself a
theorem of composition: among regulators
\(\exp(-\varepsilon f((x-y)^2/t))\), only \(f(x)=x\) (linear) preserves
semigroup closure, and this uniqueness follows from degree-counting
(non-linear \(f\) produces non-Gaussian integrands). Composition
alone---without invoking the identity limit---forces the
\(i\varepsilon\) form.

\texttt{Remark\ P4.2f\ (Universality\ of\ \textbackslash{}(\textbackslash{}kappa\textbackslash{})\ across\ interacting\ sectors).}
Proposition P4.2 forces a scale \(\kappa\) with
\([\kappa]=[\text{action}]\) for each sector individually. If two
sectors (say particles \(A\) and \(B\)) interact, their joint kernel
must compose as a single semigroup. Under the single-exponential-weight
assumption, the joint kernel inherits a single \(\kappa\): factorization
into sector-specific \(\kappa_A\neq\kappa_B\) is incompatible with joint
composition when \(A\) and \(B\) are coupled. Decoupled
(non-interacting) sectors may in principle carry independent scales, but
transitivity of interaction in any connected physics makes
\(\kappa=\hbar\) universal across all interacting degrees of freedom.
This universality is not postulated but forced by composition.

\texttt{Remark\ P4.2g\ (Continuum\ time\ forced\ by\ dimensional\ homogeneity).}
Dimensional homogeneity \textbf{(D)} not only forbids jump processes
(Remark P4.2d) but also forces continuous time parametrization. A
discrete-time formulation with lattice spacing \(\varepsilon\) would
require \([\varepsilon]=T\), but in non-relativistic quantum mechanics
the dimensional basis is \(\{m,\hbar\}\). Seeking
\(\varepsilon=[m]^a[\hbar]^b\) yields \(M^{a+b}L^{2b}T^{-b}=T\);
matching exponents gives \(2b=0\) (length) and \(-b=1\) (time), hence
\(b=0\) and \(b=-1\) simultaneously---a contradiction. The root cause is
that \(\{m,\hbar\}\) span only a two-dimensional subspace of the
three-dimensional MLT dimension space, and the reachable dimensions
satisfy \([L]=[T^{-1/2}]\) (up to mass factors). Thus \textbf{(D)}
forbids external time scales, forcing the continuum limit
\(\varepsilon\to 0\). Proposition P4.2 therefore establishes not only
the necessity of a finite action scale \(\kappa=\hbar\), but also the
necessity of continuous time as the composition parameter. (Lattice
formulations in QFT introduce \(\varepsilon\) as an external UV
regulator; their validity depends on controlled \(\varepsilon\to 0\)
limits, consistent with this obstruction.)

\texttt{Remark\ P4.2h\ (Composition\ as\ single\ master\ axiom).} The
axiom reduction of Remarks P4.2c-g can be pushed further. Hypothesis
\textbf{(D)} (dimensional homogeneity) is itself a theorem of
\textbf{(C)} (composition) on \(\mathbb{R}^d\): the composition integral
\(\int K(x,z;t_1)\,K(z,y;t_2)\,d^d z = K(x,y;t_1+t_2)\) forces
\([K]=L^{-d}\) by dimensional consistency, and the remaining content of
\textbf{(D)} is either trivially true for Lagrangian theories or a
property of the physical setup. Similarly, hypothesis \textbf{(I)}
(identity limit) is derivable: the explicit Gaussian kernel forced by
\textbf{(C)} is a nascent delta family, so \(K(x,y;t) \to \delta(x-y)\)
as \(t \to 0\) is a theorem. For general potentials, Stone's theorem
yields the same conclusion given a self-adjoint generator. \textbf{The
effective hypothesis count for Proposition P4.2 is therefore one
mathematical axiom (composition) plus the physical setup} (action-based
dynamics on \(\mathbb{R}^d\) with mass \(m\) and self-adjoint
Hamiltonian). Composition is the single master axiom for the partition
channel. (Scope caveat: the clean hypothesis reduction via the Cauchy
functional equation (P4.2c) and Lévy--Khintchine exclusion (P4.2d) is
established rigorously for the translation-invariant free case on
\(\mathbb{R}^d\). The extensions to curved, interacting, and Lorentzian
settings (Remark P4.2e) proceed by a different route ---
semiclassical/Van Vleck/operator-theoretic --- that invokes stronger
hypotheses than composition alone. The ``single master axiom'' label
applies without qualification only to the flat free case; the extended
cases share the same conclusion but via additional input.) See
{[}RCPFoundations{]} Section 6 for the full axiom-reduced formulation.

\texttt{Remark\ P4.2i\ (Parallel\ reconstruction:\ information-theoretic\ route).}
Luiz and de Oliveira {[}LuizOliveira2026{]} independently arrive at
overlapping conclusions via a different starting point: a density of
action states \(g(A;b,T|a)\) satisfying a composition law in action
space, finite variance, and locality. Their Proposition 1 derives the
Gaussian form via the same Lévy--Khintchine exclusion, and their \(d/2\)
exponent matches ours. Their route additionally derives complex
amplitudes from Cramér--Rao indistinguishability---a step we assume (the
exponential weight is here forced by the Cauchy functional equation,
Section 6.2). Conversely, our approach yields the groupoid reading
(Section 8), the RCP three-channel framework (Section 9), and the
deformation-quantization bridge {[}TangentGroupoidBridge{]}, none of
which appear in {[}LuizOliveira2026{]}. The shared core---convolution
semigroup structure forces an action-dimensional scale---is standard
mathematics (the Lévy--Khintchine theorem applied to propagator
kernels); the convergence of two independent lines of argument
strengthens the case that composition is the operative principle. A
complementary \emph{kinematic} derivation by Goyal, Knuth, and Skilling
{[}GoyalKnuthSkilling2010{]} shows that composition of sequential
measurement amplitudes, together with continuity, forces complex
arithmetic and the Born rule---recovering Feynman's sum and product
rules without postulating complex amplitudes. Where
{[}LuizOliveira2026{]} and the present work derive \emph{dynamical}
structure (\(\hbar\), Gaussian kernels), {[}GoyalKnuthSkilling2010{]}
derives \emph{algebraic} structure (the complex field); the three
results are complementary instances of the composition-forcing
programme. The GKS framework has been extended to a
coordinate-independent classification of allowable amplitude algebras
(complex and quaternionic) via Hurwitz's composition-algebra theorem,
deriving the Born rule without postulating the complex field
{[}Köplinger2025{]}.

\hypertarget{from-additive-action-to-multiplicative-weights}{%
\subsection{6.2 From Additive Action to Multiplicative
Weights}\label{from-additive-action-to-multiplicative-weights}}

The Section 4/Section 5 structure gives an additive discrete action:

\[
S_N[q]=\sum_{k=0}^{N-1}\mathcal L\!\left(q_k,\frac{q_{k+1}-q_k}{\Delta t_k},t_k\right)\Delta t_k.
\]

Assume short-time locality: each slice contributes a factor depending
only on local step data. Write

\[
K_\Delta(q_{k+1},q_k;t_k)=\mathcal N_k\,W_k.
\]

\texttt{Proposition\ P4.1\ (Exponential\ form\ under\ locality\ +\ composition).}
If 1. total path weight is multiplicative across concatenated slices,
and 2. \(\log W_k\) is additive in \(\Delta t_k\) to first order
(equivalently,
\(W_k = \exp(c_0 \mathcal{L}_k \Delta t_k + O(\Delta t^2))\); the
derivation that composition \emph{forces} this form via the Cauchy
functional equation is in Remark P4.2c),

then, up to normalization and higher-order slicing corrections,

\[
\prod_{k=0}^{N-1}W_k
\propto
\exp\!\big(c_0\,S_N[q]\big),
\]

for a constant \(c_0\) with dimensions \([\text{action}]^{-1}\).

Choosing oscillatory quantum time evolution gives \(c_0=i/\hbar\) (the
necessity of this scale --- dimensional homogeneity forces
\([c_0]=[\text{action}]^{-1}\) and the identity limit pins the
coefficient --- is derived in Proposition P4.2(ii)), hence the standard
phase factor \(\exp(iS_N/\hbar)\) {[}Dirac1933{]} {[}Feynman1948{]}.

\hypertarget{ordering-discretization-and-quantum-ambiguity}{%
\subsection{6.3 Ordering, Discretization, and Quantum
Ambiguity}\label{ordering-discretization-and-quantum-ambiguity}}

Different short-time discretizations (left/right/midpoint or more
general \(\alpha\)-schemes) typically correspond to different operator
orderings. In deformation language, this is the same ambiguity as
choosing a star-product representative; these constructions agree in the
classical limit but can differ at subleading quantum order
{[}Landsman1998{]} {[}deGosson2018ShortTimePropagators{]}.

\texttt{Heuristic\ H4.1\ (Same\ classical\ limit,\ different\ quantum\ corrections).}
Two discretizations that differ by \(O(\Delta t)\) in each slice can
produce equivalent classical equations while shifting \(O(\hbar)\) terms
in quantum generators. Thus ordering is a controlled modeling choice,
not a contradiction.

\texttt{Derivation\ D4.1b\ (Ordering\ witness:\ \textbackslash{}(H=qp\textbackslash{})\ under\ \textbackslash{}(\textbackslash{}alpha\textbackslash{})-discretization).}
For the classical Hamiltonian \(H(q,p)=qp\), the phase-space path
integral with \(\alpha\)-prescription (evaluating position at
\(q_\alpha=(1-\alpha)q_k+\alpha q_{k+1}\) in each slice) produces the
operator
\[\hat H_\alpha=\alpha\hat q\hat p + (1-\alpha)\hat p\hat q = \hat p\hat q + \alpha\,i\hbar.\]
To verify: the matrix element
\(\langle q'|\hat H_\alpha|q\rangle = [\alpha q'+(1-\alpha)q](-i\hbar)\delta'(q'-q) = q_\alpha(-i\hbar)\delta'(q'-q)\),
which matches the kernel's \(\alpha\)-interpolated integrand order by
order in \(\Delta t\). At \(\alpha=0\) (prepoint) this is anti-standard
ordering \(\hat p\hat q\); at \(\alpha=1/2\) (midpoint) it is the
Weyl-symmetric form \(\tfrac12(\hat q\hat p+\hat p\hat q)\) connected to
the Moyal product of Section 7; at \(\alpha=1\) (postpoint) it is
standard ordering \(\hat q\hat p=\hat p\hat q+i\hbar\). All three share
the classical limit \(H=qp\); the \(O(\hbar)\) corrections are
discretization artifacts controlled by \(\alpha\). This is the simplest
instance of the general \(f(q)p\) family treated in Section 10.2.

\texttt{Remark\ D4.1c\ (Symmetry\ selects\ the\ midpoint).} In the
position representation
\(\hat H_\alpha=-i\hbar(q\tfrac{d}{dq}+(1-\alpha))\) on
\(L^2(\mathbb R,dq)\), the formal symmetry defect is
\(\langle u,\hat H_\alpha v\rangle - \langle\hat H_\alpha u,v\rangle = i\hbar(2\alpha-1)\langle u,v\rangle\)
for test functions with compact support away from \(q=0\). This vanishes
if and only if \(\alpha=1/2\). The logical chain is: unitarity of the
generated group requires self-adjointness of the generator,
self-adjointness requires symmetry, and symmetry selects \(\alpha=1/2\).
Essential self-adjointness (closure to a unique self-adjoint extension)
additionally depends on the configuration space: it holds automatically
on \(\mathbb R_+\) via the dilation group but requires choosing a
self-adjoint extension on \(\mathbb R\) where the singularity at \(q=0\)
creates deficiency indices \((1,1)\). The \(\alpha=1/2\) selection
itself is a purely algebraic consequence of the \(L^2\) inner product
and is independent of these domain subtleties.

\texttt{Remark\ D4.1d\ (Discretization-stochastic\ dictionary:\ Itô\ vs\ Stratonovich).}
The \(\alpha\)-discretization maps directly to stochastic calculus
conventions. For an \(N\)-impulse model with position-dependent random
impulses \(J_k=\sigma(q_k^\ast)\sqrt{\Delta t}\,\xi_k\) (where \(\xi_k\)
are i.i.d. standard normals and \(q_k^\ast\) is the evaluation point),
the three standard discretizations correspond to: \(\alpha=0\) (prepoint
\(q_k^\ast=q_k\)) yields the Itô integral; \(\alpha=1/2\) (midpoint
\(q_k^\ast=(q_k+q_{k+1})/2\)) yields the Stratonovich integral;
\(\alpha=1\) (postpoint \(q_k^\ast=q_{k+1}\)) yields the anti-Itô or
backward integral. The Stratonovich-to-Itô conversion formula adds a
correction term \(\tfrac12\sigma(q)\sigma'(q)\,dt\) to the drift, which
has the same structural origin as the \(\alpha\)-dependent \(O(\hbar)\)
shift in the quantum Hamiltonian: both are ``chain-rule corrections''
arising from moving the evaluation point in a context where increments
have \(O(\sqrt{\Delta t})\) fluctuations. The Stratonovich convention
preserves the classical chain rule and the variational impulse-work
formula; the Itô convention has better martingale properties but breaks
manifest symmetry. This is not a claim that path integrals ``are''
stochastic processes, but rather that discretization conventions and
their \(O(\hbar)\) or \(O(\Delta t)\) corrections map across both
formalisms.

\texttt{Remark\ D4.1e\ (Composition\ selects\ half-density,\ not\ midpoint,\ on\ curved\ manifolds).}
On flat configuration space \(\mathbb{R}^d\), the midpoint
discretization (\(\alpha=1/2\), Weyl ordering, Stratonovich convention)
and the half-density conjugation \(|g|^{1/4}(-\Delta_g)|g|^{-1/4}\)
produce operators that agree on the principal symbol and connection
terms, differing only in an \(O(\hbar^2)\) scalar potential
(\texttt{Remark\ D9.1a}). On curved Riemannian manifolds, however, these
two selections diverge. The midpoint/Stratonovich prescription produces
a scalar curvature coupling \(\xi_W = 1/8\) (i.e.~\(V = R/8\)), while
the half-density conjugation produces \(V_{\mathrm{HD}} = -R/6\) at each
Riemann normal coordinate center (\texttt{Remark\ D9.1l}). The
composition law takes precedence: the Van Vleck--Morette determinant
that appears in the semiclassical kernel (\texttt{Derivation\ D4.3})
transforms as a bi-half-density, and kernel composition requires the
\(|g|^{1/4}\) prefactor, not the midpoint evaluation point. (This step
uses the additional assumption that the kinetic operator is defined by
the half-density conjugation
\(\Delta_{1/2}=|g|^{1/4}(-\Delta_g)|g|^{-1/4}\); composition determines
the measure coefficient universally via Proposition P4.2, and the
conjugation then specifies the corresponding operator ordering. On
general manifolds the half-density \(|g|^{1/4}\) has no unique algebraic
origin beyond P4.2 itself, in contrast to the Lie group case where it
coincides with the Duflo factor,
\texttt{Remark\ D9.1o\textquotesingle{}}.) Thus the hierarchy of
selection principles on curved manifolds is: composition (half-density,
\(R/6\)) \(\supset\) symmetry (midpoint, \(R/8\)) \(\supset\) classical
limit (any \(\alpha\)). The first two coincide on flat space where all
curvature couplings vanish.

\hypertarget{formal-continuum-limit-and-stationary-phase}{%
\subsection{6.4 Formal Continuum Limit and Stationary
Phase}\label{formal-continuum-limit-and-stationary-phase}}

\texttt{Heuristic\ H4.2a\ (Formal\ continuum-limit\ expression).}
Formally, as mesh size \(\max_k\Delta t_k\to0\):

\[
K(q_f,t_f;q_i,t_i)\sim
\int_{q_i}^{q_f}\mathcal Dq\;
\exp\!\left(\frac{i}{\hbar}S[q]\right).
\]

This expression is formal at this stage: we do not claim a countably
additive measure construction on full path space. (For an explicit
regulated-kernel family with exact composition and controlled regulator
removal in the Euclidean free and harmonic-oscillator models, see
Appendix 10.6.)

\texttt{Derivation\ D4.2\ (Classical\ recovery\ mechanism).} Let
\(q=q_{\mathrm{cl}}+\xi\), where \(q_{\mathrm{cl}}\) is stationary:
\(\delta S[q_{\mathrm{cl}};\eta]=0\). Expand:

\[
S[q_{\mathrm{cl}}+\xi]
=S[q_{\mathrm{cl}}]
+\frac12\langle \xi,\mathcal H_{q_{\mathrm{cl}}}\xi\rangle
+O(\xi^3).
\]

Fast phase oscillations cancel nonstationary contributions, while
neighborhoods of stationary paths contribute coherently. This is the
precise sense in which the classical equations reappear as \(\hbar\to0\)
asymptotics.

\texttt{Derivation\ D4.2a\ (Soft\ extremum\ and\ why\ a\ finite\ \textbackslash{}(\textbackslash{}hbar\textbackslash{})\ stabilizes\ refinement).}
Even before any infinite-dimensional measure issues, the
refinement-composition pattern forces a ``softened'' version of
extremization. Consider a finite-dimensional two-slice action
\(S(q_2,q_1)+S(q_1,q_0)\) and form the Euclideanized composed weight \[
W_\hbar(q_2,q_0):=\int dq_1\;\exp\!\left(-\frac{1}{\hbar}\big(S(q_2,q_1)+S(q_1,q_0)\big)\right).
\] Define the associated coarse effective action (a log-partition
functional) \[
S_{\mathrm{eff}}^{(\hbar)}(q_2,q_0):=-\hbar\ln W_\hbar(q_2,q_0).
\] Then refinement-composition is exact at the level of weights (add
actions in the exponent, integrate the intermediate variable), and the
hard elimination/extremization rule appears only as the sharpening
limit: under standard nondegeneracy assumptions, Laplace's method gives
\[
S_{\mathrm{eff}}^{(\hbar)}(q_2,q_0)
\xrightarrow{\hbar\to0}
\inf_{q_1}\big(S(q_2,q_1)+S(q_1,q_0)\big),
\] with \(O(\hbar)\) corrections determined by local quadratic data near
the minimizer(s). So \(\hbar\) plays the role of a universal control
parameter that makes ``refine then compare'' stable, with classical
extremals recovered as a limit. In real time, the same pattern appears
with \(e^{iS/\hbar}\) and stationary phase in place of positivity and
Laplace concentration.

\texttt{Example\ D4.2b\ (Free-particle\ two-slice\ integral:\ explicit\ classical\ recovery).}
For a free particle of mass \(m\), the two-slice action is
\(S=\frac{m}{2\Delta t}\bigl[(q_2-q_1)^2+(q_1-q_0)^2\bigr]\). Completing
the square gives
\(S=\frac{m}{4\Delta t}(q_2-q_0)^2+\frac{m}{\Delta t}(q_1-\bar q)^2\)
with \(\bar q=(q_0+q_2)/2\). The Euclideanized weight integral is
Gaussian: \[
W_\hbar(q_2,q_0)=\sqrt{\frac{\pi\hbar\Delta t}{m}}\;\exp\!\left(-\frac{m(q_2-q_0)^2}{4\hbar\Delta t}\right),
\] giving the coarse effective action \[
S_{\mathrm{eff}}^{(\hbar)}(q_2,q_0)=\frac{m(q_2-q_0)^2}{4\Delta t}+\frac\hbar2\ln\!\frac{m}{\pi\hbar\Delta t}.
\] As \(\hbar\to0\),
\(S_{\mathrm{eff}}^{(\hbar)}\to\inf_{q_1}S=\frac{m(q_2-q_0)^2}{4\Delta t}\)
with a subleading \(O(\hbar\ln\hbar)\) correction from the Gaussian
width. This makes the classical-recovery mechanism of D4.2a fully
explicit: the extremal path (\(q_1=\bar q\), uniform velocity) is
selected by sharpening, with no additional hypotheses.

\texttt{Remark\ D4.2c\ (Delocalized\ angles\ in\ angular-momentum\ eigenstates).}
The stationary-phase mechanism explains how classical trajectories
reappear in semiclassical packets. It does not imply that a single
stationary eigenstate is a localized classical orbit. A simple witness
occurs already in central potentials: in polar coordinates the azimuthal
angle \(\phi\) is conjugate to \(L_z\), and separation of variables
yields {[}TongQMLectures{]} \[
\psi(r,\phi)=R(r)\,e^{im\phi}.
\] Therefore \[
|\psi(r,\phi)|^2=|R(r)|^2
\] is independent of \(\phi\), i.e.~the azimuthal angle is uniformly
distributed in an \(L_z\) eigenstate. Localized ``orbit phase'' pictures
correspond to coherent superpositions/wavepackets, consistent with the
manuscript's use of stationary-phase concentration rather than
``eigenstate \(=\) orbit'' identification. (A companion note on
action-angle indeterminacy expands this observation to a second witness
--- the harmonic oscillator, where Fock states delocalize the orbit
phase while coherent states --- superpositions spread across many Fock
modes --- localize it, with decoherence dynamically selecting the
localized packets --- and formulates the general structure as an
uncertainty relation between action and angle variables.)

\texttt{Derivation\ D4.3\ (Van\ Vleck\ prefactor\ is\ a\ bi-half-density).}
In the semiclassical approximation, the endpoint kernel has the standard
form \[
K(q_f,t_f;q_i,t_i)\approx
\frac{1}{(2\pi i\hbar)^{d/2}}
\left|\det\!\left(-\frac{\partial^2 S_{\mathrm{cl}}}{\partial q_f\,\partial q_i}\right)\right|^{1/2}
\exp\!\left(\frac{i}{\hbar}S_{\mathrm{cl}}(q_f,t_f;q_i,t_i)\right),
\] where \(S_{\mathrm{cl}}\) is the classical action evaluated on the
stationary path with those endpoints. Under changes of coordinates
\(q_f=q_f(q_f')\), \(q_i=q_i(q_i')\), the mixed Hessian transforms by
the chain rule, and \[
\det\!\left(-\frac{\partial^2 S_{\mathrm{cl}}}{\partial q_f'\,\partial q_i'}\right)
=
\det\!\left(\frac{\partial q_f}{\partial q_f'}\right)
\det\!\left(\frac{\partial q_i}{\partial q_i'}\right)
\det\!\left(-\frac{\partial^2 S_{\mathrm{cl}}}{\partial q_f\,\partial q_i}\right).
\] Taking square roots yields a factor
\(|\det(\partial q_f/\partial q_f')|^{1/2}|\det(\partial q_i/\partial q_i')|^{1/2}\),
so the prefactor transforms as a half-density in each endpoint variable.
This is the concrete semiclassical origin of the half-density viewpoint
in \texttt{Heuristic\ H4.0}. For an early
semiclassical/correspondence-principle anchor in the ``Van Vleck''
tradition, see {[}VanVleck1928Correspondence{]}. For a modern OA
statement of the Van Vleck propagator/prefactor and the associated ``Van
Vleck density'', see {[}deGosson2018ShortTimePropagators{]}. An explicit
finite-dimensional quadratic-elimination template (Schur complement)
shows how mixed endpoint Hessians arise in time slicing; we omit it
here.

\texttt{Remark\ D4.3a\ (Caustics\ and\ the\ Maslov\ index).} At caustics
(conjugate points where the Van Vleck determinant \(D\to\infty\)), the
semiclassical approximation appears to break down: the amplitude
\(|D|^{1/2}\) diverges and \(\sqrt{D}\) changes sign. In the
half-density framework the singularity is a projection artifact: the
semiclassical state is a smooth half-density on the Lagrangian
submanifold \(L\subset T^\ast M\), and the caustic occurs because the
projection \(\pi:L\to M\) develops a fold {[}BatesWeinstein1997{]}. The
sign ambiguity of \(\sqrt{D}\) is resolved by the metaplectic structure:
half-densities transform under the double cover \(\mathrm{Mp}(2n)\) of
\(\mathrm{Sp}(2n)\), and the Maslov index \(\mu\) --- counting conjugate
points along the classical path --- records the accumulated phase
correction \(e^{-i\pi\mu/2}\). This makes the ``amplitudes are
half-densities'' pattern of Section 3.3 precise: the Van Vleck prefactor
is not a scalar but a section of a metalinear bundle, globally
well-defined even through caustics.

\hypertarget{link-back-to-section-5-singular-dynamics}{%
\subsection{6.5 Link Back to Section 5 Singular
Dynamics}\label{link-back-to-section-5-singular-dynamics}}

The composition picture naturally includes piecewise-smooth
trajectories. At impulses, the dominant classical skeleton must satisfy
the jump laws from Section 5:

\[
\left[\frac{\partial\mathcal L}{\partial\dot q}\right]_{t_0^-}^{t_0^+}=J
\quad\text{(impulse)}
\qquad
\left[\frac{\partial\mathcal L}{\partial\dot q}\right]_{t_0^-}^{t_0^+}=0
\quad\text{(corner, unforced)}.
\]

So the ``extremal set'' entering semiclassical evaluation is broader
than globally smooth trajectories; it includes admissible broken
trajectories obeying the correct matching conditions.

\texttt{Derivation\ D6.5\ (Impulse-kick\ kernel:\ composition\ produces\ the\ jump\ law).}
For a free particle on \(\mathbb R\) subject to a single instantaneous
impulse \(J\) at time \(t_0\in(0,T)\), the propagator factorizes through
the composition integral

\[
K_J(x_f,T;x_i,0)=\int dy\;K_{\mathrm{free}}(x_f,T;y,t_0)\,e^{iJy/\hbar}\,K_{\mathrm{free}}(y,t_0;x_i,0),
\]

where the phase \(e^{iJy/\hbar}\) encodes the impulse action
\(J\cdot q(t_0)\). Completing the Gaussian integral gives:

\[
K_J=K_{\mathrm{free}}(x_f,T;x_i,0)\;\exp\!\Bigl[\frac{iJ\,\bar x(t_0)}{\hbar}-\frac{iJ^2\,t_0(T-t_0)}{2m\hbar T}\Bigr],
\]

with \(\bar x(t_0)=x_i+(x_f-x_i)t_0/T\) the unforced classical midpoint.
The saddle point \(y^\ast=\bar x(t_0)-Jt_0(T-t_0)/(mT)\) satisfies
\(\Delta p=m(x_f-y^\ast)/(T-t_0)-m(y^\ast-x_i)/t_0=J\), recovering the
Weierstrass--Erdmann impulse condition of Section 5 as a \emph{derived
consequence} of stationarity, not an additional input. The limits
\(J\to 0\) (free particle) and \(J\to\infty\) (decoupling) are both
physically correct.

Transition to Section 7: with composition, weighting, and
classical-recovery logic in place, we can now present quantization as
deformation of algebraic products, linking path-integral discretization
choices to tangent/cotangent groupoid deformation structure.

\hypertarget{deformation-quantization-bridge}{%
\section{7. Deformation Quantization
Bridge}\label{deformation-quantization-bridge}}

\hypertarget{from-path-weights-to-product-deformation}{%
\subsection{7.1 From Path Weights to Product
Deformation}\label{from-path-weights-to-product-deformation}}

Section 6 established that discretized composition introduces nonunique
short-time prescriptions (left/right/midpoint and related schemes). The
algebraic restatement is: quantization should deform the classical
product of observables rather than replace classical mechanics by
unrelated objects {[}Landsman1998{]} {[}Connes1994{]}.

Let \(M\) be phase space with Poisson bracket \(\{\cdot,\cdot\}\), and
let \(\mathcal A_0\) be a commutative algebra of classical observables
(e.g., smooth functions with suitable decay/domain conditions). A
deformation quantization is a family of associative products
\(\star_\hbar\) on \(\mathcal A_0\) such that:

\[
f\star_\hbar g
=
fg+\sum_{n\ge 1}\hbar^n B_n(f,g),
\]

where \(B_n\) are bilinear operators, with \(f\star_0 g=fg\).

\texttt{Proposition\ P5.1\ (Classical\ compatibility\ conditions).} If
\(\star_\hbar\) is associative for each \(\hbar\) and depends
smoothly/formally on \(\hbar\), then the antisymmetric part of \(B_1\)
controls the leading noncommutativity:

\[
[f,g]_{\star_\hbar}
\equiv
f\star_\hbar g-g\star_\hbar f
=
\hbar\big(B_1(f,g)-B_1(g,f)\big)+O(\hbar^2).
\]

So first-order noncommutativity is fully determined by
\(B_1^{\mathrm{anti}}\).

\hypertarget{commutator-to-poisson-recovery}{%
\subsection{7.2 Commutator-to-Poisson
Recovery}\label{commutator-to-poisson-recovery}}

\texttt{Derivation\ D5.1\ (Correspondence\ limit).} Impose the
correspondence requirement that first-order antisymmetry matches the
Poisson bracket:

\[
B_1(f,g)-B_1(g,f)=i\,\{f,g\}.
\]

Then

\[
[f,g]_{\star_\hbar}
=
i\hbar\,\{f,g\}+O(\hbar^2),
\]

and therefore

\[
\lim_{\hbar\to0}
\frac{1}{i\hbar}[f,g]_{\star_\hbar}
=
\{f,g\}.
\]

Dimensional closure: \([\hbar]=[\text{action}]\), while \(\{f,g\}\)
carries one inverse action factor relative to \(fg\) in canonical
coordinates, so \(i\hbar\{f,g\}\) has the same physical dimension as
\(fg\). This is the same unit-consistency condition already used in
Section 6 for \(\exp(iS/\hbar)\).

\hypertarget{concrete-model-and-ordering-content}{%
\subsection{7.3 Concrete Model and Ordering
Content}\label{concrete-model-and-ordering-content}}

For flat phase space, the Moyal product provides an explicit
representative:

\[
(f\star_M g)(q,p)
=
f(q,p)\exp\!\left[
\frac{i\hbar}{2}
\left(
\overleftarrow{\partial_q}\overrightarrow{\partial_p}
-\overleftarrow{\partial_p}\overrightarrow{\partial_q}
\right)\right]g(q,p),
\]

which reproduces the Poisson bracket at leading order and higher quantum
corrections at higher orders {[}Groenewold1946ElementaryQM{]}
{[}Moyal1949StatisticalQM{]} {[}Landsman1998{]}.

\texttt{Derivation\ D5.1a\ (Moyal\ product\ for\ linear\ and\ quadratic\ observables).}
For the canonical pair \(f=q\), \(g=p\), the exponential terminates at
first order (all higher derivatives vanish): \[
(q\star_M p)(q,p)
=qp+\frac{i\hbar}{2}(\partial_q q)(\partial_p p)
=qp+\frac{i\hbar}{2}.
\] By symmetry, \((p\star_M q)=pq-\frac{i\hbar}{2}\), so
\([q,p]_{\star_M}=i\hbar\), exactly reproducing the canonical
commutation relation with no higher-order corrections (as expected for
linear functions).

For \(f=q^2\), \(g=p\), the second-order derivative
\(\partial_q^2(q^2)=2\) is constant, but it multiplies
\(\partial_p^2 p=0\), so the expansion again terminates at first order:
\[
(q^2\star_M p)=q^2p+\frac{i\hbar}{2}(2q)(1)=q^2p+i\hbar\,q.
\] Thus \([q^2,p]_{\star_M}=2i\hbar\,q\), matching
\([\hat q^2,\hat p]=2i\hbar\,\hat q\) in Weyl ordering. More generally,
\([q^n,p]_{\star_M}=ni\hbar\,q^{n-1}\), recovering the Leibniz rule for
the Poisson bracket \(\{q^n,p\}=nq^{n-1}\) at leading order with no
further corrections.

\texttt{Derivation\ D5.1b\ (Cubic\ witness:\ genuine\ \textbackslash{}(O(\textbackslash{}hbar\^{}3)\textbackslash{})\ correction\ in\ the\ Moyal\ bracket).}
For pure monomials \(f=q^m\), \(g=p^n\), all cross-derivatives vanish
(\(\partial_p q^m=\partial_q p^n=0\)), so the Moyal product terminates
at order \(\min(m,n)\) in \(\hbar\):
\[[q^m,p^n]_{\star_M}=\sum_{\substack{k=1\\k\;\mathrm{odd}}}^{\min(m,n)}\frac{2(i\hbar/2)^k}{k!}\,\frac{m!\,n!}{(m\!-\!k)!\,(n\!-\!k)!}\,q^{m-k}p^{n-k}.\]
When \(\min(m,n)\le 2\) only the \(k=1\) term contributes, giving
\(i\hbar\{q^m,p^n\}\) exactly --- the Poisson bracket suffices, as
verified in D5.1a. The first case requiring a higher term is \(m=n=3\):
the \(k=1\) term gives \(9i\hbar\,q^2p^2=i\hbar\{q^3,p^3\}\), and the
\(k=3\) term gives \(2(i\hbar/2)^3/3!\cdot(3!)^2=-\tfrac32\,i\hbar^3\),
so \[[q^3,p^3]_{\star_M}=i\hbar\{q^3,p^3\}-\tfrac32\,i\hbar^3.\] The
constant \(-\tfrac32 i\hbar^3\) is a genuine quantum correction that
cannot be recovered from the Poisson bracket. This makes the cubic pair
the simplest witness that deformation quantization goes beyond a
re-encoding of the Poisson algebra.

\texttt{Heuristic\ H5.1\ (Ordering\ as\ deformation\ gauge\ choice).}
The Section 6 discretization ambiguity is naturally interpreted as
choosing different but deformation-equivalent star products; they share
the same classical bracket data but differ in \(O(\hbar)\) and higher
corrections {[}Landsman1998{]}.

\hypertarget{equivalence-classes-and-groupoid-viewpoint}{%
\subsection{7.4 Equivalence Classes and Groupoid
Viewpoint}\label{equivalence-classes-and-groupoid-viewpoint}}

\texttt{Proposition\ P5.2\ (Equivalent\ star\ products,\ same\ classical\ limit).}
If two products \(\star_\hbar\) and \(\star'_\hbar\) are related by a
formal automorphism

\[
T_\hbar=\mathrm{id}+\hbar T_1+O(\hbar^2),
\qquad
f\star'_\hbar g
=
T_\hbar^{-1}\!\big((T_\hbar f)\star_\hbar(T_\hbar g)\big),
\]

then they define the same Poisson bracket in the \(\hbar\to0\) limit,
while generally differing in subleading quantum terms.

This is the algebraic side of the same continuity narrative:
quantization data are organized into equivalence classes compatible with
one classical limit. Geometric deformation programs (including
tangent-groupoid viewpoints) encode the same bridge from commutative
classical data to noncommutative quantum products {[}Connes1994{]}. (A
companion satellite develops the tangent-groupoid bridge explicitly: the
pair groupoid encodes the sewing law, Connes' tangent groupoid
interpolates between classical and quantum composition, and the
resulting \(\hbar\)-deformation recovers the path-integral kernel as a
groupoid convolution {[}TangentGroupoidBridge{]}.)

\texttt{Remark\ P5.2a\ (Deformation\ equivalence\ is\ physical,\ not\ merely\ formal).}
The formal-automorphism statement of Proposition P5.2 is not purely
asymptotic: explicit calculations for a position-dependent mass
\(f(q)=1+\alpha q^2\) in a harmonic trap show that different
prescriptions (Weyl, half-density conjugation) agree exactly on the
principal symbol (Layer 1) and the first-derivative connection term
(Layer 2), differing only in an \(O(\hbar^2)\) scalar potential (Layer
3). The resulting ground-state energy shift between prescriptions is
\(|\Delta E_0|=\hbar\omega\alpha_0^2/16\), where \(\alpha_0\) is
dimensionless mass variation at the oscillator scale. For realistic
semiconductor heterostructures (GaAs quantum wells,
\(\hbar\omega\sim 10\) meV, \(\alpha_0\lesssim 0.3\)), this gives
\(|\Delta E_0|\lesssim 0.06\) meV, well below current spectroscopic
resolution (\(\sim 0.1\) meV). The four-layer stratification and the
explicit energy estimate are detailed in Appendix \S,10.2
(\texttt{Remark\ D9.1a}). The physical content of deformation
equivalence is thus that ordering prescriptions are observationally
indistinguishable at accessible scales, while the half-density
prescription provides a geometrically distinguished representative
within the equivalence class (analogous to Lorenz gauge).

(A companion satellite on ordering equivalence develops the four-layer
classification (principal symbol, connection, scalar potential, domain)
systematically, with additional worked examples --- position-dependent
mass in a harmonic trap, curved-manifold Laplace-Beltrami operator ---
and connects the ordering/discretization freedom to star-product
automorphisms and the Itô/Stratonovich correspondence in path-integral
time-slicing.)

\hypertarget{formal-deformation-boundary}{%
\subsection{7.5 Formal Deformation
Boundary}\label{formal-deformation-boundary}}

In this section we use formal/asymptotic deformation language for local
bridge statements. We do not require the full \(C^\ast\)-algebraic
deformation-quantization program for the manuscript's main argument; the
needed ingredient is compatibility of the classical limit and quantum
corrections under the stated assumptions {[}Landsman1998{]}.

Transition to Section 8: with the deformation bridge in place, the
remaining problem is not how to define first-order quantum corrections,
but how to keep refined predictions finite and scale-consistent when
naive limits diverge. That control problem is precisely the
renormalization step.

\hypertarget{renormalization-as-controlled-refinement}{%
\section{8. Renormalization as Controlled
Refinement}\label{renormalization-as-controlled-refinement}}

\hypertarget{why-renormalization-appears-in-refinement-limits}{%
\subsection{8.1 Why Renormalization Appears in Refinement
Limits}\label{why-renormalization-appears-in-refinement-limits}}

The previous sections treated refinement as benign: polygonal refinement
in Section 3, time-slicing in Section 6, and deformation parameter
limits in Section 7. In quantum field theory and in several singular
quantum-mechanical models (e.g.~contact interactions), the same
refinement step can instead \emph{diverge}
{[}ManuelTarrach1994PertRenQM{]} {[}BoyaRivero1994Contact{]}: as the
cutoff scale is removed, intermediate quantities blow up even when
low-energy physics is expected to remain finite.

Renormalization is the mechanism that restores the program's central
thesis in the divergent case: it provides a controlled rule for taking
refinement limits so that observables remain stable. Operationally, it
accepts that intermediate expressions depend on a regulator (cutoff),
but requires that properly defined observables do not.

To keep the discussion aligned with the paper's composition language, we
treat renormalization as an invariance/consistency condition across
composed refinement steps.

\texttt{Heuristic\ H6.1\ (Renormalization\ as\ part\ of\ “what\ a\ theory\ is”).}
In benign refinement problems, one can often send the refinement
parameter to zero without further choices. In divergent refinement
problems, the renormalization prescription (what is regulated, what is
held fixed, and how parameters are re-expressed as the cutoff moves) is
not optional bookkeeping: it is part of the definition of the continuum
theory, because it specifies which composed/refined predictions are
declared physically stable.

\hypertarget{regulator-bare-data-and-renormalized-observables}{%
\subsection{8.2 Regulator, Bare Data, and Renormalized
Observables}\label{regulator-bare-data-and-renormalized-observables}}

Let \(\Lambda\) denote a refinement cutoff (e.g., momentum cutoff
\(|k|<\Lambda\) or lattice spacing \(a\) with \(\Lambda\sim 1/a\)). Let
\(g_B(\Lambda)\) denote the cutoff-dependent \emph{bare} parameters of
the regulated theory (couplings, masses, field normalizations), and let
\(O_\Lambda\) be a regulated prediction for some observable \(O\).

\texttt{Proposition\ P6.1\ (Renormalized\ observable\ as\ cutoff-stable\ limit).}
If there exists a choice of cutoff-dependent bare parameters
\(g_B(\Lambda)\) such that the limit

\[
O_{\mathrm{phys}}
\equiv
\lim_{\Lambda\to\infty} O_\Lambda\big(g_B(\Lambda)\big)
\]

exists and is finite (or has a controlled asymptotic expansion) for the
observables of interest, then the refinement limit is \emph{defined} by
this prescription.

This statement is intentionally operational: it does not assume that the
cutoff-free object exists without tuning. It states that ``physical
theory'' means a stable target under refinement.

It is often convenient to introduce a renormalization scale \(\mu\) (a
reference resolution) and a renormalization map \(R_{\Lambda\to\mu}\)
from bare to renormalized parameters:

\[
g_R(\mu) = R_{\Lambda\to\mu}\big(g_B(\Lambda)\big).
\]

The composition viewpoint suggests a compatibility condition:
renormalizing from \(\Lambda\) down to \(\mu\) should be the same as
renormalizing from \(\Lambda\) to an intermediate scale \(\kappa\) and
then from \(\kappa\) to \(\mu\):

\[
R_{\Lambda\to\mu} = R_{\kappa\to\mu}\circ R_{\Lambda\to\kappa}.
\]

This is the renormalization-group (RG) semigroup property in refinement
language; for a standard Wilsonian/ERG discussion of coarse-graining
flows and fixed points, see {[}Rosten2012ERG{]}.

\texttt{Derivation\ D6.0\ (Control\ map\ \textbackslash{}(\textbackslash{}tau\textbackslash{}):\ comparing\ refinements\ at\ fixed\ ruler).}
The same compatibility condition can be stated without committing to a
particular regulator. Fix a reference ruler \(h>0\) (the resolution at
which we compare predictions), and let \(A_{h,\theta}\) denote a family
of amplitudes/prediction functionals indexed by parameters \(\theta\)
(couplings, normalizations, and any fixed conventions such as
scalarization gauge). For a refinement factor \(b>1\), choose a
``compare at ruler \(h\)'' operation \(\mathcal C_{b,h}\): take a
prediction written at finer ruler \(h/b\) and express it back at ruler
\(h\) (e.g.~by composing fine steps or integrating intermediate
variables when such a representation exists). Scale compatibility is the
closure requirement that refinement-comparison lands back in the same
family after a parameter update:

\[
\mathcal C_{b,h}\!\big(A_{h/b,\theta}\big)=A_{h,\tau_b(\theta)}.
\]

Here \(\tau_b\) is the control/flow map induced by the
compare-at-fixed-ruler operation. When no such \(\tau_b\) exists within
the chosen parameter family, refinement generates new operators and the
family must be enlarged (counterterms/effective operators). A concrete
micro-witness is \texttt{Derivation\ D6.2a}, where step-halving induces
\(\tau_2(a)=a/2+1/4\) with fixed point \(a_\ast=1/2\). In the cutoff
notation above, one may view \(R_{\Lambda\to\mu}\) as a special case of
\(\tau\) written with explicit reference scales.

\hypertarget{rg-equation-from-cutoff-independence}{%
\subsection{8.3 RG Equation from Cutoff
Independence}\label{rg-equation-from-cutoff-independence}}

\texttt{Derivation\ D6.1\ (RG\ equation\ as\ consistency\ under\ refinement).}
Assume a regulated observable depends on the cutoff \(\Lambda\) both
explicitly and through the bare parameters \(g_B(\Lambda)\):

\[
O_{\mathrm{phys}} = O_\Lambda\big(g_B(\Lambda)\big),
\]

and impose cutoff-independence of the physical prediction:

\[
\frac{d}{d\ln\Lambda} O_\Lambda\big(g_B(\Lambda)\big)=0.
\]

By the chain rule,

\[
0
=
\frac{\partial O_\Lambda}{\partial \ln\Lambda}
+
\sum_a \frac{d g_B^a}{d\ln\Lambda}\frac{\partial O_\Lambda}{\partial g_B^a}
,
\]

where \(a\) ranges over the components of the parameter vector. Defining
the beta functions \(\beta_B^a(g_B)\equiv \frac{d g_B^a}{d\ln\Lambda}\),
we obtain the RG equation:

\[
\left(\frac{\partial}{\partial \ln\Lambda}
+\sum_a \beta_B^a(g_B)\frac{\partial}{\partial g_B^a}\right)O_\Lambda(g_B)=0.
\]

In the \(\mu\)-parametrized form with renormalized parameters
\(g_R(\mu)\), the same reasoning yields a flow equation
\(\mu \frac{d}{d\mu}g_R(\mu)=\beta(g_R)\) plus corresponding RG
invariance equations for renormalized observables. The key point for
this manuscript is structural: RG is not extra physics added after
quantization; it is the \emph{consistency condition} that makes composed
refinement meaningful when naive limits diverge.

\texttt{Proposition\ P6.2\ (Flow\ generator\ from\ refinement\ semigroup).}
Let \(W_{\Lambda\to\kappa}\) be the map sending effective parameters at
scale \(\Lambda\) to effective parameters at scale \(\kappa<\Lambda\),
and assume: 1. \(W_{\Lambda\to\Lambda}=\mathrm{id}\), 2.
\(W_{\kappa\to\mu}\circ W_{\Lambda\to\kappa}=W_{\Lambda\to\mu}\), 3.
differentiability with respect to \(\ln\Lambda\).

Then the infinitesimal generator defines beta functions:

\[
\beta^a(g)
=
\left.\frac{d}{dt}\,W^a_{e^t\mu\to\mu}(g)\right|_{t=0},
\]

and finite scale changes are recovered by integrating this vector field
on parameter space. So RG flow is the differential form of composed
refinement.

\texttt{Derivation\ D6.2\ (Toy\ logarithmic\ divergence\ and\ subtraction).}
Consider a single-coupling situation with a logarithmic cutoff
dependence in a regulated prediction:

\[
O_\Lambda(g_B;\mu)=g_B+c\,g_B^2\ln\!\left(\frac{\Lambda}{\mu}\right)+O(g_B^3),
\]

where \(c\) is a dimensionless constant determined by the model and by
the chosen renormalization convention. Define the renormalized coupling
at scale \(\mu\) by a renormalization condition
\(g_R(\mu)\equiv O_\Lambda(g_B(\Lambda);\mu)\) which is held fixed as
\(\Lambda\to\infty\). Cutoff-independence then enforces:

\[
0=\frac{d}{d\ln\Lambda}g_R(\mu)
=\frac{d g_B}{d\ln\Lambda}+c\,g_B^2+O(g_B^3),
\]

so \(\beta_B(g_B)\equiv \frac{d g_B}{d\ln\Lambda}=-c\,g_B^2+O(g_B^3)\).
Equivalently, at fixed bare coupling one finds the running with \(\mu\):

\[
\beta(g_R)\equiv \mu\frac{d g_R}{d\mu}=-c\,g_R^2+O(g_R^3),
\]

illustrating how renormalization turns the divergent \(\ln\Lambda\)
refinement effect into a scale-dependent coupling consistent with stable
observables.

\hypertarget{refinement-control-before-qft-scale-halving-as-a-model}{%
\subsection{8.4 Refinement Control Before QFT: Scale-Halving as a
Model}\label{refinement-control-before-qft-scale-halving-as-a-model}}

One can see the same logic in purely classical numerical refinement.
Consider an evolution operator \(\Phi_\varepsilon\) representing ``one
step'' at resolution \(\varepsilon\). Composition gives
\(\Phi_{2\varepsilon}\approx \Phi_\varepsilon\circ\Phi_\varepsilon\). A
refinement-control question is then: what correction to
\(\Phi_\varepsilon\) makes the two-step composition agree with a
one-step method after rescaling back to the same reference resolution?

\texttt{Derivation\ D6.2a\ (Step-halving\ induces\ a\ control\ map\ \textbackslash{}(\textbackslash{}tau\textbackslash{})\ in\ a\ toy\ ODE).}
Consider the autonomous ODE \(y'=f(y)\) on \(\mathbb R^n\) and a
one-parameter family of one-step maps at step size \(h\), \[
\Phi_h^{(a)}(y)=y+h f(y)+a\,h^2 f'(y)[f(y)]+O(h^3).
\] Here \(f'(y)\) is the Jacobian (derivative), and \(f'(y)[v]\) denotes
its action on an increment \(v\). Define the step-halving comparison
\(H(\Phi_h):=\Phi_{h/2}\circ \Phi_{h/2}\). A direct expansion to order
\(h^2\) gives \[
H(\Phi_h^{(a)})(y)=y+h f(y)+\left(\frac14+\frac{a}{2}\right)h^2 f'(y)[f(y)]+O(h^3).
\] Thus, within this ansatz family, refinement comparison closes by a
parameter update \[
H(\Phi_h^{(a)})=\Phi_h^{(\tau_2(a))}+O(h^3),\qquad \tau_2(a)=\frac{a}{2}+\frac14,
\] with fixed point \(a_\ast=1/2\) (the second-order Taylor coefficient
of the exact flow). This is a clean micro-model for
\texttt{Derivation\ D6.0}: \(\tau_b\) is the control map required so
that ``refine and compare'' lands back in the chosen family; failure of
closure forces enlarging the family (counterterms).

\texttt{Derivation\ D6.2a-HO\ (Harmonic-oscillator\ witness\ for\ step-halving).}
Apply the control-map construction to \(y'' + y = 0\) written as a
system with \(f(y,v) = (v,-y)\). The Jacobian is constant:
\(f'= \bigl(\begin{smallmatrix}0&1\\-1&0\end{smallmatrix}\bigr)\), so
\(f'(y,v)[f(y,v)] = (-y,-v)\) (the harmonic oscillator has \(f''=0\),
making the \(O(h^3)\) analysis trivially clean).

The explicit Euler discrepancy is
\(E_{h/2}\circ E_{h/2} - E_h = (h^2/4)\,f'[f]\), confirming D6.2a. At
the fixed point \(a_\ast = 1/2\), the parametric map becomes
\((y + hv - h^2 y/2,\; v - hy - h^2 v/2)\), which matches the exact flow
\((y\cos h + v\sin h,\; v\cos h - y\sin h)\) to order \(h^2\). The
control map \(\tau_2(a) = a/2 + 1/4\) drives any initial discretization
toward this second-order-accurate scheme under repeated halving ---
exponential relaxation to the universal attractor, with rate \(1/2\) per
doubling.

\texttt{Remark\ D6.2a-sg\ (Semigroup\ law\ and\ beta\ function\ for\ general\ refinement).}
Replacing step-halving by a general \(b\)-fold refinement (composing
\(b\) copies of \(\Phi_{h/b}^{(a)}\) and reading off the \(O(h^2)\)
coefficient) gives \[
\tau_b(a)=\frac{a}{b}+\frac{b-1}{2b},\qquad a_\ast=\tfrac12\;\;\text{for all }b>0.
\] These maps satisfy the semigroup law \(\tau_b\circ\tau_c=\tau_{bc}\).
Setting \(b=1+\varepsilon\) and expanding yields the infinitesimal
generator \(\beta(a)=\tfrac12-a\), a linear flow with universal
attractor \(a_\ast=1/2\). Thus the ``RG semigroup'' language invoked in
\texttt{Heuristic\ H6.2} is not merely an analogy: the step-refinement
control maps form a one-parameter semigroup whose beta function, fixed
point, and exponential relaxation to universality are all explicit.

\texttt{Remark\ D6.2a1\ (Next\ discrepancy\ term\ and\ the\ next\ rooted\ tree\ in\ Euler\ step-doubling).}
For the explicit Euler map \(E_h(y):=y+h f(y)\) with \(f\in C^2\),
expanding one order further gives \[
E_{h/2}\!\circ E_{h/2}(y)-E_h(y)
=\frac{h^2}{4}\,f'(y)[f(y)]+\frac{h^3}{16}\,f''(y)[f(y),f(y)]+O(h^4),
\] where \(f'(y)[v]\) denotes the Jacobian acting on a vector and
\(f''(y)[v,w]\) is the bilinear second derivative. In rooted-tree
language, each monomial in the Taylor expansion is an \emph{elementary
differential} labelled by a rooted tree: the leading \(O(h^2)\) term is
the chain tree \(F([\bullet]):=f'(y)[f(y)]\), and the new \(O(h^3)\)
term is the branch tree \(F([\bullet,\bullet]):=f''(y)[f(y),f(y)]\).
(The \(O(h^3)\) contribution requires \(f\in C^2\); the \(O(h^2)\) term
only needs \(f\in C^1\).)

\texttt{Heuristic\ H6.2\ (Rooted\ trees\ as\ refinement\ bookkeeping).}
In Runge--Kutta and related integrators, the comparison between composed
steps and a single step organizes into rooted-tree expansions; the
corresponding composition law forms a group (the Butcher group).
Interpreting ``step-halving then rescaling back'' as a scale-update
operation makes the analogy with RG bookkeeping explicit, and
rooted-tree/Hopf-algebra combinatorics also appears in perturbative
renormalization {[}Brouder1999{]} {[}McLachlan2017{]}
{[}ConnesKreimer2000{]}.

This example is included not to replace QFT renormalization, but to
reinforce the paper's thesis with a clean model: renormalization is what
you do when ``refine and compare'' is not automatically stable. The
Butcher \emph{group} concerns formal method composition, whereas
Wilsonian coarse-graining is generally a \emph{semigroup} because
information is discarded at each coarse-graining step. (A companion
satellite on rooted-tree bookkeeping develops the Butcher/RG dictionary
in full: explicit Hopf coproduct formulas for trees up to order 3, a
7-entry correspondence table, a worked 2D delta RG example parallel to
the midpoint RK2 composition test, and a precise characterization of the
group-vs-semigroup structural distinction.) A structural gap remains
between the toy model and full RG: the beta function
\(\beta(a)=\tfrac12 - a\) of \texttt{Remark\ D6.2a-sg} is \emph{linear},
so the RG invariant is algebraic in the coupling and no new scale is
generated. Dimensional transmutation (\texttt{Derivation\ D6.2}, Section
8.3) requires a beta function of order \(\ge 2\) at the fixed point,
producing an essential singularity \(\Lambda_\ast\sim\mu\,e^{-1/(cg)}\)
that is non-analytic in the coupling. The semigroup axioms
(\texttt{Proposition\ P6.2}) are shared by both regimes; what separates
them is the order of vanishing of \(\beta\) at the fixed point. (For an
exactly solvable coarse-graining model --- Gaussian integration as Schur
complement --- that makes the semigroup property and non-invertibility
of coarse-graining concretely visible, cf.~Derivation RG-D1.7 in the RG
companion note.)

\hypertarget{counterterms-as-refinement-corrections}{%
\subsection{8.5 Counterterms as Refinement
Corrections}\label{counterterms-as-refinement-corrections}}

In field theory language, refinement is implemented by a regulated
action \(S_\Lambda\) with cutoff-dependent parameters. Schematically,

\[
S_\Lambda[\phi]
=
\int d^D x\left(
\frac{Z(\Lambda)}{2}(\partial\phi)^2
+\frac{m^2(\Lambda)}{2}\phi^2
+\frac{\lambda(\Lambda)}{4!}\phi^4
+\cdots
\right),
\]

where \(D\) is the spacetime dimension and the ``\(\cdots\)'' stands for
additional operators allowed by symmetries and by the desired accuracy.
The counterterm viewpoint is simply the statement that
\(Z,m^2,\lambda,\ldots\) must be chosen as functions of \(\Lambda\) so
that the cutoff-stable limits of observables exist. In this
compositional narrative, counterterms are refinement corrections
required to keep the ``same theory'' after integrating out short scales.

\texttt{Derivation\ D6.3\ (Difference\ quotient\ as\ counterterm\ subtraction).}
Let \(f\in C^1\) and \(\varepsilon\to 0^+\). The two regulated
quantities \(f(x+\varepsilon)/\varepsilon\) and \(f(x)/\varepsilon\)
each diverge like \(1/\varepsilon\). Subtracting the local counterterm
\(f(x)/\varepsilon\) produces a finite limit:

\[
\frac{f(x+\varepsilon)}{\varepsilon}-\frac{f(x)}{\varepsilon}
=\frac{f(x+\varepsilon)-f(x)}{\varepsilon}
\xrightarrow{\varepsilon\to0} f'(x).
\]

This is a minimal model of renormalization: divergent regulated
expressions become finite after subtracting a divergence that depends
only on local data, and the renormalized quantity is the cutoff-stable
remainder.

The Connes-Kreimer framework makes this consistency structural by
encoding perturbative renormalization as a factorization problem with a
Hopf-algebra organization of divergences {[}ConnesKreimer2000{]}. For
this manuscript, the take-away is not the full machinery but the
alignment: renormalization is a principled method for producing
regulator-independent predictions from composable local pieces when
refinement alone does not converge.

\hypertarget{assumptions-and-boundaries-audit}{%
\subsection{8.6 Assumptions and Boundaries
Audit}\label{assumptions-and-boundaries-audit}}

\texttt{Proposition\ P6.3\ (Closure\ assumption\ for\ finite-parameter\ flow).}
Finite-dimensional beta-function systems are closed only after choosing
a truncation/ansatz for allowed operators (or a complete effective
basis). If new operators are generated by refinement and omitted from
the parameter vector, the reduced flow is only approximate.

This caveat is essential for interpreting section 8 correctly: the RG
equations written here are exact at the level of the chosen variable
set, but practical truncations can make them approximate. The main
thesis is unaffected: renormalization remains the rule that restores
cross-scale consistency under composed refinement.

\texttt{Derivation\ D6.4\ (Two-level\ truncation\ audit\ and\ a\ quantitative\ stability\ window).}
Take a one-coupling flow with two truncation levels: \[
\beta_{(2)}(g)=-b_0 g^2,\qquad
\beta_{(3)}(g)=-b_0 g^2-b_1 g^3,\qquad b_0>0.
\] At fixed \(g\), define the local truncation defect \[
\delta_\beta(g):=\frac{|\beta_{(3)}(g)-\beta_{(2)}(g)|}{|\beta_{(2)}(g)|}
=\left|\frac{b_1}{b_0}\right|\,|g|.
\] For a tolerance \(\eta\in(0,1)\), requiring
\(\delta_\beta(g)\le \eta\) yields an explicit stability window \[
|g|\le g_{\max}(\eta):=\eta\,\frac{b_0}{|b_1|}.
\] Thus the truncation is quantitatively controlled only in the
weak-coupling region \(|g|\ll b_0/|b_1|\); when \(|g|\sim b_0/|b_1|\),
the neglected term is order-one and truncation closure fails. This turns
the qualitative caveat of \texttt{Proposition\ P6.3} into a concrete
pass/fail criterion.

\texttt{Remark\ D6.4a\ (Model-specific\ benchmark:\ \textbackslash{}(\textbackslash{}lambda\textbackslash{}phi\^{}4\textbackslash{})\ at\ one\ and\ two\ loops).}
For scalar \(\lambda\phi^4\) theory in \(D=4\) with
\(\mathcal{L}_{\mathrm{int}}=\lambda\phi^4/4!\), the MS coefficients
from \texttt{Derivation\ D8.2a} (one-loop \(b_0\)) and the standard
two-loop MS-bar result are \[
b_0=\frac{3}{16\pi^2}\approx 0.019,
\qquad
b_1=-\frac{17}{3(16\pi^2)^2}\approx -2.27\times 10^{-4}.
\] The D6.4 stability window becomes
\(|\lambda|\le\eta\cdot(144\pi^2/17)\approx 83.6\,\eta\). At 10\%
tolerance (\(\eta=0.1\)), the two-loop correction remains below 10\% for
\(|\lambda|\lesssim 8.4\), well inside the perturbative regime. At
\(|\lambda|\sim 84\), the two-loop term is order-one and the one-loop
truncation is unreliable. This confirms that D6.4's generic criterion
produces physically sensible bounds when instantiated on a concrete
model.

\texttt{Remark\ H6.3\ (Non-perturbative\ content\ recovery\ from\ the\ contact\ expansion).}
The contact expansion \(C_0+C_2 q^2+C_4 q^4+\cdots\) is a Taylor series
in \(q^2/M^2\), where \(M\) is the mass of the integrated-out mediator.
Its Taylor coefficients are infrared data---measurable at low momentum
transfer. The non-perturbative content (poles, branch cuts,
instanton-type singularities) lies outside the convergence disk
\(|q^2|<M^2\) and is invisible to any finite truncation. Yet this
content can be recovered by controlled extrapolation methods matched to
the singularity type: \textbf{(1) Poles (tree-level exchange):} For a
Yukawa amplitude \(\mathcal A(q^2)=g^2/(q^2+M^2)\), the \([0/1]\) Padé
approximant of just the first two contact coefficients \(C_0=g^2/M^2\),
\(C_2=-g^2/M^4\) yields
\(P_{[0/1]}(q^2)=C_0/(1-(C_2/C_0)q^2)=g^2/(q^2+M^2)=\mathcal A(q^2)\),
recovering the full amplitude exactly---including the pole at
\(q^2=-M^2\), which sits outside the Taylor convergence disk. Two
low-energy observables (the scattering length \(C_0\) and the
effective-range ratio \(C_2/C_0=-1/M^2\)) determine the UV mass scale.
\textbf{(2) Branch cuts (loop-level):} The vacuum polarization
\(\Pi(q^2)\) has a branch cut at \(q^2=4m^2\) (pair-production
threshold). The Taylor coefficients below threshold determine the
moments of the spectral function \(\mathrm{Im}\,\Pi(s)\) via dispersion
relations, and \([N/N]\) Padé approximants place poles that accumulate
on the cut as \(N\to\infty\) (Montessus de Ballore). \textbf{(3)
Divergent series (non-perturbative sectors):} When Taylor coefficients
grow as \(|a_n|\sim n!\), the Borel transform \(B(t)=\sum(a_n/n!)t^n\)
has finite radius of convergence, and Borel--Padé resummation recovers
the full function including exponentially suppressed contributions
\(\sim e^{-A/g}\) from instanton saddle points. In each case, the Taylor
coefficients are the ``local data'' of the refinement-compatibility
framework (Section 10.3, Proposition P10.1), and the reconstruction
method is the ``control map'' \(\tau\) that accesses global structure
from local input. The hierarchy of methods---algebraic rational
approximation for poles, integral reconstruction for cuts, Borel
resummation for essential singularities---mirrors the hierarchy of
singularity types in the analytic continuation, and each method requires
its own control hypotheses (meromorphy, dispersion-relation analyticity,
Borel summability). The contact expansion thus determines the
non-perturbative content, not despite being perturbative, but because
analyticity and crossing symmetry (the consistency conditions behind
RCP) constrain the global structure once the local data is given. This
is the inverse of the contact-decoupling process: UV physics collapses
into contact coefficients as \(M\to\infty\); conversely, the contact
coefficients can be used to reconstruct the UV physics by controlled
extrapolation.

Transition to Section 9: we now have the full chain Newtonian refinement
\(\to\) action additivity \(\to\) path-integral composition \(\to\)
deformation compatibility \(\to\) renormalized refinement control. The
final synthesis section stress-tests the transitions, labels what
remains heuristic, and consolidates the manuscript into a single
coherent argument.

\hypertarget{unified-perspective-and-open-problems}{%
\section{9. Unified Perspective and Open
Problems}\label{unified-perspective-and-open-problems}}

\hypertarget{end-to-end-claim-graph}{%
\subsection{9.1 End-to-End Claim Graph}\label{end-to-end-claim-graph}}

The manuscript has built one chain across seven technical steps: 1.
Section 3: refinement geometry in central-force motion yields an exact
finite-step invariant (equal areas / angular momentum preservation). 2.
Section 4: action stationarity and Noether symmetry express the same
invariant in variational language. 3. Section 5: weak/distributional
formulation extends stationarity to singular limits (mollifiers,
corners, impulses) with explicit admissibility boundaries. 4. Section 6:
composition under slicing plus additive action yields exponential
weighting and stationary-phase classical recovery. 5. Section 7:
ordering ambiguity is recast as deformation-equivalence data with a
shared Poisson classical limit. 6. Section 8: divergent refinement is
controlled by renormalization maps and RG semigroup consistency
(\texttt{Remark\ D6.2a-sg} gives the explicit semigroup law and beta
function in a toy model).

\texttt{Remark\ P7.1a\ (Compact\ compatibility\ map\ for\ navigation).}
The same chain can be read as three linked tracks, each with explicit
witnesses: 1. \textbf{Partition track}: D1.1-D1.2 \(\to\) D2.1 \(\to\)
D3.1 \(\to\) D4.1/D4.1a \(\to\) P4.2 \(\to\) D6.5. 2.
\textbf{Representation track}: D4.1b \(\to\) D5.1 \(\to\) D9.1/(Remark
D9.1a)/D9.1b/D9.1d/D9.1e/D9.1h/D9.1i/D9.1k. 3. \textbf{Scale track}:
D6.0-D6.2 \(\to\) (Remark D6.2a-sg)/D6.4/D6.4b/D6.6 \(\to\) D8.1-D8.2
\(\to\) D11.2-D11.3. Each arrow is a compatibility bridge, not a change
of subject. This compact map is the textual counterpart of the diagram
requested in Section 9.5.

The unifying thesis is therefore not ``classical then quantum then QFT''
as disconnected layers, but ``one refinement/composition problem under
progressively stricter consistency requirements.''

\texttt{Proposition\ P7.1\ (Compatibility\ chain\ of\ limits).} Under
the regularity and admissibility assumptions stated in sections 3--8,
the following compatibility conditions can be imposed simultaneously:

\[
\delta S[q;\eta]=0
\;\Longleftrightarrow\;
\text{Euler-Lagrange in weak form},
\]

\[
K \sim \int \mathcal Dq\,e^{iS[q]/\hbar}
\;\Longrightarrow\;
\hbar\to 0 \text{ concentrates on } \delta S=0,
\]

\[
\lim_{\hbar\to 0}\frac{1}{i\hbar}[f,g]_{\star_\hbar}=\{f,g\},
\qquad
\left(\partial_{\ln\Lambda}+\beta\cdot\partial_g\right)O_\Lambda=0.
\]

These equations are not identical statements; they are compatibility
constraints on one staged construction: classical extremals, quantum
composition, algebraic deformation, and scale consistency must match in
their overlap domains.

\hypertarget{transition-stress-test}{%
\subsection{9.2 Transition Stress Test}\label{transition-stress-test}}

\texttt{Derivation\ D7.1\ (No\ hidden\ leap\ audit\ across\ transitions).}
The manuscript can be stress-tested by checking each transition against
one explicit closure condition:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  \texttt{Section\ 3\ -\textgreater{}\ Section\ 4} closure: finite-step
  angular momentum invariance and variational Noether charge agree
  through \(\dot A=\frac{L_{\mathrm{ang}}}{2m}\). This closes the
  geometry-to-variational bridge.
\item
  \texttt{Section\ 4\ -\textgreater{}\ Section\ 5} closure:
  Euler-Lagrange equations in classical smooth form imply weak
  distributional form when tested against \(C_c^\infty\), and mollifier
  localization recovers pointwise equations under continuity
  assumptions. This closes smooth-to-weak extension.
\item
  \texttt{Section\ 5\ -\textgreater{}\ Section\ 6} closure: the
  admissible classical set in semiclassics includes smooth and
  piecewise-smooth trajectories satisfying matching laws
  \([\partial_{\dot q}\mathcal L]^+_- =0\) (corner) or \(=J\) (impulse).
  The composition integral
  \(\int dq\,K(q_f,t_f;q,t_{\mathrm{mid}})K(q,t_{\mathrm{mid}};q_i,t_i)\)
  sums over \emph{all} intermediate configurations \(q\), and for
  short-time kernels with saddle-point evaluation, the stationary-phase
  condition at the junction recovers exactly the Weierstrass--Erdmann
  corner law \([\partial_{\dot q}\mathcal L]^+_-=0\). A concrete witness
  (Derivation D6.5): a free particle receiving an instantaneous kick
  \(J\) at \(t_{\mathrm{mid}}\) satisfies the impulse law and
  contributes correctly to \(K(q_f,t_f;q_i,t_i)\) via the intermediate
  integral (the saddle point shifts by the momentum transfer). The
  bridge is thus closed at the variational level; kernel-level closure
  for general piecewise-smooth paths in the full (non-saddle-point)
  measure remains a formal identification.
\item
  \texttt{Section\ 6\ -\textgreater{}\ Section\ 7} closure:
  discretization/ordering freedom in short-time kernels maps to
  star-product representatives that share the same Poisson boundary at
  \(\hbar\to0\). This closes path-integral ambiguity into deformation
  language.
\item
  \texttt{Section\ 7\ -\textgreater{}\ Section\ 8} closure: deformation
  handles classical/quantum compatibility at fixed scale;
  renormalization handles cross-scale consistency when refinement
  diverges. This closes fixed-scale quantization into multiscale
  consistency.
\end{enumerate}

The audit criterion is simple: every bridge states its assumptions and
carries an explicit invariant or equation through the transition. Where
this fails, the claim is downgraded to heuristic.

\hypertarget{what-is-proven-vs-heuristic}{%
\subsection{9.3 What Is Proven vs
Heuristic}\label{what-is-proven-vs-heuristic}}

For navigation, Sections 3--8 contain the following mix of results and
bridges:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  \textbf{Section 3:} polygonal central-impulse refinement preserves
  angular momentum and equal areas at finite step.
  (\texttt{Proposition}, \texttt{Derivation}) Boundary: central impulses
  and consistent refinement limit.
\item
  \textbf{Section 4:} Euler--Lagrange plus Noether recover
  angular-momentum and energy invariants. (\texttt{Derivation},
  \texttt{Proposition}) Boundary: \(C^2\) trajectory regularity and
  standard variational hypotheses.
\item
  \textbf{Section 5:} weak Euler--Lagrange, mollifier probes, and jump
  laws for corners/impulses. (\texttt{Proposition}, \texttt{Derivation})
  Boundary: distribution linearity and no undefined nonlinear products.
\item
  \textbf{Section 6:} composition plus additivity imply exponential
  weighting; stationary phase yields classical recovery. The formal
  continuum-limit passage (§6.4, Heuristic H4.2a) is explicitly labeled
  as heuristic; the surrounding Derivations (D4.2, D4.2a) are labeled as
  such. (mixed: \texttt{Proposition}, \texttt{Derivation},
  \texttt{Heuristic}) Boundary: formal path-integral usage and local
  stationary-phase assumptions.
\item
  \textbf{Section 7:} deformation products recover the Poisson bracket;
  ordering appears as deformation-equivalence choice. A complementary
  geometric resolution exists: half-density conjugation
  \(\Delta_{1/2}=|g|^{1/4}(-\Delta_g)|g|^{-1/4}\) provides a canonical
  representative within the deformation-equivalence class. On flat
  space, this agrees with Weyl ordering on the principal symbol and
  connection (first-derivative) terms, differing only in an
  \(O(\hbar^2)\) scalar potential (\texttt{Remark\ D9.1a},
  \texttt{Remark\ P5.2a}). On curved manifolds, the half-density
  conjugation additionally modifies the connection via a drift term,
  producing the DeWitt curvature coupling \(R/6\) at each Riemann normal
  coordinate center (on general curved manifolds \(V_{\mathrm{HD}}\) is
  position-dependent; \texttt{Remark\ D9.1n}) rather than the
  Weyl/Stratonovich value \(R/8\) (\texttt{Remark\ D4.1e},
  \texttt{Remark\ D9.1p}). Crucially, the conjugation \(\Delta_{1/2}\)
  is unitarily equivalent to \(-\Delta_g\) and therefore spectrally
  identical to the bare Laplacian; the genuine ordering ambiguity lives
  in the shifted operator \(-\Delta_g + V_{\mathrm{HD}}\), which has a
  distinct spectrum (\texttt{Remark\ D9.1q}). (mixed:
  \texttt{Proposition}, \texttt{Derivation}, \texttt{Heuristic})
  Boundary: formal/asymptotic deformation setting and scope of
  equivalence; curved-manifold scope for connection-level differences.
\item
  \textbf{Section 8:} RG appears as semigroup consistency under composed
  refinement; counterterms appear as refinement corrections. (mixed:
  \texttt{Proposition}, \texttt{Derivation}, \texttt{Heuristic})
  Boundary: closure/truncation assumptions and regulator-scheme choice.
\end{enumerate}

\texttt{Remark\ (D=4\ scope\ boundary).} The framework does not select
\(D=4\) as the unique spacetime dimension from first principles. Several
independent observations each have \((D{-}4)=0\) as a root by different
algebraic mechanisms: conformal Laplacian simplification (H4.0b),
gauge-coupling marginality (H4.0c), constant spectral shift on \(S^3\)
(Proposition D9.1i), and conformal heat-kernel flatness (Remark D9.1q).
These are structural coincidences at the algebraic level, not a
derivation of \(D=4\) from the composition axioms. The paper reports
them as independent data points, not as evidence that the framework
privileges four dimensions.

\texttt{Heuristic\ H7.1\ (Programmatic\ interpretation).} The
Newton-to-path-integral narrative is best read as a \emph{compatibility
program} rather than a single theorem: each layer adds new consistency
constraints while preserving prior invariants in its domain of validity.

\hypertarget{residual-vulnerabilities}{%
\subsection{9.4 Residual
Vulnerabilities}\label{residual-vulnerabilities}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  The path integral remains formal at full measure-theoretic level;
  constructive control is not provided here. Minimal closure target:
  exhibit one explicit regulated kernel family \(K_\varepsilon\) with a
  proved composition law and a controlled \(\varepsilon\to0\) statement
  in a nontrivial model. Status: \textbf{Partially addressed.} Appendix
  10.6 provides the regulated Gaussian family (D12.1: exact composition
  with additive regulator; P12.1: controlled \(\varepsilon\to0\) limit
  recovering the heat-kernel semigroup), a first-order bounded-potential
  extension (D12.2: \(O(V)\) composition closure), quantitative
  operator-norm bounds (P12.2), and an explicit failure mode for
  singular potentials (D12.2a). These witnesses cover only the free
  Gaussian and first-order bounded-potential regimes; non-Gaussian,
  non-perturbative path-space constructions (i.e., the content of
  constructive quantum field theory) remain fully open.
\item
  Deformation equivalence is stated at the structural level; explicit
  model-by-model operator-domain analysis is partially addressed.
  Current status: one position-dependent-mass model
  (\(f(q)=1+\alpha q^2\) in a harmonic trap) has been carried through
  Weyl and half-density quantizations with explicit \(O(\hbar^2)\)
  mismatch term and quantitative energy-shift estimate
  (\texttt{Remark\ D9.1a}, \texttt{Remark\ P5.2a}). Curved-manifold
  case: \texttt{Proposition\ D9.1h} provides an explicit spectral
  comparison on \(S^2\); \texttt{Proposition\ D9.1i} extends to \(S^3\)
  (spectral shift constant \(-1\), unique among \(S^d\);
  \(V_{\mathrm{HD}}\) itself is constant only in left-invariant
  coordinates); \texttt{Proposition\ D9.1k} covers the non-compact case
  \(H^2\) (McKean spectral gap recovered by half-density ordering).
  \textbf{Status: substantially addressed.} Full extension to
  non-diagonal metrics and domain analysis remains open.
\item
  RG flow is derived structurally; explicit computations are now
  provided at both the quantum-mechanical level (2D contact interaction,
  Appendix 10.5: D11.1--D11.3) and the field-theory level
  (\(\lambda\phi^4\) one-loop beta function in \(D=4-2\varepsilon\),
  Appendix 10.1: D8.2a). Status: \textbf{CLOSED.} The minimal closure
  target (one fixed-scheme one-loop QFT computation with subtraction,
  beta function, and scheme change in manuscript conventions) is met by
  D8.2a.
\item
  Truncation closure in section 8 is identified but not benchmarked by
  an explicit truncation-error study. Minimal closure target: compare at
  least two truncation levels on the same model and report an
  observable-level stability window. Status: \textbf{CLOSED.} Derivation
  D6.4 provides a two-level truncation audit (\(\beta_{(2)}\) vs
  \(\beta_{(3)}\)) with a quantitative stability window
  \(|g|\le\eta\,b_0/|b_1|\). Remark D6.4a instantiates this on
  \(\lambda\phi^4\) at one and two loops, giving
  \(|\lambda|\lesssim 8.4\) at 10\% tolerance --- a concrete
  model-specific benchmark meeting the stated closure target.
\end{enumerate}

Vulnerability 1 is partially addressed by Appendix 10.6 (explicit
Gaussian and first-order witnesses; full constructive control remains
open); Vulnerability 3 is closed by Appendix 10.1. Vulnerability 2 is
substantially addressed by the \(S^2\), \(S^3\), and \(H^2\) spectral
witnesses (P D9.1h, P D9.1i, P D9.1k); Vulnerability 4 is closed by D6.4
+ Remark D6.4a (quantitative truncation defect criterion with
model-specific \(\lambda\phi^4\) benchmark). All four are honest scope
boundaries, not hidden defects: each is paired with a concrete witness
(existing or prospective) that would close it.

\hypertarget{future-work-task-driven-revision-queue-editorial-package-labels}{%
\subsection{9.5 Future Work (Task-Driven Revision Queue; Editorial
Package
Labels)}\label{future-work-task-driven-revision-queue-editorial-package-labels}}

To keep the manuscript evolving by derivation rather than by incremental
wording changes, future edits should be organized as concrete work
packages:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \textbf{Package A (Path-space control witness).} Deliverable: one
  subsection with a regulated family \(K_\varepsilon\), its composition
  identity, and a limit statement. Pass criterion: at least one numbered
  statement with assumptions and one explicit failure mode when
  assumptions are dropped. Current status: Appendix 10.6 now contains
  free-kernel exact composition, first-order bounded-potential witness,
  quantitative \texttt{L\^{}\textbackslash{}infty} control, and an exact
  nontrivial solvable kernel benchmark (\texttt{D12.1}, \texttt{P12.1},
  \texttt{D12.2}, \texttt{P12.2}, \texttt{D12.3}); full constructive
  path-space control remains open.
\item
  \textbf{Package B (Ordering/domain benchmark).} Deliverable: one
  appendix-level model comparing two orderings plus half-density
  conjugation. Pass criterion: explicit operator difference through
  \(O(\hbar)\) and a clear statement of domain/equivalence boundaries.
  Current status: Appendix 10.2 now includes periodic/curved symmetry
  benchmarks, one explicit self-adjoint extension witness
  (\texttt{D9.1b}, \texttt{D9.1d}, \texttt{D9.1e}, \texttt{D9.1f}),
  explicit curved-manifold spectral comparisons
  (\texttt{Proposition\ D9.1h}, \texttt{Proposition\ D9.1i},
  \texttt{Proposition\ D9.1k}), and a four-layer stratification of
  ordering differences with quantitative observability estimates
  (\texttt{Remark\ D9.1a}); full extension classification remains open.
\item
  \textbf{Package C (QFT-level RG witness).} Deliverable: one-loop
  running in a fixed subtraction scheme using manuscript conventions.
  Pass criterion: explicit \(\beta(g)\), one scheme-change computation,
  and direct mapping to scale compatibility in Section 8. Current
  status: \textbf{SUBSTANTIALLY COMPLETE.} Appendix 10.1 contains the
  generic single-coupling template (D8.1, D8.2, P8.1) plus an explicit
  QFT-level witness (D8.2a: \(\lambda\phi^4\) one-loop beta function in
  \(D=4-2\varepsilon\)). Appendix 10.5 provides the full 2D
  contact-interaction computation (D11.1--D11.3: cutoff loop,
  renormalized coupling, beta function, dimensional transmutation,
  scheme dependence). The Wilsonian shell-integration route making
  semigroup composition directly visible is available in the
  RG-fundamental companion note (Derivation RG-D1.2a); a forward
  reference appears in Appendix 10.5 (line after D11.2).
\item
  \textbf{Package D (Truncation error audit).} Deliverable: side-by-side
  flows for two truncation levels with at least one observable
  comparison. Pass criterion: a quantitative stability region and one
  explicit breakdown regime. Current status: \textbf{COMPLETE.} D6.4
  provides the generic two-level truncation criterion with stability
  window \(|g|\le\eta\,b_0/|b_1|\); Remark D6.4a instantiates this on
  \(\lambda\phi^4\) at one and two loops, giving a concrete
  model-specific benchmark.
\item
  \textbf{Package E (Reader-map consolidation).} Deliverable: one
  compact compatibility diagram linking Sections 3--8 and Appendices
  10.1--10.6. Pass criterion: every arrow references at least one
  numbered proposition/derivation in the text.
\end{enumerate}

A practical rule follows: additions that do not advance at least one
package should be deferred, so revision effort remains concentrated on
technical closure rather than bookkeeping edits. These package labels
are editorial planning tags only, not theorem/claim labels. Quick
navigation pointer: Appendix 10.1 primarily advances Package C/D;
Appendix 10.2 primarily advances Package B; Appendix 10.6 primarily
advances Package A; Section 9.1 + Appendix 10.3 support Package E.

\hypertarget{conclusion}{%
\subsection{9.6 Conclusion}\label{conclusion}}

The paper's central thesis is that ``continuum laws'' are most cleanly
understood as \emph{stable targets of controlled refinement}:
finite-step invariants (Newton's polygonal dynamics) persist through the
action formulation, and action additivity is the algebraic structure
that forces a consistent composition law. In the quantum setting,
multiplicative composition together with local additivity makes
exponential weighting structurally natural, and classical dynamics are
recovered by stationary-phase concentration. Two further control
mechanisms enter when naive refinement is not uniquely defined:
deformation quantization organizes ordering/discretization choices into
equivalence classes compatible with a common classical limit, and
renormalization supplies the compatibility condition required when
refinement limits diverge.

Throughout, the manuscript keeps refinement explicit, separates
derivations from heuristics, and highlights the additional hypotheses
needed for each continuum passage. (A companion satellite on the
Refinement Compatibility Principle formalizes this unifying idea as an
explicit axiom system --- five axioms (composition, identity,
representation equivalence, scale invariance, dimensional homogeneity)
organized into three channels (partition, representation, scale) ---
with worked witnesses at each channel and a multi-channel synthesis
showing how the path integral realizes all three simultaneously.)

\texttt{Remark\ P9.1\ (Forced-completion\ chain\ and\ structure\ vs\ content).}
The narrative admits a sharper reading as a chain of \emph{forced
completions}: each stage is the minimum enrichment of the composition
law needed for consistency at the next level of complexity. Stage 0→1:
limits of finite differences yield derivatives (calculus). Stage 1→2:
temporal composition of propagators forces Gaussian kernels, \(d/2\)
normalization, and \(\kappa=\hbar\) (Proposition P4.2; composition alone
suffices as the single master axiom, Remark P4.2h). Stage 2→3: per-mode
quantization plus infinite-mode assembly via renormalization yield field
theory (Sections 6 and 8). Each transition is a derivation (or, for
stage 2→3, a structural argument) from the previous stage's composition
requirement, not a postulate. A clean separation emerges: composition
constrains \emph{structure} (kernel form, normalization exponent,
exponential weight) but not \emph{content} (which interaction
Lagrangian); content selection enters only at the renormalization level,
where the assembly condition filters admissible theories.

Conversely, every known departure from the compositional framework has a
structural explanation: open systems (incomplete boundary data),
measurement (subsystem tracing violates global composition), anomalies
(symmetry--composition conflict), and UV divergence (infinite-mode
assembly failure). Three of these four categories correspond to the
limit obstructions of Heuristic H0.2 --- anomalies to non-uniqueness, UV
divergence to divergence, and measurement to singular-probe
incompleteness --- reappearing at progressively higher levels of the
compositional hierarchy. Open systems constitute an additional category
not contained in H0.2, reflecting incomplete specification of boundary
data rather than a limit-control problem per se.

\texttt{Remark\ P9.1a\ (Stage\ 4:\ composition\ over\ dynamical\ geometry).}
The forced-completion chain 0→1→2→3 does not obviously terminate at QFT.
When gravity is dynamical, the composition integral must sum over
spatial-slice geometries themselves, and the notion ``t = t₁ + t₂'' that
composition (hypothesis (C) of Proposition P4.2; axiom A1 of
{[}RCPFoundations{]}) presupposes becomes gauge-dependent under general
covariance. This is qualitatively different from stages 1--3, which fix
divergences of an existing composition integral: stage 4 challenges the
\emph{domain} of the integral (what is ``the spatial slice''?), not just
the integrand. A completion would require defining composition at the
cobordism level --- without a preferred temporal foliation --- and
current candidates (asymptotic safety, holographic boundary composition,
worldsheet methods) each propose different resolutions, none yet derived
from a single composition principle. At the categorical level, stages
1--3 are realised in a 1-groupoid (the pair groupoid \(G = M \times M\),
where intermediate points are uniquely determined), whereas stage 4
requires at minimum an \((\infty,1)\)-category (the cobordism category
\(\mathrm{Cob}\), where intermediate 3-geometries are not unique ---
each foliation of a 4-cobordism gives a different factorization, and
these foliations form the 2-morphisms). The forced-completion principle
at the cobordism level is precisely the requirement that
\(Z\colon \mathrm{Cob} \to \mathrm{Hilb}\) be a symmetric monoidal
functor --- Atiyah's axiom system for TQFT. In topological theories
(\(d=2{+}1\) gravity, BF theory), this completion is achievable; in
physical \(3{+}1\) gravity with local degrees of freedom, it is not ---
which is why the chain branches rather than extending linearly. For
local-degree-of-freedom gravity, this branch may terminate unless a
concrete framework derives a background-independent analog of
\((C)+(I)+(D)\); until then, the Stage 4 continuation should be read as
analogy-level rather than theorem-level. Conversely, the classical limit
\(\kappa\to 0\) is singular (Proposition P4.2(iii)), consistent with the
interpretation that it attempts to undo a forced completion: composition
requires finite \(\kappa\), and removing it collapses the semigroup to
Hamilton--Jacobi extremization, which generically lacks an identity
limit.

\texttt{Remark\ P9.1a-Cob\ (Cobordism\ hypothesis\ as\ Stage\ 4\ uniqueness).}
The Baez--Dolan--Lurie cobordism hypothesis (Lurie 2009,
arXiv:0905.0465) makes Stage 4 uniqueness precise for topological
theories: a symmetric monoidal functor
\(Z\colon \mathrm{Bord}_n^{\mathrm{fr}} \to \mathcal{C}\) is uniquely
determined (up to equivalence) by
\(Z(\mathrm{point}) \in \mathcal{C}^{\mathrm{fd}}\), the fully
dualizable objects of \(\mathcal{C}\). This is the Stage 4 analog of
P4.2's uniqueness at Stages 1--2: just as (C)+(D)+(I) uniquely determine
\(\kappa = \hbar\) in the partition channel, monoidal functoriality on
bordisms uniquely determines the TQFT from its value at a point. The
topological restriction is essential: non-topological QFTs with running
couplings require additional structure beyond the cobordism hypothesis.

\texttt{Remark\ P9.1b\ (Stage\ 3\ analog:\ CFT\ sewing\ forces\ c/24).}
An explicit Stage 3 instance of the composition-forcing pattern exists
in conformal field theory. Segal's sewing axiom requires
\(K_\lambda(\tau_1 + \tau_2) = K_\lambda(\tau_1) \cdot K_\lambda(\tau_2)\)
for conformal-block amplitudes indexed by primary operators \(\lambda\),
where \(\tau\) is the modular parameter. The Cauchy functional equation
forces \(K_\lambda(q) = q^{\alpha_\lambda}\) with
\(q = e^{2\pi i \tau}\). The Weyl anomaly of the path-integral measure
under conformal rescaling then fixes
\(\alpha_\lambda = \Delta_\lambda - c/24\), where \(\Delta_\lambda\) is
the scaling dimension and \(c\) the central charge. The normalization
exponent \(c/24\) is forced by composition plus the Virasoro algebra
structure, just as \(d/2\) is forced by composition plus dimensional
homogeneity at stages 1--2. The central charge \(c\) itself is
\emph{not} forced (it specifies the theory, i.e.~content); but given any
\(c\), the vacuum energy \(-c/24\) is a structural output. Modular
invariance \(Z(\tau) = Z(-1/\tau)\) is an additional constraint on the
operator spectrum (content), not on the form of \(K_\lambda\). This
makes the \(d/2 \to c/24\) correspondence a genuine inter-stage pattern:
normalization exponents are forced by composition at every categorical
level. The Zamolodchikov \(c\)-theorem (\(c\) monotone decreasing under
2D RG flow, 1986) is an independent physical constraint orthogonal to
the composition-forcing structure: composition determines \(c/24\) given
\(c\) within a fixed CFT, while the \(c\)-theorem constrains how \(c\)
varies between CFTs at different energy scales.

\texttt{Remark\ P9.1b-Q1d\ (Stage\ 3.5:\ Verlinde\ fusion\ forces\ level\ quantization).}
The Verlinde formula provides an intermediate forcing step between
Stages 3 and 4. Segal sewing (Stage 3 composition) combined with modular
covariance of characters \(\chi_\lambda(\tau)\) under
\(\mathrm{SL}(2,\mathbb{Z})\) forces conformal dimensions to be
rational. Imposing additionally that fusion multiplicities
\(N^{ij}_k \in \mathbb{Z}_{\geq 0}\) (non-negativity, which requires the
vacuum normalization convention \(\lVert\lvert 0\rangle\rVert = 1\), a
choice parallel to the identity limit (I) of P4.2) forces the
Chern-Simons level \(k \in \mathbb{Z}_{\geq 0}\). The mechanism: quantum
dimension \(\dim_q(j) = \sin((j+1)\pi/(k+2))/\sin(\pi/(k+2))\) vanishes
at \(j = k+1\) (null representation, Kac-Walton truncation), forcing the
primary-field spectrum to the finite set
\(j = 0, \tfrac{1}{2}, \ldots, \tfrac{k}{2}\), which is equivalent to
\(k \in \mathbb{Z}_{\geq 0}\). Two independent derivations confirm this:
(a) algebraic, via modular-S-matrix positivity in the Verlinde formula
{[}Verlinde1988{]}; (b) topological, via the \(2\pi\)-periodicity of the
Wess-Zumino term under gauge transformations (\(\pi_3(G) = \mathbb{Z}\)
for simple \(G\)) {[}Witten1989{]}, forcing \(k \in \mathbb{Z}\). The
full deformation parameter \(q_{\mathrm{QG}} = e^{2\pi i/(k+g^\vee)}\)
is not forced at Stage 3.5: the dual Coxeter number \(g^\vee\) arises
from the conformal dimension of the adjoint representation
\(h_{\mathrm{adj}} = g^\vee / 2(k+g^\vee)\), which is group-theoretic
dynamical content. The forcing chain thus has a precise intermediate
step: Stage 3.5 forces the level \(k \in \mathbb{Z}\) from Verlinde
fusion-algebra consistency; Stage 4 forces the quantum group parameter
\(q_{\mathrm{QG}}\) from cobordism unitarity and semisimplicity (Remark
P9.2 below, {[}ReshetikhinTuraev1991{]}).

\texttt{Remark\ P9.2\ (q-Deformed\ forcing\ at\ Stage\ 4).} The forcing
pattern of P4.2 has a Stage 4 analog in Chern-Simons theory. For a 3D
topological field theory with gauge group \(G\), the requirement that
the sewing law (Atiyah composition on 3-manifolds) extend to a unitary,
normalized symmetric monoidal functor
\(Z\colon \mathrm{Bord}_3 \to \mathrm{Vect}\) forces the deformation
parameter to \(q = e^{2\pi i/(k+g^\vee)}\), where
\(k \in \mathbb{Z}_{\geq 0}\) is the level and \(g^\vee\) is the dual
Coxeter number of \(G\) {[}ReshetikhinTuraev1991{]}. The parallel with
P4.2 is structural: at Stage 2, (C)+(D)+(I) forces \(\hbar\) in the
partition channel; at Stage 4, cobordism composition + unitarity +
normalization forces \(q\) in the representation channel. In both cases,
composition alone is insufficient --- the additional constraint
(dimensional homogeneity at Stage 2; unitarity and semisimplicity at
Stage 4) is required. The deformation parameter \(q\) is \emph{not}
forced at the path-integral level (Stage 2) by any \(q\)-deformed analog
of (C): the coassociativity of \(U_q(\mathfrak{g})\) holds for all
\(q \in \mathbb{C}^*\), with no selection mechanism.

\texttt{Remark\ P9.3\ (Arithmetic\ rigidity\ progression\ of\ the\ forcing\ chain).}
The four forcing stages, traced along the Segal-sewing/cobordism
channel, exhibit a progression toward greater arithmetic rigidity in
their forced constants. Stage 2 (P4.2) forces
\(\kappa = \hbar \in \mathbb{R}_+\) (positive real, via dimensional
homogeneity (D)): the forced constant has no torsion. Stage 3 (P9.1b)
forces \(c/24 \in \mathbb{Q}\) (rational, given \(c \in \mathbb{Q}\),
via modular closure of \(\mathrm{SL}(2,\mathbb{Z})\)): the forced
constant is rational. Stage 3.5 (Remark P9.1b-Q1d) forces
\(k \in \mathbb{Z}_{\geq 0}\) (non-negative integer, via Verlinde fusion
non-negativity and \(\pi_3(G) = \mathbb{Z}\)): the forced constant is
integral. Stage 4 (P9.2, {[}ReshetikhinTuraev1991{]}) forces
\(q = e^{2\pi i/(k+g^\vee)} \in \mu_{k+g^\vee}\) (primitive root of
unity, via surgery finiteness of the modular tensor category): the
forced constant is torsion in \(\mathbb{C}^\times\). Each stage adds a
finiteness axiom driving the forced constant toward the torsion subgroup
of \(\mathbb{C}^\times\): the chain
\(\mathbb{R}_+ \to \mathbb{Q} \to \mathbb{Z} \to \mu_N\) mirrors the
filtration of \(\mathbb{C}^\times = \mathbb{R}_+ \times S^1\) by
arithmetic complexity. The progression is specific to composition in the
sewing channel; other composition-forcing mechanisms at Stage 3, such as
conformal-bootstrap associativity, produce generically irrational forced
constants (e.g., 3D Ising \(\Delta_\sigma \approx 0.518\)
{[}ElShowk2014{]}), so the arithmetic rigidity pattern is not universal
across all forcing channels. Accordingly, the ladder
\(\mathbb{R}_+ \to \mathbb{Q} \to \mathbb{Z} \to \mu_N\) is an a
posteriori pattern for this channel, not a theorem covering all Stage-3
forcings. Stages 2 and 4 together determine both components of the
quantum group deformation parameter: P4.2 fixes the norm
\(\lvert\kappa\rvert = \hbar \in \mathbb{R}_+\); the RT theorem fixes
the phase \(\arg(q) = 2\pi/(k+g^\vee)\) to a torsion element. The
partition functions of the associated TQFTs satisfy
\(Z(M^3) \in \mathbb{Z}[\zeta_N, N^{-1}]\), \(N = k + g^\vee\),
reflecting the cyclotomic integrality of Stage 4 {[}Murakami1995{]}
{[}Habiro2008{]}. The forcing mechanism at Stage 2 rests on the
Stone--von Neumann uniqueness theorem for irreducible representations of
the Heisenberg algebra; at higher stages, where unitarily inequivalent
representations proliferate (Haag's theorem), each additional finiteness
axiom serves as a partial substitute for uniqueness, applicable only
within a narrower class of theories. The restriction at each stage to
theories admitting such a classification theorem (rational CFTs at
Stage\textasciitilde3, integrable representations at
Stage\textasciitilde3.5, modular tensor categories at
Stage\textasciitilde4) is therefore not a selection bias in the forcing
chain but an intrinsic consequence: composition can determine a specific
forced constant only within a class of theories where a uniqueness or
finiteness theorem is available.

\hypertarget{technical-appendices}{%
\section{10. Technical Appendices}\label{technical-appendices}}

This section provides the appendices announced at the end of Section 9.
Each subsection is a compact worked extension tied to one residual
vulnerability.

\hypertarget{worked-renormalization-template-single-coupling}{%
\subsection{10.1 Worked Renormalization Template (Single
Coupling)}\label{worked-renormalization-template-single-coupling}}

The objective is to replace purely structural RG language with one
explicit subtraction-and-running calculation.

Assume a regulated quantity has the perturbative form

\[
F_\Lambda(g_B;\mu)
=
g_B
+c\,g_B^2\ln\!\left(\frac{\Lambda}{\mu}\right)
+d\,g_B^2
+O(g_B^3),
\]

with dimensionless constants \(c,d\). Define a renormalized coupling by
a subtraction condition at scale \(\mu\):

\[
g_R(\mu)\equiv g_B+c\,g_B^2\ln\!\left(\frac{\Lambda}{\mu}\right).
\]

\texttt{Derivation\ D8.1\ (Finite\ renormalized\ prediction\ at\ fixed\ subtraction\ scale).}
Invert the definition to second order:

\[
g_B
=
g_R-c\,g_R^2\ln\!\left(\frac{\Lambda}{\mu}\right)+O(g_R^3).
\]

Substitute into \(F_\Lambda\):

\[
F_\Lambda
=
g_R
+d\,g_R^2
+O(g_R^3),
\]

so the explicit logarithmic cutoff dependence cancels at this order.
This is the concrete implementation of the Section 8 rule: tune bare
data so predictions at reference scale remain stable.

\texttt{Derivation\ D8.2\ (Running\ from\ cutoff-independence).} At
fixed bare coupling \(g_B\), differentiating the renormalization
condition gives

\[
\mu\frac{d g_R}{d\mu}
=
-c\,g_R^2+O(g_R^3)
\equiv
\beta(g_R).
\]

This turns divergent cutoff dependence into controlled scale dependence.

\texttt{Proposition\ P8.1\ (Leading\ beta\ coefficient\ under\ analytic\ scheme\ change).}
For a reparametrization \(g_R' = g_R + a\,g_R^2 + O(g_R^3)\), the
leading coefficient of \(\beta\) is unchanged:

\[
\beta'(g_R')=-c\,{g_R'}^2+O({g_R'}^3).
\]

So scheme changes shift higher-order terms while preserving the first
nontrivial flow coefficient in this template.

\texttt{Derivation\ D8.2a\ (One-loop\ QFT\ witness\ in\ fixed\ scheme:\ \textbackslash{}(\textbackslash{}lambda\textbackslash{}phi\^{}4\textbackslash{})\ near\ four\ dimensions).}
To make Section 8's structural RG statements explicit at QFT level,
consider scalar \(\lambda\phi^4\) theory in \(D=4-2\varepsilon\), with
minimal-subtraction-style parametrization \[
\lambda_B
=
\mu^{2\varepsilon}\!\left(
\lambda_R
+\frac{3}{16\pi^2}\frac{\lambda_R^2}{\varepsilon}
+O(\lambda_R^3)
\right).
\] Here the interaction convention is
\(\mathcal L_{\mathrm{int}}=\lambda_R\phi^4/4!\), which fixes the
one-loop coefficient \(3/(16\pi^2)\). Holding \(\lambda_B\) fixed and
differentiating with respect to \(\ln\mu\) gives \[
\beta(\lambda_R)\equiv \mu\frac{d\lambda_R}{d\mu}
=
-2\varepsilon\,\lambda_R
+\frac{3}{16\pi^2}\lambda_R^2
+O(\lambda_R^3).
\] At \(D=4\) (\(\varepsilon\to0\)): \[
\beta(\lambda_R)=\frac{3}{16\pi^2}\lambda_R^2+O(\lambda_R^3),
\qquad
\frac{1}{\lambda_R(\mu)}
=
\frac{1}{\lambda_R(\mu_0)}
-\frac{3}{16\pi^2}\ln\!\frac{\mu}{\mu_0}
+O(\lambda_R).
\] This is the field-theory analogue of \texttt{Derivation\ D6.2}:
logarithmic refinement dependence is traded for controlled scale running
in a fixed subtraction convention. Under an analytic scheme change
\(\lambda_R'=\lambda_R+a\lambda_R^2+O(\lambda_R^3)\), the coefficient
\(3/(16\pi^2)\) is unchanged at this order, matching
\texttt{Proposition\ P8.1}.

\hypertarget{orderingdiscretization-pair-with-same-classical-limit}{%
\subsection{10.2 Ordering/Discretization Pair with Same Classical
Limit}\label{orderingdiscretization-pair-with-same-classical-limit}}

This appendix gives an explicit example of the Section 6/Section 7 claim
that discretization choice changes \(O(\hbar)\) terms while preserving
classical dynamics.

Take the classical symbol \(A(q,p)=f(q)p\), with smooth \(f\). Consider
two quantizations: 1. Left ordering: \(Q_L(A)=f(\hat q)\hat p\). 2. Weyl
(symmetric) ordering:
\(Q_W(A)=\frac12\left(f(\hat q)\hat p+\hat p f(\hat q)\right)\).

Using \([\hat p,f(\hat q)]=-i\hbar f'(\hat q)\):

\[
Q_W(A)
=
f(\hat q)\hat p
-\frac{i\hbar}{2}f'(\hat q)
=
Q_L(A)-\frac{i\hbar}{2}f'(\hat q).
\]

\texttt{Derivation\ D9.1\ (Classical\ agreement,\ quantum\ shift).} The
difference operator is \(O(\hbar)\):

\[
Q_W(A)-Q_L(A)=-\frac{i\hbar}{2}f'(\hat q).
\]

Therefore

\[
\lim_{\hbar\to0}\big(Q_W(A)-Q_L(A)\big)=0
\]

in the formal classical limit, while quantum generators differ at
subleading order.

\texttt{Remark\ D9.1a\ (Quadratic\ symbols\ and\ half-density\ resolution).}
For the quadratic symbol \(A(q,p)=f(q)p^2\) (e.g.~kinetic energy with
position-dependent mass \(f=1/m\)), the same comparison yields \[
Q_W(fp^2)-Q_L(fp^2)=-i\hbar f'(\hat q)\hat p-\tfrac{1}{4}\hbar^2 f''(\hat q).
\] The correction now has two layers: an \(O(\hbar)\) first-order
differential operator and an \(O(\hbar^2)\) potential. In particular,
different orderings of \(p^2/m(q)\) disagree in the coefficient of the
first-derivative term \(i\hbar(m'/m^2)\hat p\). The half-density
conjugation \(|g|^{1/4}\Delta_g|g|^{-1/4}\) does not eliminate the
first-derivative (connection) term: both the Weyl prescription and the
half-density prescription share the same connection term
\(f'\partial_q\) (as required by formal self-adjointness on
\(L^2(\mathbb R,dq)\)). They differ only at the next layer: the
\(O(\hbar^2)\) scalar potential, with
\(\hat H_W-\hat H_{\mathrm{HD}}=-\hbar^2 f'^2/(32mf)\) (a purely
multiplicative operator, no derivatives). This supports a four-layer
stratification of ordering differences: (1) principal symbol --- all
prescriptions agree; (2) connection (first-derivative) --- fixed by
self-adjointness, independent of ordering; (3) scalar \(O(\hbar^2)\) ---
genuine deformation freedom persists; (4) operator domain ---
independent. The half-density prescription is a canonical representative
within the deformation equivalence class (like Lorenz gauge), not a
different physics. Explicit energy-shift estimates for
position-dependent mass \(f(q)=1+\alpha q^2\) in a harmonic trap show
\(|\Delta E_0|\sim O(\alpha^2)\), with the first-order shift vanishing
identically and the leading correction unmeasurably small
(\(\sim 0.01\)--\(0.06\) meV for GaAs quantum wells, below current
resolution thresholds). This confirms that deformation equivalence
(Proposition P5.2) is physical, not merely formal (cf.~Derivation
HD-D1.3 in the half-density companion note).

\texttt{Derivation\ D9.1b\ (Periodic-domain\ symmetry\ witness\ for\ \textbackslash{}(Q\_L\textbackslash{})\ vs\ \textbackslash{}(Q\_W\textbackslash{})).}
Take configuration space \(S^1\) with coordinate \(q\in[0,2\pi)\),
Hilbert space \(L^2(S^1,dq)\), and periodic Sobolev domain
\(H^1_{\mathrm{per}}(S^1)\). Let \(f\in C^1(S^1,\mathbb R)\). Define \[
Q_L=-i\hbar\,f(q)\partial_q,\qquad
Q_W=-i\hbar\!\left(f(q)\partial_q+\frac12 f'(q)\right).
\] For \(u,v\in H^1_{\mathrm{per}}(S^1)\), integration by parts with
periodic boundary cancellation gives \[
\langle u,Q_L v\rangle-\langle Q_L u,v\rangle
=
i\hbar\int_0^{2\pi}\overline{u(q)}\,f'(q)\,v(q)\,dq,
\] while for the Weyl representative the extra \(\frac12 f'\) terms
cancel: \[
\langle u,Q_W v\rangle-\langle Q_W u,v\rangle=0.
\] Hence \(Q_W\) is symmetric on \(H^1_{\mathrm{per}}(S^1)\) for real
\(f\), whereas \(Q_L\) is symmetric only for \(f' = 0\). This is an
explicit operator-domain boundary behind the \(O(\hbar)\) ordering
difference of \texttt{Derivation\ D9.1}.

\texttt{Remark\ D9.1c\ (Scope\ boundary\ for\ domain\ claims).} The
witness above establishes symmetry on the stated periodic domain; it
does not claim essential self-adjointness or classify self-adjoint
extensions in singular/degenerate-coefficient cases.

\texttt{Derivation\ D9.1d\ (Curved-manifold\ kinetic\ benchmark\ via\ half-density\ conjugation).}
Let \((M,g)\) be a compact Riemannian manifold without boundary. Write
\(d\mathrm{vol}_g=|g|^{1/2}dx\) in a local chart \(x\), and define \[
U: L^2(M,d\mathrm{vol}_g)\to L^2(M,dx),\qquad (U\psi)(x)=|g(x)|^{1/4}\psi(x).
\] The Laplace-Beltrami kinetic operator \[
H_g:=-\frac{\hbar^2}{2}\Delta_g,\qquad \Delta_g=|g|^{-1/2}\partial_i\!\left(|g|^{1/2}g^{ij}\partial_j\right),
\] is symmetric on \(H^2(M,d\mathrm{vol}_g)\). Conjugating by \(U\)
gives \[
\widetilde H_g:=U H_g U^{-1}
=-\frac{\hbar^2}{2}\,|g|^{1/4}\Delta_g|g|^{-1/4}
\] on domain \(U(H^2(M,d\mathrm{vol}_g))\subset L^2(M,dx)\), and
symmetry is preserved by unitarity: \[
\langle u,\widetilde H_g v\rangle_{dx}
=\langle U^{-1}u,H_g U^{-1}v\rangle_{d\mathrm{vol}_g}
=\langle \widetilde H_g u,v\rangle_{dx}.
\] This gives a curved-manifold, operator-domain witness that the
half-density prescription is not a cosmetic rewrite: it is the
symmetry-preserving transport of the geometric kinetic operator.

\texttt{Derivation\ D9.1e\ (Naive\ left\ kinetic\ operator\ fails\ symmetry\ in\ generic\ charts).}
On the same chart domain (with boundary terms suppressed by
compactness/periodicity), define the left-ordered principal-symbol
operator \[
H_L:=-\frac{\hbar^2}{2}\,g^{ij}(x)\partial_i\partial_j.
\] For smooth \(u,v\), repeated integration by parts yields \[
\langle u,H_L v\rangle_{dx}-\langle H_L u,v\rangle_{dx}
=\frac{\hbar^2}{2}\int dx\;(\partial_i g^{ij})\big(\overline{u}\,\partial_j v-(\partial_j\overline{u})\,v\big).
\] Hence \(H_L\) is symmetric only under extra coordinate/coefficient
constraints (e.g.~\(\partial_i g^{ij}=0\) in the chosen chart). In
general curved coordinates, left ordering breaks symmetry while the
half-density-conjugated Laplace-Beltrami form remains symmetric by
construction (\texttt{Derivation\ D9.1d}).

\texttt{Proposition\ D9.1h\ (Curved-manifold\ ordering\ witness:\ spectral\ comparison\ on\ \textbackslash{}(S\^{}2\textbackslash{})).}
On the unit sphere \(S^2\) with coordinates \((\theta,\phi)\) and metric
\(g=d\theta^2+\sin^2\!\theta\,d\phi^2\), define on
\(L^2(d\theta\,d\phi)\): \[
H_L=-\partial_\theta^2-\frac{1}{\sin^2\!\theta}\,\partial_\phi^2,
\qquad
\widetilde{H}=|g|^{1/4}(-\Delta_g)|g|^{-1/4}=H_L+V_{\mathrm{HD}},
\] where
\(V_{\mathrm{HD}}(\theta)=-\tfrac{1}{4}-\tfrac{1}{4\sin^2\!\theta}\).
Then: 1. Both operators are essentially self-adjoint on
\(C^\infty(S^2)\) (compact, no boundary). 2. \(\widetilde{H}\) has
eigenfunctions \((\sin\theta)^{1/2}Y_l^m\) with eigenvalues
\(l(l{+}1)\), reproducing the Laplace-Beltrami spectrum. 3. The spectra
differ: \(\mathrm{Spec}(\widetilde{H})=\{l(l{+}1):l\ge0\}\) while
\(\mathrm{Spec}(H_L)\supset\{n^2:n\ge1\}\), with shift \(-(l{+}1)\)
growing linearly in \(l\). 4. The ordering difference is a pure Layer-3
scalar potential \(V_{\mathrm{HD}}\); no Layer-4 domain freedom appears.

This is the first Appendix 10.2 witness with an explicit spectral
comparison on a curved manifold. The connection term
\(\cot\theta\,\partial_\theta\) of \(\Delta_g\) is traded for the scalar
\(V_{\mathrm{HD}}\), demonstrating concretely the mechanism described
abstractly in \texttt{Derivation\ D9.1d}.

\texttt{Proposition\ D9.1i\ (Curved-manifold\ ordering\ witness:\ spectral\ comparison\ on\ \textbackslash{}(S\^{}3\textbackslash{})).}
On the unit 3-sphere \(S^3\cong\mathrm{SU}(2)\) with hyperspherical
coordinates \((\chi,\theta,\phi)\) and metric
\(ds^2=d\chi^2+\sin^2\!\chi\,(d\theta^2+\sin^2\!\theta\,d\phi^2)\),
define on \(L^2(d\chi\,d\theta\,d\phi)\): \[
H_L=-\partial_\chi^2-\frac{1}{\sin^2\!\chi}\bigl(\partial_\theta^2+\frac{1}{\sin^2\!\theta}\,\partial_\phi^2\bigr),
\qquad
\widetilde{H}=|g|^{1/4}(-\Delta_g)|g|^{-1/4}=H_L+V_{\mathrm{HD}},
\] where
\(V_{\mathrm{HD}}(\chi,\theta)=-1-\frac{1}{4\sin^2\!\chi}-\frac{1}{4\sin^2\!\chi\,\sin^2\!\theta}\).
Then: 1. Both operators are essentially self-adjoint on
\(C^\infty(S^3)\). 2. \(\widetilde{H}\) has eigenvalues \(l(l{+}2)\)
with degeneracy \((l{+}1)^2\), reproducing the Laplace--Beltrami
spectrum. The Peter--Weyl decomposition of \(L^2(\mathrm{SU}(2))\)
identifies these as quadratic Casimir values. 3.
\(\mathrm{Spec}(\widetilde{H})=\{l(l{+}2):l\ge0\}\) while
\(\mathrm{Spec}(H_L)\supset\{n^2:n\ge1\}\), with constant shift
\(l(l{+}2)-(l{+}1)^2=-1\). 4. The ordering difference is a pure Layer-3
scalar potential; no Layer-4 domain freedom appears. In left-invariant
coordinates on \(\mathrm{SU}(2)\cong S^3\), \(V_{\mathrm{HD}}=-R/6=-1\)
(constant, Remark D9.1j); the non-constant geodesic-polar expression
reflects coordinate dependence (Remark D9.1n).

Unlike the \(S^2\) witness (Proposition D9.1h), where the spectral shift
\(-(l{+}1)\) grows linearly, the \(S^3\) spectral shift is uniform
(\(-1\)). In the general \(S^d\) family, the full half-density potential
is
\(V_{\mathrm{HD}}=-\alpha^2+\alpha(\alpha{-}1)/\sin^2 r + (\sin r)^{-2}\,V_{\mathrm{HD}}^{S^{d-1}}(\Omega)\),
where the angular V\_HD of the sub-sphere contributes a
position-dependent term for all \(d\ge2\). The \emph{spectral} shift is
constant iff \(d=3\); this is an intrinsic statement independent of the
coordinate-dependent V\_HD. Since \(S^3\) is the spatial section of
four-dimensional de Sitter spacetime, this gives a fourth independent
\(D=4\) coincidence of the half-density framework: the compositionally
forced ordering on the de Sitter spatial section produces a
\emph{spectrally} uniform correction (constant shift, no
position-dependent distortion in the spectrum), only a vacuum energy
shift.

\texttt{Remark\ D9.1j\ (Scope\ boundary\ for\ curved\ spectral\ witnesses).}
Propositions D9.1h and D9.1i cover the maximally symmetric compact
spaces \(S^2\) and \(S^3\). On any compact Lie group with bi-invariant
metric, \(V_{\mathrm{HD}}\) is constant \emph{in left-invariant
coordinates} (the bi-invariance of the volume form forces the
half-density conjugation to commute with group translations);
\(S^3 = \mathrm{SU}(2)\) is the unique case where this coincides with
constant sectional curvature. Extension to non-homogeneous spaces or
higher-dimensional spheres with position-dependent \(V_{\mathrm{HD}}\)
remains open.

\texttt{Proposition\ D9.1k\ (Non-compact\ ordering\ witness:\ unit\ \textbackslash{}(H\^{}2\textbackslash{})).}
On the hyperbolic plane \(H^2\) (constant curvature \(K=-1\)) with
geodesic radial coordinate \(\rho\in[0,\infty)\) and metric
\(ds^2=d\rho^2+\sinh^2\!\rho\,d\phi^2\), define on
\(L^2(d\rho\,d\phi)\): \[
H_L=-\partial_\rho^2-\frac{1}{\sinh^2\!\rho}\,\partial_\phi^2,
\qquad
\widetilde{H}=|g|^{1/4}(-\Delta_g)|g|^{-1/4}=H_L+V_{\mathrm{HD}},
\] where
\(V_{\mathrm{HD}}(\rho)=\tfrac{1}{4}-\tfrac{1}{4\sinh^2\!\rho}\). Then:
1. \(\widetilde{H}\) has purely continuous spectrum \([1/4,\infty)\),
matching the Laplace--Beltrami operator (McKean's theorem). The
left-ordered \(H_L\) has spectrum \([0,\infty)\). 2. The spectral gap
\(1/4\) equals \(-R/8\) where \(R=-2\) is the scalar curvature. The
half-density ordering recovers this gap; the left ordering erases it. 3.
The ordering difference is a pure Layer-3 scalar potential, with
\(V_{\mathrm{HD}}\to1/4\) as \(\rho\to\infty\).

Combined with the compact witnesses (Propositions D9.1h--D9.1i), this
covers positive and negative curvature, compact and non-compact
topology, and discrete and continuous spectra.

\texttt{Remark\ D9.1l\ (Unified\ constant-curvature\ formula).} On
\(S^d\) (respectively \(H^d\)) of unit radius, the half-density
potential takes the form
\(V_{\mathrm{HD}}=-\alpha^2+\alpha(\alpha{-}1)/\sin^2 r\)
(resp.~\(+\alpha^2+\alpha(\alpha{-}1)/\sinh^2 r\)) with
\(\alpha=(d{-}1)/2\). The constant part satisfies
\(V_{\mathrm{HD}}(\mathrm{const})=-(d{-}1)R/(4d)\) where \(R\) is the
scalar curvature. This coupling is distinct from conformal coupling
\(\xi_c=(d{-}2)/(4(d{-}1))\) for all integer \(d\ge2\). More generally,
on any Riemannian manifold, \(V_{\mathrm{HD}}(p)=-R(p)/6\) at the center
of Riemann normal coordinates at \(p\) (since \(|g(0)|=1\) and
\(|g(x)|^{-1/4}=1+\frac{1}{12}R_{ij}x^ix^j+O(|x|^3)\) in RNC). On a
compact Lie group with bi-invariant metric, bi-invariance forces
\(V_{\mathrm{HD}}\) to be constant in left-invariant coordinates (Remark
D9.1j), so \(V_{\mathrm{HD}}=-R/6\) globally in that chart. The two
formulas agree (i.e., \((d{-}1)/(4d)=1/6\)) only for \(d=3\), confirming
that \(S^3\cong\mathrm{SU}(2)\) is the unique sphere where the radial
V\_HD is constant in geodesic polars and matches the RNC value.

\texttt{Remark\ D9.1l\textquotesingle{}\ (Universal\ potential\ mirror).}
Although \(V_{\mathrm{HD}}\) on a \(d\)-dimensional spatial section is
distinct from the \(d\)-dimensional conformal coupling
\(\xi_c(d)=(d{-}2)/(4(d{-}1))\), it \emph{equals} the conformal coupling
in one higher dimension:
\(\xi_{\mathrm{conf}}(D{=}d{+}1)=(D{-}2)/(4(D{-}1))=(d{-}1)/(4d)\). Thus
\(V_{\mathrm{HD}}(d)+V_{\mathrm{conf}}(D{=}d{+}1)=0\) identically for
all \(d\). This universal mirror is the algebraic reason why the
half-density ordering potential on the spatial section always mirrors
the spacetime conformal coupling. The special role of \(d=3\) (\(D=4\))
arises not from the potential mirror (which is universal) but from two
independent mechanisms: (i)\textasciitilde the algebraic identity
\((d{-}1)/(4d)=1/6\) at \(d=3\) makes \(a_1=R/6-\xi R=0\), and
(ii)\textasciitilde the conformal eigenvalues on \(S^3\) are perfect
squares \((l{+}1)^2\), and the resulting Jacobi theta structure
eliminates all polynomial corrections in the heat trace asymptotic
expansion, producing the universal factor \(d(d{-}1)(d{-}3)\) in the
Seeley--DeWitt coefficients and forcing \(a_k=0\) for \(k\ge2\).
Together, the compositionally-forced conformal scalar on \(S^3\) has
\(a_k=0\) for all \(k\ge1\), making the de\textasciitilde Sitter vacuum
energy maximally curvature-insensitive (Remark\textasciitilde D9.1q,
re-scoped to conformal operator).

\texttt{Remark\ D9.1m\ (Scope\ boundary\ for\ non-compact\ spectral\ witnesses).}
The \(H^2\) witness exploits maximal symmetry and radial decomposition.
Extension to non-homogeneous negative-curvature manifolds,
variable-curvature spaces, or Lorentzian signature remains open.

\texttt{Remark\ D9.1n\ (Chart\ dependence\ vs\ intrinsic\ content).} The
pointwise value of
\(V_{\mathrm{HD}}(x)=-|g(x)|^{1/4}\Delta_g(|g(x)|^{-1/4})\) depends on
the coordinate chart (e.g., on \(S^2\) at the equator: \(-1/2\) in
spherical coordinates, \(-R/6=-1/3\) in Riemann normal coordinates).
However, the spectral comparison
\(\mathrm{Spec}(\widetilde{H})\neq\mathrm{Spec}(H_L)\) is intrinsic:
both operators are chart-independently defined, and their spectra are
coordinate-invariant. All witnesses in this appendix are stated as
spectral identities, hence chart-independent.

\texttt{Remark\ D9.1o\ (Weyl\ vector\ formula\ on\ compact\ Lie\ groups).}
On a compact semisimple Lie group \(G\) with bi-invariant metric
\(g(X,Y)=-2\,\mathrm{Tr}(XY)\) (Gell-Mann/ON normalization), the
half-density ordering potential \(V_{\mathrm{HD}}\) is constant (Remark
D9.1j) with value \[
V_{\mathrm{HD}}(G)=-|\rho|^2_g,
\] where \(\rho=\tfrac{1}{2}\sum_{\alpha\in\Phi^+}\alpha\) is the Weyl
vector and \(|\cdot|_g\) is the metric-dual norm on the Cartan
subalgebra. Equivalently, via the Freudenthal--de Vries formula,
\(V_{\mathrm{HD}}=-\dim(G)\,h^\vee/24\) in the Cartan--Killing
normalization (\(|\alpha_{\mathrm{long}}|^2=2\)). \emph{Proof:} By
Remark D9.1j, \(V_{\mathrm{HD}}\) is constant on \(G\). Evaluating at
the identity in Riemann normal coordinates (\(|g(0)|=1\)), the standard
expansion \(|g|^{-1/4}=1+\tfrac{1}{12}R_{ij}x^ix^j+O(|x|^3)\) gives
\(V_{\mathrm{HD}}=-R/6\) {[}DeWitt1957{]}. The Freudenthal--de Vries
identity \(R/6=|\rho|^2_g\) then yields the stated formula. Numerical
cross-check (finite-difference \(\Delta_g(|g|^{-1/4})\) in exponential
coordinates): \(\mathrm{SU}(2):-1/4\), \(\mathrm{SU}(3):-1\),
\(\mathrm{SU}(4):-5/2\), all matching \(-|\rho|^2_g\) to \(10^{-7}\).
The constant-curvature formula \(-(d{-}1)R/(4d)\) of Remark D9.1l
coincides with \(-|\rho|^2_g\) only for \(\mathrm{SU}(2)\cong S^3\)
(constant sectional curvature); for higher-rank groups they diverge,
with \(-|\rho|^2_g\) always smaller in magnitude.

\texttt{Remark\ D9.1o\textquotesingle{}\ (Duflo\ isomorphism\ and\ half-density\ on\ Lie\ groups).}
On a compact semisimple Lie group \(G\) with bi-invariant metric, the
half-density factor \(|g(x)|^{1/4}\) in exponential coordinates equals
the absolute value of the Duflo factor:
\(|g(x)|^{1/4}=|\det^{1/2}(\sinh(\mathrm{ad}(x)/2)/(\mathrm{ad}(x)/2))|\).
This identification follows from \(\mathrm{tr}(\mathrm{ad}(x))=0\) for
semisimple \(\mathfrak{g}\). The Duflo isomorphism
\(j^{1/2}\colon S(\mathfrak{g})^G\to Z(U(\mathfrak{g}))\)
{[}Duflo1977{]} maps the quadratic Casimir to \(-\Delta_G+|\rho|^2\),
which is the conformal operator \(-\Delta_G+R/6\) (via Freudenthal--de
Vries). The half-density conjugation of P4.2 thus coincides with the
Duflo correction to quantization on Lie groups, and the conformal
operator is the Duflo-corrected Laplacian. This explains the exponential
Seeley--DeWitt structure \(a_k(-\Delta_G)=(R/6)^k/k!\) and the conformal
heat-kernel flatness \(a_k(-\Delta+R/6;G)=0\) for all \(k\ge 1\) on
compact simple Lie groups: the Duflo isomorphism trivializes the
heat-kernel asymptotics of the correctly quantized Laplacian. The
identification is specific to Lie groups with bi-invariant metrics
(where the exponential map Jacobian has a clean Lie-algebraic form); on
general manifolds, the half-density \(|g|^{1/4}\) has no Duflo-type
interpretation, but its role as the compositionally-forced measure
(P4.2) persists.

\texttt{Remark\ D9.1o\textquotesingle{}\textquotesingle{}\ (Exponential\ Seeley-\/-DeWitt\ structure\ on\ compact\ Lie\ groups).}
On any compact simple Lie group \(G\) with bi-invariant metric, the
Seeley--DeWitt coefficients of the bare Laplacian satisfy
\(a_k(-\Delta_G)=(R/6)^k/k!\) for all \(k\ge 0\). \emph{Proof sketch:}
The Peter--Weyl heat trace factorizes via the Weyl character formula.
Extending the sum from dominant weights to the full weight lattice
(using \(J(\mu)=0\) on Weyl chamber walls) and applying Poisson
summation, the leading term is a Gaussian integral of
\(J(\mu)^2\exp(-t|\mu|^2)\). Since
\(J(\mu)^2=\prod_{\alpha>0}\langle\mu,\alpha\rangle^2\) is homogeneous
of degree \(d-r\) (where \(r=\mathrm{rank}\)), this integral equals
\(t^{-d/2}\) times the Macdonald--Mehta constant --- a single power of
\(t\), with no polynomial corrections. Non-zero Fourier modes contribute
\(O(\exp(-c/t))\). Assembling:
\(K(t,e,e)=(4\pi t)^{-d/2}\exp(t|\rho|^2)+O(\exp(-c/t))\), giving
\(a_k=|\rho|^{2k}/k!=(R/6)^k/k!\). Corollary: the conformal operator
\(-\Delta_G+R/6\) has \(a_k=0\) for all \(k\ge 1\) on every compact
simple Lie group. Among rank-1 symmetric spaces,
\(\mathbb{CP}^2=\mathrm{SU}(3)/\mathrm{U}(2)\) also satisfies
\(|\rho_m|^2=R/6\) (a dimension-specific algebraic coincidence at
\(n=2\)) but fails conformal heat-kernel flatness because its spectral
multiplicities are odd-degree polynomials in the eigenvalue label, so
the Euler--Maclaurin boundary terms do not vanish; the exponential
Seeley--DeWitt structure is thus specific to Lie groups (where the
multiplicity function is an even polynomial).

\texttt{Remark\ D9.1p\ (Isospectrality\ of\ the\ half-density\ Laplacian).}
The half-density Laplacian
\(\Delta_{1/2}=|g|^{1/4}(-\Delta_g)|g|^{-1/4}\) is unitarily equivalent
to \(-\Delta_g\) via the unitary map \(U:f\mapsto |g|^{1/4}f\) from
\(L^2(M,\mathrm{dvol}_g)\) to \(L^2(M,dx)\). Therefore
\(\mathrm{Spec}(\Delta_{1/2})=\mathrm{Spec}(-\Delta_g)\) and all
Seeley--DeWitt coefficients agree:
\(a_k(\Delta_{1/2};M)=a_k(-\Delta_g;M)\) for all \(k\). In particular,
\(a_1(\Delta_{1/2})=R/6\neq 0\) generically. \emph{Caution:} The
decomposition \(\Delta_{1/2}=-\Delta_g+V_{\mathrm{HD}}\) omits
first-order drift terms \(W^i\partial_i\) arising from the conjugation.
When the drift is absorbed into a modified connection via the
Vassilevich standard form \(-(g^{ij}\nabla'_i\nabla'_j+E')\), the
effective endomorphism is \(E'=0\) (not \(-R/6\)), giving
\(a_1=R/6+E'=R/6\). The naive formula \(a_1=R/6+V_{\mathrm{HD}}=0\) is
incorrect.

\texttt{Remark\ D9.1q\ (Heat-kernel\ coefficients\ of\ the\ shifted\ operator\ on\ \textbackslash{}(S\^{}3\textbackslash{})).}
The shifted operator \(O_3=-\Delta_{S^3}+V_{\mathrm{HD}}\) (without
drift terms, eigenvalues \(l(l{+}2)-1\)) is distinct from the
conjugation \(\Delta_{1/2}\) (eigenvalues \(l(l{+}2)\)). On \(S^3\),
where \(V_{\mathrm{HD}}=-1\) is constant in left-invariant coordinates,
the heat trace of \(O_3\) satisfies
\(\mathrm{tr}\,e^{-tO_3}=e^t\,\mathrm{tr}\,e^{t\Delta_g}\), giving
Seeley--DeWitt coefficients \(a_k(O_3)=2^k/k!\). The Kluth--Litim
generating function \(\kappa_n(3)=\delta_{n,0}\) yields
\(a_k(O_3)-\sum_{j<k}\binom{k}{j}a_j(O_3)/k!=0\), consistent with the
product formula. The conformal scalar
\(-\Delta_{S^3}+R/6=-\Delta_{S^3}+1\) has eigenvalues \((l{+}1)^2\) and
is heat-kernel flat: \(a_k(-\Delta+R/6;S^3)=0\) for all \(k\ge1\). Among
round spheres \(S^d\) (\(d\ge2\)), this conformal heat-kernel flatness
is unique to \(d=3\) (equivalently \(D=4\)), via the universal factor
\(d(d{-}1)(d{-}3)\) in the Seeley--DeWitt coefficients; it constitutes a
fifth \(D=4\) coincidence of the half-density framework. (On compact
simple Lie groups with bi-invariant metric, conformal heat-kernel
flatness holds more broadly via the Killing form factorization
\(|{\mathrm{Riem}}|^2=|{\mathrm{Ric}}|^2\); the sphere-specific
selection mechanism is the Jacobi theta eigenvalue structure.)

\texttt{Derivation\ D9.1f\ (Domain-parameter\ witness:\ same\ symbol,\ inequivalent\ self-adjoint\ realizations).}
Consider the formal 1D kinetic operator \[
\widehat H_{\mathrm{form}}=-\frac{\hbar^2}{2m}\frac{d^2}{dx^2}
\] on \(C_c^\infty(\mathbb R\setminus\{0\})\). It is symmetric but not
self-adjoint; self-adjoint realizations are fixed by boundary data at
\(x=0\). A standard one-parameter family is the delta-contact extension
\[
\mathcal D(H_g)=\Bigl\{\psi\in H^2(\mathbb R\setminus\{0\})\cap H^1(\mathbb R):
\psi'(0^+)-\psi'(0^-)=\frac{2mg}{\hbar^2}\psi(0)\Bigr\},
\] with \(H_g\psi=\widehat H_{\mathrm{form}}\psi\) for \(x\neq0\).
Different \(g\) define inequivalent quantum theories while sharing the
same principal symbol \(p^2/(2m)\): for \(g<0\) there is one bound state
\[
E_B=-\frac{m g^2}{2\hbar^2},
\] whereas for \(g\ge0\) no bound state appears. So representation
compatibility in Package B requires explicit domain data in addition to
ordering data.

\texttt{Remark\ D9.1g\ (Scope\ boundary\ for\ extension\ witness).} This
is a witness-level extension family, not a full classification of all
self-adjoint extensions (e.g.~full \(U(2)\)-parameter boundary
conditions at a point).

\texttt{Proposition\ P10.2a\ (Discretization-ordering\ equivalence\ class\ statement).}
If two short-time kernel prescriptions map to \(Q_L\)-type and
\(Q_W\)-type representatives of the same classical symbol algebra, then
they define the same classical equations and differ only by controlled
\(O(\hbar)\) corrections. This is the worked version of the Section 6 to
Section 7 transition claim {[}Landsman1998{]}.

\hypertarget{foundational-compatibility-principle}{%
\subsection{10.3 Foundational Compatibility
Principle}\label{foundational-compatibility-principle}}

This appendix states a foundational compatibility principle aimed at the
manuscript's core objective.

\texttt{Principle\ P10.1\ (Refinement\ Compatibility\ Principle,\ RCP).}
A dynamical framework is admissible when three compatibility conditions
hold simultaneously: 1. \textbf{Partition compatibility}: composition
across temporal subdivisions preserves the same action-based extremal
equations in the refinement limit. 2. \textbf{Representation
compatibility}: alternative quantum representations
(ordering/discretization choices) agree in the classical limit and
differ only by controlled subleading corrections. 3. \textbf{Scale
compatibility}: observable predictions remain stable under composed
coarse/fine scale changes after parameter flow adjustment.

In compact form, for any prediction map \(\mathcal O\),

\[
\mathcal O
=
\mathcal O\circ\mathcal C_t
=
\mathcal O\circ\mathcal Q_\hbar
=
\mathcal O\circ\mathcal R_\Lambda,
\]

where \(\mathcal C_t\) is temporal composition/refinement,
\(\mathcal Q_\hbar\) is representation change within a fixed
classical-limit class, and \(\mathcal R_\Lambda\) is
scale-refinement/renormalization flow.

\texttt{Derivation\ D10.1a\ (Operational\ closure\ form:\ compatibility\ as\ “there\ exists\ \textbackslash{}(\textbackslash{}theta\textquotesingle{}\textbackslash{})”).}
The schematic equalities above suppress the crucial fact that each
operation generally requires a \textbf{parameter update} (coupling flow,
normalization change, or a controlled representation change) to land
back in the same admissible family. Concretely, the operators
\(\mathcal C_t,\mathcal Q_\hbar,\mathcal R_\Lambda\) can be instantiated
by indexed families: \(\mathcal C_t\) by a ``compose \(b\) fine steps
into one coarse step'' map \(\mathcal C_{b,h}\), \(\mathcal Q_\hbar\) by
a family \(\mathcal Q_\alpha\) of representation/ordering changes at
fixed \(\hbar\), and \(\mathcal R_\Lambda\) by
scale-compare/coarse-grain maps \(\mathcal R_b\) (with \(\Lambda\)
standing for whatever cutoff/subtraction convention parametrizes the
family being compared). Here \(h\) is the ruler at which we compare
predictions, \(b\) is a refinement/coarse-graining factor, and
\(\alpha\) labels a choice of representation within a fixed
classical-limit class. An operational way to state RCP is to write
predictions as a family \(\{\mathcal O_{h,\theta}\}\) indexed by \(h>0\)
and parameters \(\theta\), and require that for each operation there
exists an update map \(\tau\) such that the post-operation object is
again representable inside the same family: \[
\mathcal O_{h,\theta}
=
\mathcal O_{h,\tau_C(b,h;\theta)}\circ \mathcal C_{b,h}
=
\mathcal O_{h,\tau_Q(\alpha;\theta)}\circ \mathcal Q_\alpha
=
\mathcal O_{h,\tau_R(b;\theta)}\circ \mathcal R_b.
\] Written this way, compatibility is falsifiable: closure can fail when
no admissible \(\theta'\) exists. The manuscript's strongest
constructive witness is Proposition P4.2: under hypotheses (C), (L),
(I), (D), composition-compatible refinement of action-based dynamics
forces a structural constant \(\kappa\) with
\([\kappa]=[\mathrm{action}]\), and both \(\kappa\to0\) and
\(\kappa\to\infty\) limits fail---the former collapses composition to
Hamilton--Jacobi extremization with no distributional identity limit,
the latter trivializes weights. The simplest sub-case is the
normalization exponent: semigroup closure fixes \(A(t)\propto t^{-d/2}\)
(Derivation D4.1a); choosing any other power breaks closure.

\texttt{Remark\ D10.1b\ (What\ belongs\ to\ \textbackslash{}(\textbackslash{}theta\textbackslash{}):\ ordering\ data\ and\ domain\ data).}
The parameter bundle \(\theta\) in \texttt{Derivation\ D10.1a} includes
more than couplings: it also contains representation data such as
ordering choices and admissible operator domains/boundary conditions.
\texttt{Derivation\ D9.1f} gives a concrete witness: the same principal
symbol \(p^2/(2m)\) admits inequivalent self-adjoint realizations
indexed by contact parameter \(g\), with different spectra. So the
\(\mathcal Q_\hbar\)-channel is not ``ordering only''; closure may fail
unless domain data is transported as part of \(\theta\).

\texttt{Derivation\ D10.1\ (Bridge\ to\ sections\ 3-\/-8).} 1.
\textbf{Partition compatibility} (\(\mathcal C_t\)): Sections 3--4
(area-law refinement; action/Noether bridge). 2. \textbf{Representation
compatibility} (\(\mathcal Q_\hbar\)): Sections 6--7
(ordering/discretization choices with identical \(\hbar\to0\) limit). 3.
\textbf{Scale compatibility} (\(\mathcal R_\Lambda\)): Section 8 (RG
semigroup consistency).

Therefore the Newton-to-path-integral narrative is an implementation of
RCP rather than a sequence of disconnected formalisms.

\texttt{Remark\ D10.1c\ (Crown\ witnesses\ for\ each\ RCP\ channel).}
Each compatibility channel now has a constructive witness beyond the
structural bridge: \textbf{(1) Partition channel} (\(\mathcal C_t\)):
Proposition P4.2 proves \(\hbar\) is necessary (not merely convenient)
for composition closure---the partition-compatibility update map is
forced and its absence is catastrophic. \textbf{(2) Representation
channel} (\(\mathcal Q_\hbar\)): Derivation D9.1f shows domain data
(self-adjoint extension parameter) must be transported as part of
\(\theta\); inequivalent realizations share classical symbols but have
different spectra. \textbf{(3) Scale channel} (\(\mathcal R_\Lambda\)):
Remark H6.3 demonstrates that local contact-expansion data, combined
with analyticity (Padé, dispersion, Borel), reconstructs
non-perturbative global structure---the control map \(\tau\) accesses
poles, cuts, and instanton sectors from Taylor coefficients. The first
two witnesses make RCP constructive rather than axiomatic: they show not
just that compatibility can be required, but that it determines specific
structural constants and domain data. The third witness (scale channel)
is now partially constructive at the heuristic level: the partition
composition law (C), when applied to models with Borel-summable
perturbative sectors (2D delta model, CP(1) sigma model), forces the
positions of multi-instanton Borel singularities \(\{n\zeta_*\}\) to
form an additive semigroup from the leading singularity \(\zeta_1\),
given simple-pole Borel singularity type. The uniqueness is
conditional---it determines the semigroup structure of singularity
positions given the leading instanton scale, but not the leading scale
itself (which requires the physical coupling \(g_R(\mu)\)). The Stokes
constants (residues at \(n\zeta_*\)) are partially constrained: for
rank-2 models with two independent instanton types (actions
\(A_1, A_2\)), composition forces the mixed-sector Stokes constants to
satisfy \(C_{n,m} = C_{1,0}^n \cdot C_{0,1}^m\) at leading order
(non-resonant scope --- resonant bion sectors require additional
non-perturbative input). H6.3 remains a heuristic for unconditional
reconstruction; the instanton-lattice and Stokes-constant claims are
stated as conditional propositions (D6.4b, Lemma D6.6) below, under
explicit Borel/instanton-type assumptions (Écalle 1981 alien calculus
applied to the RCP scale channel).

\texttt{Proposition\ D6.4b\ (Instanton\ lattice\ rigidity,\ conditional).}
Assume: (i) the partition composition law (C); (ii) a model with
Borel-summable perturbative sector and simple-pole Borel singularity
type; (iii) a leading instanton action \(\zeta_1\). Then (C) forces the
multi-instanton Borel singularity positions to form the additive
semigroup \(\{n\zeta_1 : n\ge 1\}\), and under RG flow (scale channel),
the entire lattice runs rigidly: \(\zeta_n(\mu) = n\zeta_1(\mu)\)
(tautological from chain rule; the non-trivial content is the semigroup
structure). Scope: verified in the 2D delta model (QM) and CP(1) sigma
model (QFT). Attribution: Écalle (1981) alien calculus; the RCP-level
derivation from (C) is this paper's contribution.

\texttt{Lemma\ D6.6\ (Stokes\ constant\ factorization,\ conditional).}
Under the assumptions of D6.4b, for rank-2 models with two independent
instanton types (actions \(A_1, A_2\)), composition forces the
mixed-sector Stokes constants to satisfy
\(C_{n,m} = C_{1,0}^n \cdot C_{0,1}^m\) at leading order. Scope:
non-resonant sectors only; resonant bion sectors require additional
non-perturbative input.

\texttt{Heuristic\ H10.1\ (Foundational\ reading).} RCP can be
interpreted as a candidate foundational postulate: physical laws are
those statements that survive controlled changes of partition,
representation, and scale.

\hypertarget{appendix-summary}{%
\subsection{10.4 Appendix Summary}\label{appendix-summary}}

Appendix sections 10.1--10.3 close three technical gaps identified in
Section 9: 1. explicit renormalization subtraction/running, now
including a fixed-scheme one-loop QFT witness (10.1), 2. explicit
ordering/discretization \(O(\hbar)\) shift with fixed classical limit
(10.2), 3. explicit foundational compatibility principle unifying the
full chain (10.3).

Appendix 10.5 supplies a fully worked quantum-mechanical RG computation
(2D contact interaction) demonstrating divergence, subtraction, running
coupling, dimensional transmutation, and scheme dependence in a concrete
model. Appendix 10.6 adds an explicit regulated-kernel composition
witness with controlled regulator removal and a concrete failure mode
when admissibility assumptions are violated.

These additions do not alter the thesis; they increase computational
accountability of the existing chain.

\texttt{Remark\ D10.4a\ (Package-to-appendix\ map\ for\ fast\ navigation).}
For reader navigation: 1. \textbf{Package C/D (RG witness + truncation
control):} Appendix 10.1 with \texttt{D8.1}, \texttt{D8.2},
\texttt{D8.2a}, \texttt{P8.1}, Section 8.6 \texttt{D6.4},
\texttt{Remark\ D6.4a}, and Appendix 10.3 \texttt{Proposition\ D6.4b},
\texttt{Lemma\ D6.6}. 2. \textbf{Package B (ordering/domain/extension):}
Appendix 10.2 with \texttt{D9.1}, \texttt{D9.1a}, \texttt{D9.1b},
\texttt{D9.1d}, \texttt{D9.1e}, \texttt{D9.1f},
\texttt{Proposition\ D9.1h}, \texttt{Proposition\ D9.1i},
\texttt{Remark\ D9.1j}, \texttt{Proposition\ D9.1k},
\texttt{Remark\ D9.1l}, \texttt{Remark\ D9.1l\textquotesingle{}},
\texttt{Remark\ D9.1m}, \texttt{Remark\ D9.1n}, \texttt{Remark\ D9.1o},
\texttt{Remark\ D9.1p}, \texttt{Remark\ D9.1q}. 3. \textbf{Package A
(path-space/kernel closure ladder):} Appendix 10.6 with \texttt{D12.1},
\texttt{P12.1}, \texttt{D12.2}, \texttt{P12.2}, \texttt{D12.3}. 4.
\textbf{Package E (global compatibility map):} Section 9.1
\texttt{P7.1a} plus Appendix 10.3 \texttt{P10.1}, \texttt{D10.1a},
\texttt{D10.1b}, \texttt{Remark\ D10.1c}.

\hypertarget{singular-contact-interaction-as-an-explicit-rg-computation-2d-delta}{%
\subsection{10.5 Singular Contact Interaction as an Explicit RG
Computation (2D
Delta)}\label{singular-contact-interaction-as-an-explicit-rg-computation-2d-delta}}

Section 8 argues that RG is the scale-compatibility condition required
when refinement limits diverge. This appendix supplies a fully explicit
example in a singular quantum-mechanical model where the continuum
theory is defined only after a renormalization prescription is chosen.
The derivations below (D11.1--D11.3) are concrete instances of the
abstract renormalization template (D8.1--D8.2, Appendix 10.1) applied to
the 2D contact interaction: D11.1 evaluates the regulated loop
(cf.~D8.1's generic cutoff dependence), D11.2 defines the renormalized
coupling and derives the beta function (cf.~D8.2's running from
cutoff-independence), and D11.3 exhibits scheme dependence as coupling
reparametrization (cf.~P8.1's leading-coefficient universality). For a
perturbative-QFT-style treatment of this mechanism in quantum mechanics
(including the 2D delta interaction), see
{[}ManuelTarrach1994PertRenQM{]}. For a standard discussion of
delta-function potentials in two and three dimensions (and their
renormalization issues), see {[}Jackiw1991DeltaPotentials{]}.

\texttt{Remark\ D11.0a\ (Explicit\ reparametrization\ bridge\ from\ D8\ to\ D11).}
For the scale-track arrow
\texttt{D8.1-D8.2\ -\textgreater{}\ D11.2-D11.3}, pass to
inverse-coupling coordinates \(u:=1/g\), and compare D8's generic
denominator variable with the contact-model denominator
\(\mathcal D_\Lambda(E):=T(E;\Lambda)^{-1}\). In these variables the
subtraction step is \[
u_R(\mu)=u_B+\frac{m}{2\pi\hbar^2}\ln\!\left(\frac{\Lambda^2}{\mu^2}\right),\qquad \ln\!\frac{\Lambda^2}{\mu^2}=2\ln\!\frac{\Lambda}{\mu},
\] making the D11 map the D8 template written in inverse-coupling
coordinates; finite analytic reparametrizations of \(u_R\)
(equivalently, local reparametrizations of \(g_R\) away from \(g_R=0\))
then match the scheme statement in \texttt{P8.1}.

Consider the two-dimensional contact interaction

\[
H
=
-\frac{\hbar^2}{2m}\Delta
+g\,\delta^{(2)}(x)
\quad \text{on }\mathbb R^2.
\]

The interaction is Dirac-supported and the naive continuum limit is
ill-defined: loop integrals diverge logarithmically.

\texttt{Derivation\ D11.1\ (Cutoff\ evaluation\ of\ the\ contact\ loop).}
Let \(E>0\) and write \(E=\hbar^2 k^2/(2m)\). The Lippmann--Schwinger
equation yields an algebraic \(T\)-matrix

\[
T(E;\Lambda)
=
\frac{1}{g_B(\Lambda)^{-1}-I(E;\Lambda)},
\]

where the loop integral is the free resolvent at the origin with a
wavevector cutoff \(|q|<\Lambda\):

\[
I(E;\Lambda)
=
\int_{|q|<\Lambda}\frac{d^2q}{(2\pi)^2}\,
\frac{1}{E-\frac{\hbar^2 q^2}{2m}+i0}
=
-\frac{m}{2\pi\hbar^2}\left[\ln\!\left(\frac{\Lambda^2}{k^2}\right)+i\pi\right]
+O\!\left(\frac{k^2}{\Lambda^2}\right).
\]

Thus the regulated theory contains a logarithmic divergence
\(\sim -\frac{m}{2\pi\hbar^2}\ln\Lambda^2\).

\texttt{Derivation\ D11.2\ (Renormalized\ coupling\ and\ beta\ function).}
Define a renormalized coupling at subtraction scale \(\mu\) by

\[
\frac{1}{g_R(\mu)}
\equiv
\frac{1}{g_B(\Lambda)}
+\frac{m}{2\pi\hbar^2}\ln\!\left(\frac{\Lambda^2}{\mu^2}\right).
\]

Substituting into \(T(E;\Lambda)\) cancels the explicit cutoff
dependence and gives a finite amplitude:

\[
T(E)
=
\frac{1}{
\frac{1}{g_R(\mu)}
+\frac{m}{2\pi\hbar^2}\ln\!\left(\frac{\mu^2}{k^2}\right)
+ i\,\frac{m}{2\hbar^2}
}.
\]

Since \(\mu\) is arbitrary, physical predictions must satisfy
\(dT/d\ln\mu=0\). This yields the RG equation

\[
\mu\frac{d}{d\mu}\left(\frac{1}{g_R(\mu)}\right)
=-\frac{m}{\pi\hbar^2},
\qquad
\beta(g_R)\equiv \mu\frac{d g_R}{d\mu}
=\frac{m}{\pi\hbar^2}\,g_R^2.
\]

This is the explicit ``scale-compatibility vector field'' promised by
Section 8, obtained from the demand that the subtraction scale not
affect the composed prediction. (For an alternative derivation via
explicit Wilsonian shell integration --- making the semigroup
composition
\(W_{\Lambda_1\to\Lambda_2}\circ W_{\Lambda\to\Lambda_1} = W_{\Lambda\to\Lambda_2}\)
directly visible as an identity of momentum-shell integrals ---
cf.~Derivation RG-D1.2a in the RG companion note.)

\texttt{Proposition\ P11.1\ (Dimensional\ transmutation:\ an\ RG-invariant\ bound-state\ scale).}
For \(E<0\), write \(E=-\hbar^2\kappa^2/(2m)\). The bound state
corresponds to a pole of \(T\), which occurs when

\[
\frac{1}{g_R(\mu)}
+\frac{m}{2\pi\hbar^2}\ln\!\left(\frac{\mu^2}{\kappa^2}\right)
=0.
\]

Define

\[
\kappa_\ast^2
\equiv
\mu^2\exp\!\left(\frac{2\pi\hbar^2}{m}\frac{1}{g_R(\mu)}\right).
\]

Using the RG equation for \(1/g_R(\mu)\), one checks
\(d\kappa_\ast/d\mu=0\). Thus the renormalized delta interaction trades
the regulator-dependent coupling for a physical scale \(\kappa_\ast\)
(equivalently a bound-state energy \(E_B=\hbar^2\kappa_\ast^2/(2m)\)).

\texttt{Derivation\ D11.3\ (Scheme\ dependence\ as\ rescaling\ of\ the\ transmutation\ scale).}
The subtraction defining \(g_R(\mu)\) is not unique: one may shift it by
a finite constant \(C\) by defining

\[
\frac{1}{g_R^{(C)}(\mu)}
\equiv
\frac{1}{g_R(\mu)}+\frac{m}{2\pi\hbar^2}C.
\]

Differentiation in \(\ln\mu\) removes the constant, so the beta function
is unchanged. However, the RG-invariant scale rescales:

\[
\kappa_{\ast}^{(C)\,2}
\equiv
\mu^2\exp\!\left(\frac{2\pi\hbar^2}{m}\frac{1}{g_R^{(C)}(\mu)}\right)
=e^{C}\,\kappa_\ast^2.
\]

Thus, in this one-scale model, ``scheme dependence'' is precisely the
freedom to rescale the single physical scale. Fixing one physical datum
(e.g.~\(E_B\)) fixes \(\kappa_\ast\) and removes the ambiguity from
predictions.

\hypertarget{regulated-kernel-composition-witness-euclidean-free-model}{%
\subsection{10.6 Regulated-Kernel Composition Witness (Euclidean Free
Model)}\label{regulated-kernel-composition-witness-euclidean-free-model}}

Section 9.4 identifies the path-space formalism as an open vulnerability
unless one can exhibit a regulated family with exact composition and
controlled regulator removal. The following Gaussian witness supplies
that structure in a model where all integrals are explicit. For explicit
kernel formulas in this subsection we use units \(m=\hbar=1\);
operator-norm bounds below are unchanged up to the corresponding
conventional rescalings.

\texttt{Derivation\ D12.1\ (Exact\ composition\ with\ additive\ regulator\ update).}
For \(t>0\), \(\varepsilon>0\), define \[
K_\varepsilon(x,y;t)
:=
\frac{1}{\bigl(2\pi(t+\varepsilon)\bigr)^{d/2}}
\exp\!\left[-\frac{|x-y|^2}{2(t+\varepsilon)}\right].
\] Since
\(K_\varepsilon(\cdot,\cdot;t)=K_0(\cdot,\cdot;t+\varepsilon)\),
Gaussian convolution gives, for \(t_1,t_2>0\) and
\(\varepsilon_1,\varepsilon_2>0\), \[
\int_{\mathbb R^d} d^dz\;
K_{\varepsilon_1}(x,z;t_1)\,
K_{\varepsilon_2}(z,y;t_2)
=
K_{\varepsilon_1+\varepsilon_2}(x,y;t_1+t_2).
\] Thus composition is exact inside the regulated family, with regulator
flow law \(\varepsilon\mapsto\varepsilon_1+\varepsilon_2\).

\texttt{Proposition\ P12.1\ (Controlled\ regulator\ removal\ and\ explicit\ failure\ mode).}
For fixed \(t>0\), \(K_\varepsilon(x,y;t)\to K_0(x,y;t)\) pointwise and
in \(L^1_x\) as \(\varepsilon\to0^+\) (for \(\varepsilon\le t/2\),
\(|K_\varepsilon(x,y;t)|\le (2\pi t)^{-d/2}\exp(-|x{-}y|^2/(3t))\in L^1_x\);
dominated convergence gives \(L^1\) convergence), so \[
\lim_{\varepsilon_1,\varepsilon_2\to0^+}
\int d^dz\;K_{\varepsilon_1}(x,z;t_1)K_{\varepsilon_2}(z,y;t_2)
=
K_0(x,y;t_1+t_2),
\] recovering the standard heat-kernel semigroup. A concrete failure
mode is immediate: if \(t+\varepsilon\le 0\), the Gaussian normalization
is undefined/non-integrable, and composition no longer closes in the
admissible family. This gives a model-level realization of the
manuscript's compatibility logic: closure requires explicit
admissibility conditions on the refinement-regulator pair.

\texttt{Derivation\ D12.2\ (First-order\ potential\ perturbation:\ composition\ closure\ to\ \textbackslash{}(O(V)\textbackslash{})).}
Let \(V:\mathbb R^d\to\mathbb R\) be bounded, and define the first-order
(in \(V\)) regulated kernel by Duhamel expansion: \[
K_{\varepsilon,V}^{(1)}(x,y;t)
:=
K_\varepsilon(x,y;t)
-\int_0^t d\tau\int_{\mathbb R^d} d^dz\;
K_\varepsilon(x,z;t-\tau)\,V(z)\,K_\varepsilon(z,y;\tau).
\] Using \texttt{Derivation\ D12.1} for the free part and retaining
terms through \(O(V)\), \[
\int d^dz\;K_{\varepsilon,V}^{(1)}(x,z;t)\,K_{\varepsilon,V}^{(1)}(z,y;s)
=K_{\varepsilon,V}^{(1)}(x,y;t+s)+O(V^2).
\] The first-order term combines by splitting \([0,t+s]\) into
\([0,t]\cup[t,t+s]\): in the second interval set \(\tau=t+\sigma\), use
free-kernel composition to collapse intermediate integrations, and
recover the same single-time-convolution structure at total time
\(t+s\). Thus nontrivial potential data still fits the
refinement-composition narrative at controlled order.

\texttt{Remark\ D12.2a\ (Failure\ mode\ for\ singular\ attractive\ potentials).}
The \(O(V)\) formula requires the space-time convolution integral to be
finite. For distributional or too-singular attractive potentials (for
example, bare contact interactions in dimensions where renormalization
is required), the integral can diverge and \(K_{\varepsilon,V}^{(1)}\)
is not well-defined without extra renormalization/boundary data. This is
precisely the regime where the explicit RG treatment of Appendix 10.5
becomes necessary.

\texttt{Proposition\ P12.2\ (Quantitative\ remainder\ and\ composition-defect\ bounds\ for\ bounded\ \textbackslash{}(V\textbackslash{})).}
Let \(H_0=-\frac{\hbar^2}{2}\Delta\), \(T_0(t)=e^{-tH_0}\), and
\(T_V(t)=e^{-t(H_0+V)}\) on \(L^2(\mathbb R^d)\), with \(V\) a bounded
multiplication operator (\(H_0+V\) is self-adjoint on
\(H^2(\mathbb R^d)\) by Kato-Rellich) and \(M:=\|V\|_\infty\). Define
the first-order Duhamel approximation \[
T_V^{(1)}(t):=T_0(t)-\int_0^t T_0(t-\tau)\,V\,T_0(\tau)\,d\tau.
\] Then: 1. \textbf{Remainder bound} \[
\|T_V(t)-T_V^{(1)}(t)\|
\le e^{Mt}-1-Mt
\le \frac12 M^2 t^2 e^{Mt}.
\] 2. \textbf{Composition-defect bound (first-order approximation)} \[
\|T_V^{(1)}(t)T_V^{(1)}(s)-T_V^{(1)}(t+s)\|
\le C\,M^2\,(t+s)^2 e^{M(t+s)}
\] for a universal constant \(C\) (e.g.~\(C=1\), which is sharp; see
below).

Proof sketch: expand \(T_V\) by Duhamel to second order, bound iterated
integrals with semigroup norms \(\|T_0(r)\|\le1\),
\(\|T_V(r)\|\le e^{Mr}\), and use \[
T_V^{(1)}(t)T_V^{(1)}(s)-T_V^{(1)}(t+s)
=\big(T_V^{(1)}(t)-T_V(t)\big)T_V^{(1)}(s)
+T_V(t)\big(T_V^{(1)}(s)-T_V(s)\big)
+\big(T_V(t+s)-T_V^{(1)}(t+s)\big).
\] Thus \texttt{Derivation\ D12.2} has explicit quantitative control in
the bounded-potential regime, not only formal \(O(V)\) bookkeeping.

\texttt{Derivation\ D12.3\ (Exact\ nontrivial\ semigroup\ witness:\ Euclidean\ harmonic\ oscillator).}
For confining quadratic potential \(V(x)=\frac12\omega^2|x|^2\) with
\(\omega>0\), the Euclidean kernel in \(\mathbb R^d\) is the Mehler form
\[
K_\omega(x,y;t)
=
\left(\frac{\omega}{2\pi\sinh(\omega t)}\right)^{d/2}
\exp\!\left[
-\frac{\omega}{2\sinh(\omega t)}
\Big((|x|^2+|y|^2)\cosh(\omega t)-2x\!\cdot\! y\Big)
\right].
\] Gaussian integration in the intermediate variable gives, for
\(t_1,t_2>0\), \[
\int_{\mathbb R^d} d^dz\;K_\omega(x,z;t_1)K_\omega(z,y;t_2)
=K_\omega(x,y;t_1+t_2),
\] using standard hyperbolic identities (notably
\(\sinh(a+b)=\sinh a\cosh b+\cosh a\sinh b\) and the induced identity
for \(\coth(a+b)\)). Thus we obtain an all-order, nontrivial composition
witness (beyond free and first-order perturbative regimes). Defining
\(K_{\omega,\varepsilon}(x,y;t):=K_\omega(x,y;t+\varepsilon)\) with
\(\varepsilon>0\), the same calculation yields additive regulator flow:
\[
\int d^dz\;K_{\omega,\varepsilon_1}(x,z;t_1)K_{\omega,\varepsilon_2}(z,y;t_2)
=K_{\omega,\varepsilon_1+\varepsilon_2}(x,y;t_1+t_2).
\] Since \(K_{\omega,\varepsilon}(x,y;t)=K_\omega(x,y;t+\varepsilon)\)
and \(K_\omega(\cdot,y;t)\in L^1_x\) for all \(t>0\), the same dominated
convergence argument as in \texttt{Proposition\ P12.1} gives
\(K_{\omega,\varepsilon}\to K_\omega\) pointwise and in \(L^1_x\) as
\(\varepsilon\to0^+\), completing the regulated-removal chain for the
nontrivial witness.

\texttt{Remark\ D12.3a\ (Scope\ boundary\ for\ the\ exact\ benchmark).}
This exact closure witness is specific to confining quadratic potentials
(\(\omega>0\)) in Euclidean time. Inverted/nonconfining cases require
separate treatment and are outside the admissible class used here.

\texttt{Remark\ D12.3b\ (Sanity\ limits:\ free\ limit\ and\ short-time\ localization).}
Two immediate checks fix normalization and interpretation: 1.
\textbf{Free limit \(\omega\to0\)}: using
\(\sinh(\omega t)=\omega t+O((\omega t)^3)\),
\(\cosh(\omega t)=1+O((\omega t)^2)\), \[
K_\omega(x,y;t)\xrightarrow[\omega\to0]{}
\frac{1}{(2\pi t)^{d/2}}\exp\!\left(-\frac{|x-y|^2}{2t}\right)
=K_0(x,y;t).
\] 2. \textbf{Short-time limit \(t\to0^+\)}: \(K_\omega(\cdot,\cdot;t)\)
concentrates to \(\delta\) in distributions, matching the semigroup
initial condition. These checks ensure \texttt{Derivation\ D12.3} is
consistent with both the free witness (\texttt{D12.1}) and the standard
heat-kernel normalization at short times.

\hypertarget{references}{%
\section{References}\label{references}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  {[}Newton1687{]} Isaac Newton, \emph{Philosophiae Naturalis Principia
  Mathematica} (1687), Book I (limit methods and central-force
  geometry). Reference access point: Newton Project and standard
  translated editions.
\item
  {[}Noether1918{]} Emmy Noether, ``Invariante Variationsprobleme''
  (1918). English translation commonly used in modern mechanics
  references.
\item
  {[}Dirac1933{]} P. A. M. Dirac, ``The Lagrangian in Quantum
  Mechanics,'' \emph{Physikalische Zeitschrift der Sowjetunion} 3
  (1933), 64--72. (Commonly cited as the earliest explicit path-integral
  style phase-weighting statement.)
\item
  {[}Feynman1948{]} R. P. Feynman, ``Space-Time Approach to
  Non-Relativistic Quantum Mechanics,'' \emph{Reviews of Modern Physics}
  20 (1948), 367--387. DOI \texttt{10.1103/RevModPhys.20.367}. OA:
  Caltech author-repository PDF.
\item
  {[}Connes1994{]} Alain Connes, \emph{Noncommutative Geometry}
  (Academic Press, 1994). ISBN \texttt{978-0-12-185860-5}.
\item
  {[}Landsman1998{]} N. P. Landsman, \emph{Mathematical Topics Between
  Classical and Quantum Mechanics} (Springer, 1998), Springer Monographs
  in Mathematics. DOI \texttt{10.1007/978-1-4612-1680-3}. ISBN
  \texttt{978-0-387-98318-9}.
\item
  {[}ConnesKreimer2000{]} Alain Connes and Dirk Kreimer,
  ``Renormalization in quantum field theory and the Riemann-Hilbert
  problem I,'' \emph{Communications in Mathematical Physics} 210 (2000),
  249--273. DOI \texttt{10.1007/s002200050779}.
\item
  {[}Brouder1999{]} Ch. Brouder, ``Runge-Kutta methods and
  renormalization,'' arXiv:\texttt{hep-th/9904014} (2 Apr 1999).
\item
  {[}McLachlan2017{]} Robert I. McLachlan, Klas Modin, Hans Munthe-Kaas,
  Olivier Verdier, ``Butcher series: A story of rooted trees and
  numerical methods for evolution equations,'' arXiv:\texttt{1512.00906}
  (v3, 27 Feb 2017).
\item
  {[}BoyaRivero1994Contact{]} Luis J. Boya and Alejandro Rivero,
  ``Renormalization in 1-D Quantum Mechanics: contact interactions,''
  arXiv:\texttt{hep-th/9411081} (v1, 11 Nov 1994).
\item
  {[}ManuelTarrach1994PertRenQM{]} Cristina Manuel and Rolf Tarrach,
  ``Perturbative Renormalization in Quantum Mechanics,'' \emph{Physics
  Letters B} 328 (1994), 113--118. arXiv:\texttt{hep-th/9309013} (v1, 2
  Sep 1993). DOI \texttt{10.1016/0370-2693(94)90437-5}.
\item
  {[}Jackiw1991DeltaPotentials{]} R. Jackiw, ``Delta-function potentials
  in two- and three-dimensional quantum mechanics,'' MIT-CTP-1937 (Jan
  1991). Reprinted in \emph{M.A.B. Bég Memorial Volume} (World
  Scientific, 1991), pp.~25--42. OA mirror:
  \url{https://www.physics.smu.edu/scalise/P6335fa21/notes/Jackiw.pdf}.
\item
  {[}VanVleck1928Correspondence{]} J. H. Van Vleck, ``The Correspondence
  Principle in the Statistical Interpretation of Quantum Mechanics,''
  \emph{Proceedings of the National Academy of Sciences of the United
  States of America} 14(2) (1928), 178--188. DOI
  \texttt{10.1073/pnas.14.2.178}.
\item
  {[}deGosson2018ShortTimePropagators{]} Maurice A. de Gosson,
  ``Short-Time Propagators and the Born--Jordan Quantization Rule,''
  \emph{Entropy} 20(11) (2018), 869. DOI \texttt{10.3390/e20110869}. OA:
  PubMed Central (PMCID: PMC 7512447).
\item
  {[}Rosten2012ERG{]} Oliver J. Rosten, ``Fundamentals of the Exact
  Renormalization Group,'' \emph{Physics Reports} 511 (2012), 177--272.
  arXiv:\texttt{1003.1366} (v4, 15 Feb 2012). DOI
  \texttt{10.1016/j.physrep.2011.12.003}.
\item
  {[}Velhinho2017InfDimMeasure{]} José Velhinho, ``Topics of Measure
  Theory on Infinite Dimensional Spaces,'' \emph{Mathematics} 5(3)
  (2017), 44. DOI \texttt{10.3390/math5030044}. OA: MDPI.
\item
  {[}Groenewold1946ElementaryQM{]} H. J. Groenewold, ``On the Principles
  of Elementary Quantum Mechanics,'' \emph{Physica} 12 (1946), 405--460.
  DOI \texttt{10.1016/S0031-8914(46)80059-4}.
\item
  {[}Moyal1949StatisticalQM{]} J. E. Moyal, ``Quantum mechanics as a
  statistical theory,'' \emph{Proceedings of the Cambridge Philosophical
  Society} 45 (1949), 99--124. DOI \texttt{10.1017/S0305004100000487}.
\item
  {[}TongQMLectures{]} David Tong, ``Quantum Mechanics'' (lecture notes,
  no DOI). OA: lecture-note PDF. (Contains
  \(Y_{l,m}(\theta,\phi)=P_{l,m}(\cos\theta)e^{im\phi}\) as simultaneous
  eigenstates of \(L^2\) and \(L_z\).)
\item
  {[}Nauenberg2003KeplerArea{]} Michael Nauenberg, ``Kepler's Area Law
  in the Principia: Filling in some details in Newton's proof of Prop.
  1,'' \emph{Historia Mathematica} 30 (2003), 441--456.
  arXiv:\texttt{math/0112048}. DOI
  \texttt{10.1016/S0315-0860(02)00027-7}. (Defends Newton's continuum
  limit via Lemma 3; the polygonal construction has a well-defined limit
  parameterizing a continuous planar curve.)
\item
  {[}Pourciau2003{]} Bruce Pourciau, ``Newton's Argument for Proposition
  1 of the Principia,'' \emph{Archive for History of Exact Sciences} 57
  (2003), 267--311. DOI \texttt{10.1007/s00407-002-0062-x}. (Critically
  analyses the impulse assumption and identifies error-accumulation and
  planarity problems in Newton's limit argument.)
\item
  {[}Berkeley1734Analyst{]} George Berkeley, \emph{The Analyst; or, A
  Discourse Addressed to an Infidel Mathematician} (Dublin/London,
  1734). (Foundational critique of Newton's fluxions and Leibniz's
  infinitesimals --- the ``ghosts of departed quantities'' objection to
  evanescent limits. Historical precursor to modern constructive
  refinement approaches.)
\item
  {[}Nauenberg1994SymplecticNewton{]} Michael Nauenberg, ``Newton's
  early computational method for dynamics,'' \emph{Archive for History
  of Exact Sciences} 46 (1994), 221--252. DOI
  \texttt{10.1007/BF01686278}. (The impulse equations correspond to a
  canonical/symplectic mapping --- exact solutions of a Hamiltonian with
  impulsive forces. Discusses convergence and adaptive time-stepping.)
\item
  {[}Nauenberg2018GraphicalMethod{]} Michael Nauenberg, ``Newton's
  graphical method for central force orbits,'' \emph{American Journal of
  Physics} 86(10) (2018), 765--771. DOI \texttt{10.1119/1.5046424}.
  arXiv:\texttt{1810.05264}. (Explicitly identifies Newton's Proposition
  1 construction as a first-order symplectic integrator; shows discrete
  energy conservation and time-reversal invariance. OA author copy: UCSC
  Emeriti.)
\item
  {[}BatesWeinstein1997{]} Sean Bates and Alan Weinstein, ``Lectures on
  the Geometry of Quantization,'' Berkeley Mathematics Lecture Notes,
  vol.~8, AMS, 1997. ISBN \texttt{978-0-8218-0798-9}. OA:
  \url{https://math.berkeley.edu/~alanw/GofQ.pdf}. (Canonical reference
  for half-density formalism in geometric quantization; half-density
  kernels and composition.)
\item
  {[}ReshetikhinTuraev1991{]} N. Yu. Reshetikhin and V. G. Turaev,
  ``Invariants of 3-manifolds via link polynomials and quantum groups,''
  \emph{Inventiones Mathematicae} \textbf{103}, 547--598 (1991). DOI
  \texttt{10.1007/BF01239527}. (RT construction: ribbon categories +
  quantum groups → 3-manifold invariants; forces q\_QG =
  e\^{}\{2πi/(k+g∨)\} from unitarity of the modular tensor category.)
\item
  {[}Verlinde1988{]} Erik Verlinde, ``Fusion rules and modular
  transformations in 2D conformal field theory,'' \emph{Nuclear Physics
  B} \textbf{300}, 360--376 (1988). DOI
  \texttt{10.1016/0550-3213(88)90603-7}. (Derives fusion multiplicities
  N\^{}ij\_k from the modular S-matrix; non-negativity forces level
  quantization.)
\item
  {[}Witten1989{]} Edward Witten, ``Quantum field theory and the Jones
  polynomial,'' \emph{Communications in Mathematical Physics}
  \textbf{121}, 351--399 (1989). DOI \texttt{10.1007/BF01217730}.
  (Chern-Simons theory as 3D TQFT; k∈ℤ from π₃(G)=ℤ gauge invariance;
  q=e\^{}\{2πi/(k+g∨)\}.) Source:
  sources/witten1989-chern-simons-jones.md.
\item
  {[}Murakami1995{]} Hitoshi Murakami, ``Quantum SO(3)-invariants
  dominate the SU(2)-invariant of Casson and Walker,'' \emph{Math. Proc.
  Cambridge Philos. Soc.} \textbf{117} (1995), no. 2, 237--249. DOI
  \texttt{10.1017/S0305004100073084}. (Algebraic integrality of WRT-type
  SU(2)/SO(3) invariants at prime order roots of unity.)
\item
  {[}Habiro2008{]} Kazuo Habiro, ``A unified Witten-Reshetikhin-Turaev
  invariant for integral homology spheres,'' \emph{Invent. Math.}
  \textbf{171} (2008), no. 1, 1--81. DOI
  \texttt{10.1007/s00222-007-0071-0}. (Cyclotomic integrality: Z(M³) ∈
  ℤ{[}ζ\_N, N\^{}\{-1\}{]} for integral homology spheres.)
\item
  {[}ElShowk2014{]} Sheer El-Showk et al., ``Solving the 3d Ising Model
  with the Conformal Bootstrap II. c-Minimization and Precise Critical
  Exponents,'' arXiv:\texttt{1403.4545} (2014). (Reports
  \(\Delta_\sigma = 0.518154(15)\); used as a concrete
  irrational-dimension example in the conformal-bootstrap channel.)
\item
  {[}GoyalKnuthSkilling2010{]} Philip Goyal, Kevin H. Knuth, and John
  Skilling, ``Origin of complex quantum amplitudes and Feynman's
  rules,'' \emph{Physical Review A} \textbf{81}, 022109 (2010).
  arXiv:\texttt{0907.0909}. (Derives complex amplitudes, Feynman's sum
  and product rules, and the Born rule from composition of sequential
  measurement pairs plus continuity --- kinematic complement to the
  dynamical forcing in P4.2.)
\item
  {[}LuizOliveira2026{]} Fabricio Souza Luiz and Marcos César de
  Oliveira, ``Information Theory of Action: Reconstructing Quantum
  Dynamics from Inference over Action Space,'' arXiv:\texttt{2602.09984}
  (10 Feb 2026). (Independent information-theoretic reconstruction:
  composition in action space plus finite variance forces Gaussian
  kernels and an action-dimensional scale via the same Lévy--Khintchine
  exclusion.)
\item
  {[}PathIntegralNormalization{]} A. Rivero and A.I.Scaffold,
  ``Path-Integral Normalization: The d/2 Exponent as Composition
  Compatibility Datum,'' companion satellite paper in this series (in
  preparation, 2026). (Comprehensive treatment of the d/2 exponent
  across temporal composition, Van Vleck determinant, heat-kernel
  diffusion, renormalization thresholds, and Lévy-stable exclusion.)
\item
  {[}RCPFoundations{]} A. Rivero and A.I.Scaffold, ``Refinement
  Compatibility Principle: Foundations,'' companion satellite paper in
  this series (in preparation, 2026). (Axiom system for RCP;
  three-channel forcing hierarchy; Krein Q-function transport; forward
  connections to all satellite papers.)
\item
  {[}TangentGroupoidBridge{]} A. Rivero and A.I.Scaffold, ``Groupoid
  Composition and Quantization: The Pair-Groupoid Bridge,'' companion
  satellite paper in this series (in preparation, 2026). (Pair groupoid
  as sewing law; d/2 forced by Fourier multiplicativity and dimensional
  homogeneity; tangent groupoid as hbar-deformation; Wick rotation as
  A3.)
\item
  {[}DeWitt1957{]} Bryce S. DeWitt, ``Dynamical Theory in Curved Spaces.
  I. A Review of the Classical and Quantum Action Principles,''
  \emph{Reviews of Modern Physics} \textbf{29}(3), 377--397 (1957). DOI
  \texttt{10.1103/RevModPhys.29.377}. (Derives the RNC expansion of
  \(|g|^{-1/4}\) and the ordering potential \(V_{\mathrm{HD}}=-R/6\) at
  any point in Riemann normal coordinates; foundational reference for
  curved-space path-integral measure and operator ordering.)
\item
  {[}KleinertChervyakov2000{]} Hagen Kleinert and Aleksei Chervyakov,
  ``Reparametrization Invariance of Path Integrals,''
  arXiv:\texttt{quant-ph/0002008} (v1, 1 Feb 2000). (Derives the Van
  Vleck--Morette determinant \(\Delta^{1/2}\) from the global
  semigroup/composition property of the path integral; direct precedent
  for P4.2's composition-forced normalization.)
\item
  {[}BaldazziPercacciZanusso2021{]} Pietro Baldazzi, Roberto Percacci,
  and Omar Zanusso, ``Self-normalizing path integrals,''
  arXiv:\texttt{2109.00517} (v1, 1 Sep 2021). (Shows that cutting and
  gluing --- composition across temporal boundaries --- uniquely
  determines the normalization of self-normalizing path integrals.)
\item
  {[}Duflo1977{]} Michel Duflo, ``Opérateurs différentiels bi-invariants
  sur un groupe de Lie,'' \emph{Annales Scientifiques de l'École Normale
  Supérieure} (4) \textbf{10}(2), 265--288 (1977). (Constructs the Duflo
  isomorphism \(j^{1/2}\colon S(\mathfrak{g})^G\to Z(U(\mathfrak{g}))\);
  the half-density factor \(|g|^{1/4}\) on compact semisimple Lie groups
  equals \(|J^{1/2}|\) in exponential coordinates.)
\item
  {[}Sudakov1959{]} V.N. Sudakov, ``Linear sets with quasi-invariant
  measure,'' \emph{Doklady Akademii Nauk SSSR} \textbf{127}(3) (1959),
  524--526. (In Russian.) (Establishes the absence of nontrivial
  translation-invariant \(\sigma\)-finite Borel measures on
  infinite-dimensional normed spaces; foundational non-existence result
  for Lebesgue measure on path space.)
\item
  {[}GlimmJaffe1987{]} James Glimm and Arthur Jaffe, \emph{Quantum
  Physics: A Functional Integral Point of View}, 2nd ed.,
  Springer-Verlag, New York (1987). ISBN 978-0-387-96476-8. DOI
  \texttt{10.1007/978-1-4612-4728-9}. (Standard textbook treatment of
  the non-existence of translation-invariant measures on
  infinite-dimensional spaces and the rigorous foundations of the path
  integral; H0.2a statement is standard in this context.)
\item
  {[}Köplinger2025{]} Jens Köplinger, Michael Habeck, and Philip Goyal,
  ``Operational reconstruction of Feynman rules for quantum amplitudes
  via composition algebras,'' arXiv:\texttt{2508.14822} (v2, 16 Dec
  2025). (Coordinate-independent classification of allowable amplitude
  algebras as real associative composition algebras (complex,
  quaternionic, and split forms) via Hurwitz's theorem; derives the Born
  rule without postulating the complex field. Extension of
  {[}GoyalKnuthSkilling2010{]}.)
\end{enumerate}

\end{document}
